---
title: "fig3helper_chromatin_data_diffbind_qc"
output: html_document
date: '2024-01-30'
---
# Overview

## Figure 2 Chromatin changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants

## This is a helper notebook for general exploration of statistical parameters from the test

# Libraries
```{r}
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
```

# Functions
```{r}


```

# Read data

```{r}
data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```

DESeq files
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


Results joined files

```{r}
res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```


# Data re-shaping

Filter by chromatin mark 
```{r}
deseq_list_h3k4me3 <- str_detect(names(deseq_list),"H3K4me3")
deseq_list_h3k27ac <- str_detect(names(deseq_list),"H3K27ac")
deseq_list_rnapolii <- str_detect(names(deseq_list),"RNAPolII")

```

Clean list names
```{r}
names(deseq_list) <- str_remove(names(deseq_list),"cutnrun_")
```

# Read counts distributions

```{r}
deseq_housing <- deseq_list[deseq_list_h3k4me3][[2]]

as.data.frame(counts(deseq_housing)) %>%
  pivot_longer(everything(), names_to = "sample", values_to = "counts") %>%
  ggplot(aes(log10(counts + 1), sample)) +
  geom_boxplot()
```


# P value distributions for each test


housing
```{r}
res_df_h3k27ac %>%
  select(starts_with("pval")) %>%
  select(contains("housing")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram() +
  ggtitle("H3K27ac")

res_df_h3k4me3 %>%
  select(starts_with("pval")) %>%
    select(contains("housing")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram() +
  ggtitle("H3K4me3")

res_df_rnapolii%>%
  select(starts_with("pval")) %>%
    select(contains("housing")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram()+
  ggtitle("RNAPolII")

```


genotype
```{r}

res_df_h3k4me3 %>%
  select(starts_with("pval")) %>%
    select(contains("genotype")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram() +
  ggtitle("H3K4me3")

res_df_rnapolii%>%
  select(starts_with("pval")) %>%
    select(contains("genotype")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram()+
  ggtitle("RNAPolII")

```

Interaction
```{r}

res_df_h3k4me3 %>%
  select(starts_with("pval")) %>%
    select(contains("interaction")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram() +
  ggtitle("H3K4me3")

res_df_rnapolii%>%
  select(starts_with("pval")) %>%
    select(contains("interaction")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram()+
  ggtitle("RNAPolII")

```

# 
```{r}
library(fdrtool)
library(fdrtool)

res_df_h3k27ac_fdrtool <- fdrtool::fdrtool(x =res_df_h3k27ac$stat_H3K27ac_CS_housing_ashr[!is.na(res_df_h3k27ac$padj_H3K27ac_CS_housing_ashr)],plot = TRUE)

res_df_h3k27ac_fdrtool$pval %>%
  enframe() %>%
  ggplot(aes(value)) +
  geom_histogram()

summary(res_df_h3k27ac_fdrtool$qval < 0.05)
```

# Volcano plot for pairwise comparisons

Housing
```{r}
res_df_h3k27ac %>%
  ggplot(aes(log2FoldChange_H3K27ac_CS_housing_ashr, - 10 * log10(pvalue_H3K27ac_CS_housing_ashr), color = padj_H3K27ac_CS_housing_ashr < 0.05)) +
  geom_point() 

res_df_h3k27ac %>%
  ggplot(aes(x = log10(baseMean_H3K27ac_CS_housing_ashr),log2FoldChange_H3K27ac_CS_housing_ashr, color = padj_H3K27ac_CS_housing_ashr < 0.05)) +
  geom_point() 

```

```{r}
res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_CS_housing_ashr, - 10 * log10(pvalue_H3K4me3_CS_housing_ashr), color = padj_H3K4me3_CS_housing_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_CS_housing_ashr),log2FoldChange_H3K4me3_CS_housing_ashr, color = padj_H3K4me3_CS_housing_ashr < 0.05)) +
  geom_point() 

```

```{r}

res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_dsxmut_housing_ashr, - 10 * log10(pvalue_H3K4me3_dsxmut_housing_ashr), color = padj_H3K4me3_dsxmut_housing_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_dsxmut_housing_ashr),log2FoldChange_H3K4me3_dsxmut_housing_ashr, color = padj_H3K4me3_dsxmut_housing_ashr < 0.05)) +
  geom_point() 

```

```{r}

res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_frumut_housing_ashr, - 10 * log10(pvalue_H3K4me3_frumut_housing_ashr), color = padj_H3K4me3_frumut_housing_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_frumut_housing_ashr), log2FoldChange_H3K4me3_frumut_housing_ashr, color = padj_H3K4me3_frumut_housing_ashr < 0.05)) +
  geom_point(alpha = 0.2, size = 0.2)

```

```{r}
res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or47bmut_housing_ashr, - 10 * log10(pvalue_H3K4me3_Or47bmut_housing_ashr), color = padj_H3K4me3_Or47bmut_housing_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_Or47bmut_housing_ashr),log2FoldChange_H3K4me3_Or47bmut_housing_ashr, color = padj_H3K4me3_Or47bmut_housing_ashr < 0.05)) +
  geom_point() 

```


```{r}
res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or67dmut_housing_ashr, - 10 * log10(pvalue_H3K4me3_Or67dmut_housing_ashr), color = padj_H3K4me3_Or67dmut_housing_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_Or67dmut_housing_ashr),log2FoldChange_H3K4me3_Or67dmut_housing_ashr, color = padj_H3K4me3_Or67dmut_housing_ashr < 0.05)) +
  geom_point() 

```

```{r}

res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_frumut_housing_ashr, - 10 * log10(pvalue_RNAPolII_frumut_housing_ashr), color = padj_RNAPolII_frumut_housing_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_frumut_housing_ashr),log2FoldChange_RNAPolII_frumut_housing_ashr, color = padj_RNAPolII_frumut_housing_ashr < 0.05)) +
  geom_point() 

```

```{r}
res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_CS_housing_ashr, - 10 * log10(pvalue_RNAPolII_CS_housing_ashr), color = padj_RNAPolII_CS_housing_ashr < 0.05)) +
  geom_point() 


res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_CS_housing_ashr),log2FoldChange_RNAPolII_CS_housing_ashr, color = padj_RNAPolII_CS_housing_ashr < 0.05)) +
  geom_point() 

```



```{r}
res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_dsxmut_housing_ashr, - 10 * log10(pvalue_RNAPolII_dsxmut_housing_ashr), color = padj_RNAPolII_dsxmut_housing_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_dsxmut_housing_ashr),log2FoldChange_RNAPolII_dsxmut_housing_ashr, color = padj_RNAPolII_dsxmut_housing_ashr < 0.05)) +
  geom_point() 

```


```{r}
res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or47bmut_housing_ashr, - 10 * log10(pvalue_RNAPolII_Or47bmut_housing_ashr), color = padj_RNAPolII_Or47bmut_housing_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_Or47bmut_housing_ashr),log2FoldChange_RNAPolII_Or47bmut_housing_ashr, color = padj_RNAPolII_Or47bmut_housing_ashr < 0.05)) +
  geom_point() 

```


```{r}



res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or67dmut_housing_ashr, - 10 * log10(pvalue_RNAPolII_Or67dmut_housing_ashr), color = padj_RNAPolII_Or67dmut_housing_ashr < 0.05)) +
  geom_point() 


res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_Or67dmut_housing_ashr),log2FoldChange_RNAPolII_Or67dmut_housing_ashr, color = padj_RNAPolII_Or67dmut_housing_ashr < 0.05)) +
  geom_point() 
```

```{r}
res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_dsxmut_GH_genotype_ashr), color = padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_dsxmut_SH_genotype_ashr), color = padj_RNAPolII_dsxmut_SH_genotype_ashr < 0.05)) +
  geom_point() 


res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_dsxmut_GH_genotype_ashr),log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr, color = padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_dsxmut_SH_genotype_ashr),log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr, color = padj_RNAPolII_dsxmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```


```{r}
res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_frumut_GH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_frumut_GH_genotype_ashr), color = padj_RNAPolII_frumut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_frumut_SH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_frumut_SH_genotype_ashr), color = padj_RNAPolII_frumut_SH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_frumut_GH_genotype_ashr),log2FoldChange_RNAPolII_frumut_GH_genotype_ashr, color = padj_RNAPolII_frumut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_frumut_SH_genotype_ashr),log2FoldChange_RNAPolII_frumut_SH_genotype_ashr, color = padj_RNAPolII_frumut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```

```{r}
res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_Or47bmut_GH_genotype_ashr), color = padj_RNAPolII_Or47bmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_Or47bmut_SH_genotype_ashr), color = padj_RNAPolII_Or47bmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_Or47bmut_GH_genotype_ashr),log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr, color = padj_RNAPolII_Or47bmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_Or47bmut_SH_genotype_ashr),log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr, color = padj_RNAPolII_Or47bmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```


```{r}
res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_Or67dmut_GH_genotype_ashr), color = padj_RNAPolII_Or67dmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr, - 10 * log10(pvalue_RNAPolII_Or67dmut_SH_genotype_ashr), color = padj_RNAPolII_Or67dmut_SH_genotype_ashr < 0.05)) +
  geom_point() 


res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_Or67dmut_GH_genotype_ashr),log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr, color = padj_RNAPolII_Or67dmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_rnapolii %>%
  ggplot(aes(log10(baseMean_RNAPolII_Or67dmut_SH_genotype_ashr),log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr, color = padj_RNAPolII_Or67dmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```


```{r}
res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_dsxmut_GH_genotype_ashr), color = padj_H3K4me3_dsxmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_dsxmut_SH_genotype_ashr), color = padj_H3K4me3_dsxmut_SH_genotype_ashr < 0.05)) +
  geom_point() 


res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_dsxmut_GH_genotype_ashr),log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr, color = padj_H3K4me3_dsxmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_dsxmut_SH_genotype_ashr),log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr, color = padj_H3K4me3_dsxmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```


```{r}
res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_frumut_GH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_frumut_GH_genotype_ashr), color = padj_H3K4me3_frumut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_frumut_SH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_frumut_SH_genotype_ashr), color = padj_H3K4me3_frumut_SH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_frumut_GH_genotype_ashr),log2FoldChange_H3K4me3_frumut_GH_genotype_ashr, color = padj_H3K4me3_frumut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_frumut_SH_genotype_ashr),log2FoldChange_H3K4me3_frumut_SH_genotype_ashr, color = padj_H3K4me3_frumut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```

```{r}
res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_Or47bmut_GH_genotype_ashr), color = padj_H3K4me3_Or47bmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_Or47bmut_SH_genotype_ashr), color = padj_H3K4me3_Or47bmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_Or47bmut_GH_genotype_ashr),log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr, color = padj_H3K4me3_Or47bmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_Or47bmut_SH_genotype_ashr),log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr, color = padj_H3K4me3_Or47bmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```


```{r}
res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_Or67dmut_GH_genotype_ashr), color = padj_H3K4me3_Or67dmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr, - 10 * log10(pvalue_H3K4me3_Or67dmut_SH_genotype_ashr), color = padj_H3K4me3_Or67dmut_SH_genotype_ashr < 0.05)) +
  geom_point() 


res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_Or67dmut_GH_genotype_ashr),log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr, color = padj_H3K4me3_Or67dmut_GH_genotype_ashr < 0.05)) +
  geom_point() 

res_df_h3k4me3 %>%
  ggplot(aes(log10(baseMean_H3K4me3_Or67dmut_SH_genotype_ashr),log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr, color = padj_H3K4me3_Or67dmut_SH_genotype_ashr < 0.05)) +
  geom_point() 

```

