---
title: "Fig3 Chromatin"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
date: '2024-02-13'
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

# Overview

## Figure 2 Chromatin changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants

# Libraries
```{r}
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
library(circlize)
```

# Functions

```{r}
# plot z score matrix
plot_heatmap <- function(mat, ...) {
  Heatmap(mat = t(scale(t(mat),center = TRUE,scale = TRUE)), # z score
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), ... )
}
# log2fc matrix
plot_heatmap_log2fc <- function(mat, ...) {
  Heatmap(mat = mat,
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "log2FC",
                                      legend_height = unit(2, "in")) , ... )
}


```

# Read data

```{r}
data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```

DESeq files
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


Results joined files

```{r}
res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```


# Data re-shaping

Filter by chromatin mark 
```{r}
deseq_list_h3k4me3 <- str_detect(names(deseq_list),"H3K4me3")
deseq_list_h3k27ac <- str_detect(names(deseq_list),"H3K27ac")
deseq_list_rnapolii <- str_detect(names(deseq_list),"RNAPolII")

```

Clean list names
```{r}
names(deseq_list) <- str_remove(names(deseq_list),"cutnrun_")
```


# Set up of the CUT&RUN experiments 

# QC of the data: PCA plots 

# PCA

```{r}
vsd_h3k4me3 <- vst(deseq_list$H3K4me3_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds)
vsd_rnapolii <- vst(deseq_list$RNAPolII_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds)

```

```{r}

vsd_h3k4me3$condition <- as.factor(paste0(vsd_h3k4me3$genotype,"_", vsd_h3k4me3$housing))
plotPCA(vsd_h3k4me3, intgroup = c("condition")) + 
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3")
```
```{r}
vsd_rnapolii$condition <- as.factor(paste0(vsd_rnapolii$genotype,"_", vsd_rnapolii$housing))
plotPCA(vsd_rnapolii, intgroup = c("condition")) + 
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("RNAPolII")

```

# LRT

Split  based on log2fc sign combinations

```{r}

res_df_h3k4me3 <- res_df_h3k4me3 %>%
  mutate(across(starts_with("log2FoldChange"),sign,.names = "sign_{.col}"))

res_df_h3k4me3 <- res_df_h3k4me3 %>%
  mutate(sign_paste_genotype_gh = paste0(
    "dsx-gh:",sign_log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr,
    "_fru-gh:",sign_log2FoldChange_H3K4me3_frumut_GH_genotype_ashr,
    "_Or47b-gh:",sign_log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr,
    "_Or67d-gh:",sign_log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr),
    sign_paste_genotype_sh = paste0(
      "dsx-sh:",sign_log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_H3K4me3_frumut_SH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr),
    sign_paste_genotype = paste0(
      "dsx-gh:",sign_log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr,
      "dsx-sh:",sign_log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr,
      "_fru-gh:",sign_log2FoldChange_H3K4me3_frumut_GH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_H3K4me3_frumut_SH_genotype_ashr,
      "_Or47b-gh:",sign_log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr,
      "_Or67d-gh:",sign_log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr))

```



```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_h3kme3_df <- res_df_h3k4me3 %>%
  filter(padj_H3K4me3_genotype_lrt < 0.01) %>%
  select(seqnames, start, end, sign_paste_genotype_gh,starts_with("log2FoldChange")) %>%
  select(!contains("lrt")) %>%
  select(!contains("housing")) %>%
  select(!contains("_SH_"))

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_h3kme3_mat <- pairwise_log2fc_h3kme3_df %>%
  select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_filter <- rowSums(abs(pairwise_log2fc_h3kme3_mat) > 1) >= 1

# Filter out the dataframe
pairwise_log2fc_h3kme3_df <- pairwise_log2fc_h3kme3_df %>%
  filter(logfc_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "log2FoldChange_")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "_genotype_ashr")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "_GH")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "H3K4me3_") 
  colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "mut") 


colnames(pairwise_log2fc_h3kme3_df)
```


```{r}
pairwise_log2fc_h3kme3_df <- pairwise_log2fc_h3kme3_df %>%
  pivot_longer(cols = - c(seqnames, start, end,sign_paste_genotype_gh), names_to = "genotype",values_to = "log2FoldChange") %>%
  mutate(gene_name = paste0(seqnames,":",start,"-",end))


```

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_h3kme3_df$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential H3K4me3 regions")

```


```{r fig.width=6, fig.height=10}


pairwise_log2fc_h3kme3_df %>%
  filter(seqnames %in% c("2L","2R","3L","3R","X")) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste_genotype_gh , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("H3K4me3") 


```


RNAPolII

Split  based on log2fc sign combinations

```{r}

res_df_rnapolii <- res_df_rnapolii %>%
  mutate(across(starts_with("log2FoldChange"),sign,.names = "sign_{.col}"))

res_df_rnapolii <- res_df_rnapolii %>%
  mutate(sign_paste_genotype_gh = paste0(
    "dsx-gh:",sign_log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr,
    "_fru-gh:",sign_log2FoldChange_RNAPolII_frumut_GH_genotype_ashr,
    "_Or47b-gh:",sign_log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr,
    "_Or67d-gh:",sign_log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr),
    sign_paste_genotype_sh = paste0(
      "dsx-sh:",sign_log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_RNAPolII_frumut_SH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr),
    sign_paste_genotype = paste0(
      "dsx-gh:",sign_log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr,
      "dsx-sh:",sign_log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr,
      "_fru-gh:",sign_log2FoldChange_RNAPolII_frumut_GH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_RNAPolII_frumut_SH_genotype_ashr,
      "_Or47b-gh:",sign_log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr,
      "_Or67d-gh:",sign_log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr))

```



```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_rnapolii_df <- res_df_rnapolii %>%
  filter(padj_RNAPolII_genotype_lrt < 0.01) %>%
  select(seqnames, start, end, sign_paste_genotype_gh,starts_with("log2FoldChange")) %>%
  select(!contains("lrt")) %>%
  select(!contains("housing")) %>%
  select(!contains("_SH_"))

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_rnapolii_mat <- pairwise_log2fc_rnapolii_df %>%
  select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_filter <- rowSums(abs(pairwise_log2fc_rnapolii_mat) > 1) >= 1

# Filter out the dataframe
pairwise_log2fc_rnapolii_df <- pairwise_log2fc_rnapolii_df %>%
  filter(logfc_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "log2FoldChange_")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "_genotype_ashr")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "_GH")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "RNAPolII_") 
  colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "mut") 


colnames(pairwise_log2fc_rnapolii_df)
```


```{r}
pairwise_log2fc_rnapolii_df <- pairwise_log2fc_rnapolii_df %>%
  pivot_longer(cols = - c(seqnames, start, end,sign_paste_genotype_gh), names_to = "genotype",values_to = "log2FoldChange") %>%
  mutate(gene_name = paste0(seqnames,":",start,"-",end))


```

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_rnapolii_df$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential RNAPolII regions") +
  theme_classic() +
  theme(aspect.ratio = 1)

```


```{r fig.width=6,fig.height=10}


pairwise_log2fc_rnapolii_df %>%
  filter(seqnames %in% c("2L","2R","3L","3R","X")) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste_genotype_gh , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("RNAPolII")


```

# Volcano plots for different comparisons

### Data transform for volcano plots

```{r}
log2fc_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("log2FoldChange")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

padj_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("padj")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("pvalue")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("baseMean")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long, log2fc_long, padj_long, pval_long)
res_long_h3k4me3_df <- purrr::reduce(res_long_list,left_join,by =c("seqnames","start","end","comparison") )
```

```{r}
log2fc_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("log2FoldChange")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

padj_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("padj")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("pvalue")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("baseMean")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long, log2fc_long, padj_long, pval_long)
res_long_rnapolii_df <- purrr::reduce(res_long_list,left_join,by =c("seqnames","start","end","comparison") )
```



## Housing within the same genotype

```{r}
res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"housing")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(pvalue),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3 pairwise")
```

```{r}
res_long_rnapolii_df %>%
  filter(str_detect(comparison,"housing")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(pvalue),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("RNAPolII pairwise")
```

## GH: all to CS

```{r}

res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "GH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3 Mutant vs CS GH")


```

```{r}

res_long_rnapolii_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "GH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1)+
  ggtitle("RNAPolII Mutant vs CS GH")


```

## SH: all to a CS

```{r}

res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "SH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3 Mutant vs CS SH")


```

```{r}

res_long_rnapolii_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "SH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1)+
  ggtitle("RNAPolII Mutant vs CS SH")


```

# Heatmaps:

## Data re-shaping

### Build norm counts z score matrix

```{r}
norm_cts_h3k4me3 <- counts(deseq_list$H3K4me3_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds,norm =TRUE)

norm_cts_rnapolii <- counts(deseq_list$RNAPolII_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds,norm =TRUE)

rownames(norm_cts_h3k4me3) <- as.data.frame(granges(rowRanges(deseq_list$H3K4me3_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds))) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

rownames(norm_cts_rnapolii) <- as.data.frame(granges(rowRanges(deseq_list$RNAPolII_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds))) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

```


```{r}
de_genotype_gh_h3k4me3_id <- res_long_h3k4me3_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "GH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

de_genotype_sh_h3k4me3_id <- res_long_h3k4me3_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "SH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

```

```{r}
de_genotype_gh_rnapolii_id <- res_long_rnapolii_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "GH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

de_genotype_sh_rnapolii_id <- res_long_rnapolii_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "SH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

```

Norm counts median per group

```{r}

get_median_per_group <- function(norm_cts) {
  # Remove rows with zero counts
  norm_cts_filt <- norm_cts[rowSums(norm_cts) > 0,]
  
  # Get mean matrix
  norm_cts_median <- as.data.frame(norm_cts_filt) %>% # convert matrix to data frame, makes it compatible with dplyr
    rownames_to_column(var = "gene_symbol") %>% # move rownames to a new column, makes it compatible with dplyr 
    pivot_longer(cols = -gene_symbol, # make data.frame in tidy format
                 names_to = "sample_name",
                 values_to = "normalizedCounts") %>% 
    mutate(condition = str_remove(sample_name, "_R\\d$")) %>% # Make condition variables 
    group_by(gene_symbol, condition) %>% # Group by experimental condition 
    summarise(normalizedCounts_median = median(normalizedCounts)) %>% # Calculate mean per groups 
    pivot_wider(names_from = condition, # Return from tidy to matrix format 
                values_from = normalizedCounts_median)
  # process matrix further as a numeric matrix format with rownames, compatible with ComplexHeatmap
  norm_cts_median <- as.data.frame(norm_cts_median) 
  rownames(norm_cts_median) <- norm_cts_median$gene_symbol
  norm_cts_median <- norm_cts_median %>%
    dplyr::select(- gene_symbol)
  norm_cts_median <- as.matrix(norm_cts_median)
  return(norm_cts_median)
}
norm_cts_h3k4me3_median <- get_median_per_group(norm_cts_h3k4me3)
norm_cts_rnapolii_median <- get_median_per_group(norm_cts_rnapolii)

```

### Build log2Fold change matrix
Select only log2FoldChange variables

```{r}
log2fc_mat_h3k4me3_genotype_gh <- res_df_h3k4me3 %>%
    filter(padj_H3K4me3_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_GH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("GH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()

log2fc_mat_h3k4me3_genotype_sh <- res_df_h3k4me3 %>%
    filter(padj_H3K4me3_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_SH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("SH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()


colnames(log2fc_mat_h3k4me3_genotype_gh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_gh) ,"log2FoldChange_")
colnames(log2fc_mat_h3k4me3_genotype_gh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_gh) ,"genotype_ashr")

colnames(log2fc_mat_h3k4me3_genotype_sh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_sh) ,"log2FoldChange_")
colnames(log2fc_mat_h3k4me3_genotype_sh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_sh) ,"genotype_ashr")
```

```{r}
log2fc_mat_rnapolii_genotype_gh <- res_df_rnapolii %>%
    filter(padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_GH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("GH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()

log2fc_mat_rnapolii_genotype_sh <- res_df_rnapolii %>%
    filter(padj_RNAPolII_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_SH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("SH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()


colnames(log2fc_mat_rnapolii_genotype_gh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_gh) ,"log2FoldChange_")
colnames(log2fc_mat_rnapolii_genotype_gh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_gh) ,"genotype_ashr")

colnames(log2fc_mat_rnapolii_genotype_sh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_sh) ,"log2FoldChange_")
colnames(log2fc_mat_rnapolii_genotype_sh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_sh) ,"genotype_ashr")
```


# Connect to genes

```{r}
library(GenomicRanges)
library(GenomicFeatures)
library(plyranges)
res_gr_h3k4me3 <- makeGRangesFromDataFrame( res_df_h3k4me3,keep.extra.columns = TRUE)
res_gr_rnapolii <- makeGRangesFromDataFrame( res_df_rnapolii,keep.extra.columns = TRUE)

```

```{r}
library(TxDb.Dmelanogaster.UCSC.dm6.ensGene)
library(org.Dm.eg.db)
library(GenomicFeatures)
library(clusterProfiler)

promoters_dm6 <- promoters(TxDb.Dmelanogaster.UCSC.dm6.ensGene, columns = "gene_id",upstream=0,downstream=1)

seqlevels(promoters_dm6) <- str_remove(seqlevels(promoters_dm6),"chr")

promoter_map_df <- clusterProfiler::bitr(geneID = unlist(promoters_dm6$gene_id), fromType = "ENSEMBL",toType ="SYMBOL",OrgDb = org.Dm.eg.db )
promoter_map <- promoter_map_df$SYMBOL 
names(promoter_map) <-  promoter_map_df$ENSEMBL

promoters_dm6$gene_name <- promoter_map[unlist(promoters_dm6$gene_id)]


promoter_map_df_entrez <- clusterProfiler::bitr(geneID = unlist(promoters_dm6$gene_id), fromType = "ENSEMBL",toType ="ENTREZID",OrgDb = org.Dm.eg.db )
promoter_map_entrez <- promoter_map_df_entrez$ENTREZ 
names(promoter_map_entrez) <-  promoter_map_df_entrez$ENSEMBL

promoters_dm6$entrez_id <- promoter_map_entrez[unlist(promoters_dm6$gene_id)]

```



```{r}
# H3K4me3
res_gr_h3k4me3_genes <- plyranges::join_nearest_left(x = res_gr_h3k4me3,y = promoters_dm6, distance = TRUE) 

res_gr_h3k4me3_genes$range_id <- as.data.frame(granges(res_gr_h3k4me3_genes)) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

names(res_gr_h3k4me3_genes) <- as.data.frame(elementMetadata(res_gr_h3k4me3_genes)) %>%
  pull(range_id)

# RNAPolII

res_gr_rnapolii_genes <- plyranges::join_nearest_left(x = res_gr_rnapolii,y = promoters_dm6, distance = TRUE) 

res_gr_rnapolii_genes$range_id <- as.data.frame(granges(res_gr_rnapolii_genes)) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

names(res_gr_rnapolii_genes) <- as.data.frame(elementMetadata(res_gr_rnapolii_genes)) %>%
  pull(range_id)

```

Filter, get diff genes
```{r}
diff_ranges_h3k4me3_gh <- as.data.frame(elementMetadata(res_gr_h3k4me3_genes)) %>%
    filter(padj_H3K4me3_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_GH_genotype_ashr < 0.01) %>%
  pull(range_id)


diff_ranges_h3k4me3_sh <- as.data.frame(elementMetadata(res_gr_h3k4me3_genes)) %>%
    filter(padj_H3K4me3_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_SH_genotype_ashr < 0.01) %>%
  pull(range_id)


diff_ranges_rnapolii_gh <- as.data.frame(elementMetadata(res_gr_rnapolii_genes)) %>%
    filter(padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_GH_genotype_ashr < 0.01) %>%
  pull(range_id)


diff_ranges_rnapolii_sh <- as.data.frame(elementMetadata(res_gr_rnapolii_genes)) %>%
    filter(padj_RNAPolII_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_SH_genotype_ashr < 0.01) %>%
  pull(range_id)



```



### Read target genes

#### Fru

```{r}
fru_ma_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 1-fruma_targets.csv")[,-2]
fru_mc_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 2-frumc_targets.csv")[,-2]
fru_mb_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 3-frumb_targets.csv")[,-2]


fru_ma_genes <- fru_ma_genes$FruMA
fru_mc_genes <- fru_mc_genes$FruMC
fru_mb_genes <- fru_mb_genes$FruMB

fru_target_genes <- unique(c(fru_ma_genes, fru_mc_genes, fru_mb_genes))
```



```{r}
de_genotype_h3k4me3_gh_genes_id_fru <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$gene_name %in% fru_target_genes]

de_genotype_h3k4me3_sh_genes_id_fru <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$gene_name %in% fru_target_genes]

```

```{r}
de_genotype_rnapolii_gh_genes_id_fru <- res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$gene_name %in% fru_target_genes]

de_genotype_rnapolii_sh_genes_id_fru <- res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$gene_name %in% fru_target_genes]

```

#### dsx

```{r}
dsx_target_genes <- readxl::read_excel("../data_input/gene_annotations/dsx_target_genes.xlsx",sheet = 3)
dsx_target_genes <- dsx_target_genes$`Male_Fatbody_DamIDseq_Gene_Level_Occupancy> 0.9`
```


```{r}
de_genotype_h3k4me3_gh_genes_id_dsx <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$gene_name %in% dsx_target_genes]

de_genotype_h3k4me3_sh_genes_id_dsx <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$gene_name %in% dsx_target_genes]

```

```{r}
de_genotype_rnapolii_gh_genes_id_dsx <- res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$gene_name %in% dsx_target_genes]

de_genotype_rnapolii_sh_genes_id_dsx <- res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$gene_name %in% dsx_target_genes]

```

#### go
metabolism 
defense response
redox 
reproductive behavior 
feeding behavior 


### GH vs wt

#### Z score all reps

##### for all DEGs

```{r}
plot_heatmap(norm_cts_h3k4me3[de_genotype_gh_h3k4me3_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii[de_genotype_gh_rnapolii_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### fru

```{r}
plot_heatmap(norm_cts_h3k4me3[de_genotype_h3k4me3_gh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii[de_genotype_rnapolii_gh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### dsx

```{r}
plot_heatmap(norm_cts_h3k4me3[de_genotype_h3k4me3_gh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii[de_genotype_rnapolii_gh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### go

#### Z score median

##### for all DEGs

```{r}
plot_heatmap(norm_cts_h3k4me3_median[de_genotype_gh_h3k4me3_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii_median[de_genotype_gh_rnapolii_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```


##### fru

```{r}
plot_heatmap(norm_cts_h3k4me3_median[de_genotype_h3k4me3_gh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii_median[de_genotype_rnapolii_gh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### dsx

```{r}
plot_heatmap(norm_cts_h3k4me3_median[de_genotype_h3k4me3_gh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii_median[de_genotype_rnapolii_gh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### go

#### log2FC

##### for all DEGs

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_gh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```


```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_gh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### fru

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_gh[rownames(log2fc_mat_h3k4me3_genotype_gh) %in% de_genotype_h3k4me3_gh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_gh[rownames(log2fc_mat_rnapolii_genotype_gh) %in% de_genotype_rnapolii_gh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### dsx


```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_gh[rownames(log2fc_mat_h3k4me3_genotype_gh) %in% de_genotype_h3k4me3_gh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_gh[rownames(log2fc_mat_rnapolii_genotype_gh) %in% de_genotype_rnapolii_gh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### go

### SH vs wt

#### Z score all reps

##### for all DEGs

```{r}
plot_heatmap(norm_cts_h3k4me3[de_genotype_sh_h3k4me3_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii[de_genotype_sh_rnapolii_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### fru

```{r}
plot_heatmap(norm_cts_h3k4me3[de_genotype_h3k4me3_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii[de_genotype_rnapolii_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### dsx

```{r}
plot_heatmap(norm_cts_h3k4me3[de_genotype_h3k4me3_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii[de_genotype_rnapolii_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### go

#### Z score median

##### for all DEGs

```{r}
plot_heatmap(norm_cts_h3k4me3_median[de_genotype_sh_h3k4me3_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii_median[de_genotype_sh_rnapolii_id,], show_row_names = FALSE, cluster_rows = TRUE) 
```


##### fru

```{r}
plot_heatmap(norm_cts_h3k4me3_median[de_genotype_h3k4me3_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii_median[de_genotype_rnapolii_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### dsx

```{r}
plot_heatmap(norm_cts_h3k4me3_median[de_genotype_h3k4me3_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

```{r}
plot_heatmap(norm_cts_rnapolii_median[de_genotype_rnapolii_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE) 
```

##### go

#### log2FC

##### for all DEGs

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_sh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```


```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_sh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### fru

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_sh[rownames(log2fc_mat_h3k4me3_genotype_sh) %in% de_genotype_h3k4me3_sh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_sh[rownames(log2fc_mat_rnapolii_genotype_sh) %in% de_genotype_rnapolii_sh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### dsx


```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_sh[rownames(log2fc_mat_h3k4me3_genotype_sh) %in% de_genotype_h3k4me3_sh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_sh[rownames(log2fc_mat_rnapolii_genotype_sh) %in% de_genotype_rnapolii_sh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### go


# Venn diagram with (at least) three groups of DEGs:

## Make lists for different combinations of comparisons

```{r}
res_long_h3k4me3_df_any <- res_long_h3k4me3_df %>%
  drop_na(padj) %>%
  filter(padj < 0.01)
```

```{r}
res_long_rnapolii_df_any <- res_long_rnapolii_df %>%
  drop_na(padj) %>%
  filter(padj < 0.01)
```


## GH: all to CS

### All

```{r}
comp_list_genotype_gh_all_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_gh_all_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

```

### Up

```{r}
comp_list_genotype_gh_up_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_gh_up_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```

### Down

```{r}
comp_list_genotype_gh_down_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_gh_down_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```

## SH: all to CS

### All

```{r}
comp_list_genotype_sh_all_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_sh_all_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

```

### Up

```{r}
comp_list_genotype_sh_up_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_sh_up_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```

### Down

```{r}
comp_list_genotype_sh_down_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_sh_down_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```


## Plot venn diagrams

## GH: all to CS

### All

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Up

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

## SH: all to a CS

### All

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Up

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH DOWN H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH DOWN RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

# GO terms for different comparisons
```{r}
go_universe_h3k4me3 <- as.data.frame(unique(res_gr_h3k4me3_genes)) %>%
  pull(entrez_id) %>%
  unique()

go_universe_rnapolii <- as.data.frame(unique(res_gr_rnapolii_genes)) %>%
  pull(entrez_id) %>%
  unique()


```


```{r}

res_gr_h3k4me3_genes_list <- as.data.frame(unique(res_gr_h3k4me3_genes)) %>%
  select(entrez_id, contains("genotype") & starts_with("padj") & ! contains("lrt")) %>%
  pivot_longer(-entrez_id, names_to ="comparison",values_to = "padj") %>%
  filter(padj < 0.01) %>%
  mutate(comparison = str_remove(comparison, "padj_H3K4me3_")) %>%
  mutate(comparison = str_remove(comparison, "_genotype_ashr") ) %>%
  drop_na() %>%
  split(f = .$comparison) %>%
  map(~unique(.x$entrez_id))

```


```{r}

res_gr_h3k4me3_genes_go <- compareCluster(geneClusters = res_gr_h3k4me3_genes_list,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe_h3k4me3,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

#dotplot(res_gr_h3k4me3_genes_go,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms H3K4me3")
```





```{r}

res_gr_rnapolii_genes_list <- as.data.frame(unique(res_gr_rnapolii_genes)) %>%
  select(entrez_id, contains("genotype")  & starts_with("padj") & ! contains("lrt")) %>%
  pivot_longer(-entrez_id, names_to ="comparison",values_to = "padj") %>%
  filter(padj < 0.01) %>%
  mutate(comparison = str_remove(comparison, "padj_RNAPolII_")) %>%
  mutate(comparison = str_remove(comparison, "_genotype_ashr") ) %>%
  drop_na() %>%
  split(f = .$comparison) %>%
  map(~unique(.x$entrez_id))

```



```{r}
res_gr_rnapolii_genes_go <- compareCluster(geneClusters = res_gr_rnapolii_genes_list,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe_rnapolii,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(res_gr_rnapolii_genes_go,showCategory = Inf, by='GeneRatio') +
  ggtitle("GO terms RNAPolII")

res_gr_rnapolii_genes_go@compareClusterResult
```



# IGV view for specific genes: will update with new analysis, can put together with different heatmaps 
## Fru
## Dsx
## Dsk
## Housekeeping genes Or negative control genes 
