---
title: "Fig4 RNA + Chromatin"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
date: '2024-02-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```



# Overview

## Figure 5 Correlation of the changes on transcriptome and chromatin 

# Libraries
```{r}
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
library(circlize)
library(ComplexHeatmap) # Heatmaps
library(DESeq2) 
library(ggVennDiagram) 
library(clusterProfiler) # Go terms
library(org.Dm.eg.db) # GO annotation
library(tidyverse)
library(circlize) # Colors

```

# Functions
```{r}
get_genes_in_set <- function(gene_set, gene_universe) {
  return(map_lgl(gene_universe, ~ .x %in% gene_set))
}
get_overlap_genes <- function(named_list_gene_sets) {
  # Get all unique genes
  gene_universe <- na.omit(unique(unlist(named_list_gene_sets)))
  
  named_list_gene_sets <- map(named_list_gene_sets, # For each list:
                              # For each gene:
                              # Is gene in list? -> get logical for each list
                              get_genes_in_set,
                              gene_universe = gene_universe)
  
  # Return lgl matrix of presence / absence for each gene
  named_list_gene_sets <- as.data.frame(named_list_gene_sets)
  rownames(named_list_gene_sets) <- gene_universe
  return(named_list_gene_sets)
  
}
# Convert symbol to entrezid
tr_symbol2entrezid <- function(.x, symbol_etrez_map){
  symbol_etrez_map[.x]
}

```

# Read chromatin data

# Read data

```{r}
data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```

DESeq files
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


Results joined files

```{r}
res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```


# Data re-shaping

Filter by chromatin mark 
```{r}
deseq_list_h3k4me3 <- str_detect(names(deseq_list),"H3K4me3")
deseq_list_h3k27ac <- str_detect(names(deseq_list),"H3K27ac")
deseq_list_rnapolii <- str_detect(names(deseq_list),"RNAPolII")

```

Clean list names
```{r}
names(deseq_list) <- str_remove(names(deseq_list),"cutnrun_")
```


# Set up of the CUT&RUN experiments 

# QC of the data: PCA plots 

# PCA

```{r}
vsd_h3k4me3 <- vst(deseq_list$H3K4me3_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds)
vsd_rnapolii <- vst(deseq_list$RNAPolII_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds)

```


# LRT

Split  based on log2fc sign combinations

```{r}

res_df_h3k4me3 <- res_df_h3k4me3 %>%
  mutate(across(starts_with("log2FoldChange"),sign,.names = "sign_{.col}"))

res_df_h3k4me3 <- res_df_h3k4me3 %>%
  mutate(sign_paste_genotype_gh = paste0(
    "dsx-gh:",sign_log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr,
    "_fru-gh:",sign_log2FoldChange_H3K4me3_frumut_GH_genotype_ashr,
    "_Or47b-gh:",sign_log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr,
    "_Or67d-gh:",sign_log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr),
    sign_paste_genotype_sh = paste0(
      "dsx-sh:",sign_log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_H3K4me3_frumut_SH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr),
    sign_paste_genotype = paste0(
      "dsx-gh:",sign_log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr,
      "dsx-sh:",sign_log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr,
      "_fru-gh:",sign_log2FoldChange_H3K4me3_frumut_GH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_H3K4me3_frumut_SH_genotype_ashr,
      "_Or47b-gh:",sign_log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr,
      "_Or67d-gh:",sign_log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr))

```



```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_h3kme3_df <- res_df_h3k4me3 %>%
  filter(padj_H3K4me3_genotype_lrt < 0.01) %>%
  dplyr::select(seqnames, start, end, sign_paste_genotype_gh,starts_with("log2FoldChange")) %>%
  dplyr::select(!contains("lrt")) %>%
  dplyr::select(!contains("housing")) %>%
  dplyr::select(!contains("_SH_"))

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_h3kme3_mat <- pairwise_log2fc_h3kme3_df %>%
  dplyr::select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_filter <- rowSums(abs(pairwise_log2fc_h3kme3_mat) > 1) >= 1

# Filter out the dataframe
pairwise_log2fc_h3kme3_df <- pairwise_log2fc_h3kme3_df %>%
  filter(logfc_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "log2FoldChange_")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "_genotype_ashr")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "_GH")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "H3K4me3_") 
  colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "mut") 


colnames(pairwise_log2fc_h3kme3_df)
```


```{r}
pairwise_log2fc_h3kme3_df <- pairwise_log2fc_h3kme3_df %>%
  pivot_longer(cols = - c(seqnames, start, end,sign_paste_genotype_gh), names_to = "genotype",values_to = "log2FoldChange") %>%
  mutate(gene_name = paste0(seqnames,":",start,"-",end))


```

RNAPolII

Split  based on log2fc sign combinations

```{r}

res_df_rnapolii <- res_df_rnapolii %>%
  mutate(across(starts_with("log2FoldChange"),sign,.names = "sign_{.col}"))

res_df_rnapolii <- res_df_rnapolii %>%
  mutate(sign_paste_genotype_gh = paste0(
    "dsx-gh:",sign_log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr,
    "_fru-gh:",sign_log2FoldChange_RNAPolII_frumut_GH_genotype_ashr,
    "_Or47b-gh:",sign_log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr,
    "_Or67d-gh:",sign_log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr),
    sign_paste_genotype_sh = paste0(
      "dsx-sh:",sign_log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_RNAPolII_frumut_SH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr),
    sign_paste_genotype = paste0(
      "dsx-gh:",sign_log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr,
      "dsx-sh:",sign_log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr,
      "_fru-gh:",sign_log2FoldChange_RNAPolII_frumut_GH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_RNAPolII_frumut_SH_genotype_ashr,
      "_Or47b-gh:",sign_log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr,
      "_Or67d-gh:",sign_log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr))

```



```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_rnapolii_df <- res_df_rnapolii %>%
  filter(padj_RNAPolII_genotype_lrt < 0.01) %>%
  dplyr::select(seqnames, start, end, sign_paste_genotype_gh,starts_with("log2FoldChange")) %>%
  dplyr::select(!contains("lrt")) %>%
  dplyr::select(!contains("housing")) %>%
  dplyr::select(!contains("_SH_"))

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_rnapolii_mat <- pairwise_log2fc_rnapolii_df %>%
  dplyr::select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_filter <- rowSums(abs(pairwise_log2fc_rnapolii_mat) > 1) >= 1

# Filter out the dataframe
pairwise_log2fc_rnapolii_df <- pairwise_log2fc_rnapolii_df %>%
  filter(logfc_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "log2FoldChange_")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "_genotype_ashr")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "_GH")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "RNAPolII_") 
  colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "mut") 


```


```{r}
pairwise_log2fc_rnapolii_df <- pairwise_log2fc_rnapolii_df %>%
  pivot_longer(cols = - c(seqnames, start, end,sign_paste_genotype_gh), names_to = "genotype",values_to = "log2FoldChange") %>%
  mutate(gene_name = paste0(seqnames,":",start,"-",end))


```

### Data transform for volcano plots

```{r}
log2fc_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("log2FoldChange")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

padj_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("padj")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("pvalue")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df_h3k4me3 %>%
  dplyr::select(seqnames,start,end, starts_with("baseMean")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long, log2fc_long, padj_long, pval_long)
res_long_h3k4me3_df <- purrr::reduce(res_long_list,left_join,by =c("seqnames","start","end","comparison") )
```

```{r}
log2fc_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("log2FoldChange")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

padj_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("padj")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("pvalue")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df_rnapolii %>%
  dplyr::select(seqnames,start,end, starts_with("baseMean")) %>%
  pivot_longer(c(-seqnames,-start,-end), names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long, log2fc_long, padj_long, pval_long)
res_long_rnapolii_df <- purrr::reduce(res_long_list,left_join,by =c("seqnames","start","end","comparison") )
```


# Heatmaps:

## Data re-shaping

### Build norm counts z score matrix

```{r}
norm_cts_h3k4me3 <- counts(deseq_list$H3K4me3_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds,norm =TRUE)

norm_cts_rnapolii <- counts(deseq_list$RNAPolII_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds,norm =TRUE)

rownames(norm_cts_h3k4me3) <- as.data.frame(granges(rowRanges(deseq_list$H3K4me3_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds))) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

rownames(norm_cts_rnapolii) <- as.data.frame(granges(rowRanges(deseq_list$RNAPolII_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds))) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

```


```{r}
de_genotype_gh_h3k4me3_id <- res_long_h3k4me3_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "GH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

de_genotype_sh_h3k4me3_id <- res_long_h3k4me3_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "SH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

```

```{r}
de_genotype_gh_rnapolii_id <- res_long_rnapolii_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "GH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

de_genotype_sh_rnapolii_id <- res_long_rnapolii_df %>%
  dplyr::select(seqnames, start, end, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "SH_genotype")) %>%
  filter(padj < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id) %>%
  unique()

```

Norm counts median per group

```{r}

get_median_per_group <- function(norm_cts) {
  # Remove rows with zero counts
  norm_cts_filt <- norm_cts[rowSums(norm_cts) > 0,]
  
  # Get mean matrix
  norm_cts_median <- as.data.frame(norm_cts_filt) %>% # convert matrix to data frame, makes it compatible with dplyr
    rownames_to_column(var = "gene_symbol") %>% # move rownames to a new column, makes it compatible with dplyr 
    pivot_longer(cols = -gene_symbol, # make data.frame in tidy format
                 names_to = "sample_name",
                 values_to = "normalizedCounts") %>% 
    mutate(condition = str_remove(sample_name, "_R\\d$")) %>% # Make condition variables 
    group_by(gene_symbol, condition) %>% # Group by experimental condition 
    summarise(normalizedCounts_median = median(normalizedCounts)) %>% # Calculate mean per groups 
    pivot_wider(names_from = condition, # Return from tidy to matrix format 
                values_from = normalizedCounts_median)
  # process matrix further as a numeric matrix format with rownames, compatible with ComplexHeatmap
  norm_cts_median <- as.data.frame(norm_cts_median) 
  rownames(norm_cts_median) <- norm_cts_median$gene_symbol
  norm_cts_median <- norm_cts_median %>%
    dplyr::select(- gene_symbol)
  norm_cts_median <- as.matrix(norm_cts_median)
  return(norm_cts_median)
}
norm_cts_h3k4me3_median <- get_median_per_group(norm_cts_h3k4me3)
norm_cts_rnapolii_median <- get_median_per_group(norm_cts_rnapolii)

```

### Build log2Fold change matrix
Select only log2FoldChange variables

```{r}
log2fc_mat_h3k4me3_genotype_gh <- res_df_h3k4me3 %>%
    filter(padj_H3K4me3_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_GH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("GH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()

log2fc_mat_h3k4me3_genotype_sh <- res_df_h3k4me3 %>%
    filter(padj_H3K4me3_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_SH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("SH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()


colnames(log2fc_mat_h3k4me3_genotype_gh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_gh) ,"log2FoldChange_")
colnames(log2fc_mat_h3k4me3_genotype_gh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_gh) ,"genotype_ashr")

colnames(log2fc_mat_h3k4me3_genotype_sh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_sh) ,"log2FoldChange_")
colnames(log2fc_mat_h3k4me3_genotype_sh) <- str_remove(colnames(log2fc_mat_h3k4me3_genotype_sh) ,"genotype_ashr")
```

```{r}
log2fc_mat_rnapolii_genotype_gh <- res_df_rnapolii %>%
    filter(padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_GH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("GH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()

log2fc_mat_rnapolii_genotype_sh <- res_df_rnapolii %>%
    filter(padj_RNAPolII_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_SH_genotype_ashr < 0.01) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, starts_with("log2FoldChange") & contains("SH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "range_id") %>%
  as.matrix()


colnames(log2fc_mat_rnapolii_genotype_gh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_gh) ,"log2FoldChange_")
colnames(log2fc_mat_rnapolii_genotype_gh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_gh) ,"genotype_ashr")

colnames(log2fc_mat_rnapolii_genotype_sh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_sh) ,"log2FoldChange_")
colnames(log2fc_mat_rnapolii_genotype_sh) <- str_remove(colnames(log2fc_mat_rnapolii_genotype_sh) ,"genotype_ashr")
```


# Connect to genes

```{r}
library(GenomicRanges)
library(GenomicFeatures)
library(plyranges)
res_gr_h3k4me3 <- makeGRangesFromDataFrame( res_df_h3k4me3,keep.extra.columns = TRUE)
res_gr_rnapolii <- makeGRangesFromDataFrame( res_df_rnapolii,keep.extra.columns = TRUE)

```

```{r}
library(TxDb.Dmelanogaster.UCSC.dm6.ensGene)
library(org.Dm.eg.db)
library(GenomicFeatures)
library(clusterProfiler)

promoters_dm6 <- promoters(TxDb.Dmelanogaster.UCSC.dm6.ensGene, columns = "gene_id",upstream=0,downstream=1)

seqlevels(promoters_dm6) <- str_remove(seqlevels(promoters_dm6),"chr")

promoter_map_df <- clusterProfiler::bitr(geneID = unlist(promoters_dm6$gene_id), fromType = "ENSEMBL",toType ="SYMBOL",OrgDb = org.Dm.eg.db )
promoter_map <- promoter_map_df$SYMBOL 
names(promoter_map) <-  promoter_map_df$ENSEMBL

promoters_dm6$gene_name <- promoter_map[unlist(promoters_dm6$gene_id)]


promoter_map_df_entrez <- clusterProfiler::bitr(geneID = unlist(promoters_dm6$gene_id), fromType = "ENSEMBL",toType ="ENTREZID",OrgDb = org.Dm.eg.db )
promoter_map_entrez <- promoter_map_df_entrez$ENTREZ 
names(promoter_map_entrez) <-  promoter_map_df_entrez$ENSEMBL

promoters_dm6$entrez_id <- promoter_map_entrez[unlist(promoters_dm6$gene_id)]

```



```{r}
# H3K4me3
res_gr_h3k4me3_genes <- plyranges::join_nearest_left(x = res_gr_h3k4me3,y = promoters_dm6, distance = TRUE) 

res_gr_h3k4me3_genes$range_id <- as.data.frame(granges(res_gr_h3k4me3_genes)) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

names(res_gr_h3k4me3_genes) <- as.data.frame(elementMetadata(res_gr_h3k4me3_genes)) %>%
  pull(range_id)

# RNAPolII

res_gr_rnapolii_genes <- plyranges::join_nearest_left(x = res_gr_rnapolii,y = promoters_dm6, distance = TRUE) 

res_gr_rnapolii_genes$range_id <- as.data.frame(granges(res_gr_rnapolii_genes)) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  pull(range_id)

names(res_gr_rnapolii_genes) <- as.data.frame(elementMetadata(res_gr_rnapolii_genes)) %>%
  pull(range_id)

```

Filter, get diff genes
```{r}
diff_ranges_h3k4me3_gh <- as.data.frame(elementMetadata(res_gr_h3k4me3_genes)) %>%
    filter(padj_H3K4me3_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_GH_genotype_ashr < 0.01) %>%
  pull(range_id)


diff_ranges_h3k4me3_sh <- as.data.frame(elementMetadata(res_gr_h3k4me3_genes)) %>%
    filter(padj_H3K4me3_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_H3K4me3_frumut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_H3K4me3_Or47bmut_SH_genotype_ashr < 0.01) %>%
  pull(range_id)


diff_ranges_rnapolii_gh <- as.data.frame(elementMetadata(res_gr_rnapolii_genes)) %>%
    filter(padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_GH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_GH_genotype_ashr < 0.01) %>%
  pull(range_id)


diff_ranges_rnapolii_sh <- as.data.frame(elementMetadata(res_gr_rnapolii_genes)) %>%
    filter(padj_RNAPolII_dsxmut_SH_genotype_ashr < 0.01 | 
           padj_RNAPolII_frumut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or67dmut_SH_genotype_ashr < 0.01 |
           padj_RNAPolII_Or47bmut_SH_genotype_ashr < 0.01) %>%
  pull(range_id)



```



### Read target genes

#### Fru

```{r}
fru_ma_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 1-fruma_targets.csv")[,-2]
fru_mc_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 2-frumc_targets.csv")[,-2]
fru_mb_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 3-frumb_targets.csv")[,-2]


fru_ma_genes <- fru_ma_genes$FruMA
fru_mc_genes <- fru_mc_genes$FruMC
fru_mb_genes <- fru_mb_genes$FruMB

fru_target_genes <- unique(c(fru_ma_genes, fru_mc_genes, fru_mb_genes))
```



```{r}
de_genotype_h3k4me3_gh_genes_id_fru <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$gene_name %in% fru_target_genes]

de_genotype_h3k4me3_sh_genes_id_fru <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$gene_name %in% fru_target_genes]

```

```{r}
de_genotype_rnapolii_gh_genes_id_fru <- res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$gene_name %in% fru_target_genes]

de_genotype_rnapolii_sh_genes_id_fru <- res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$gene_name %in% fru_target_genes]

```

#### dsx

```{r}
dsx_target_genes <- readxl::read_excel("../data_input/gene_annotations/dsx_target_genes.xlsx",sheet = 3)
dsx_target_genes <- dsx_target_genes$`Male_Fatbody_DamIDseq_Gene_Level_Occupancy> 0.9`
```


```{r}
de_genotype_h3k4me3_gh_genes_id_dsx <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_gh]$gene_name %in% dsx_target_genes]

de_genotype_h3k4me3_sh_genes_id_dsx <- res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$range_id[res_gr_h3k4me3_genes[diff_ranges_h3k4me3_sh]$gene_name %in% dsx_target_genes]

```

```{r}
de_genotype_rnapolii_gh_genes_id_dsx <- res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_gh]$gene_name %in% dsx_target_genes]

de_genotype_rnapolii_sh_genes_id_dsx <- res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$range_id[res_gr_rnapolii_genes[diff_ranges_rnapolii_sh]$gene_name %in% dsx_target_genes]

```

#### go
metabolism 
defense response
redox 
reproductive behavior 
feeding behavior 




# Venn diagram with (at least) three groups of DEGs:

## Make lists for different combinations of comparisons

```{r}
res_long_h3k4me3_df_any <- res_long_h3k4me3_df %>%
  drop_na(padj) %>%
  filter(padj < 0.01)
```

```{r}
res_long_rnapolii_df_any <- res_long_rnapolii_df %>%
  drop_na(padj) %>%
  filter(padj < 0.01)
```


## GH: all to CS

### All

```{r}
comp_list_genotype_gh_all_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_gh_all_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

```

### Up

```{r}
comp_list_genotype_gh_up_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_gh_up_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```

### Down

```{r}
comp_list_genotype_gh_down_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_gh_down_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"GH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_GH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```

## SH: all to CS

### All

```{r}
comp_list_genotype_sh_all_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_sh_all_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
    mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

```

### Up

```{r}
comp_list_genotype_sh_up_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_sh_up_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange > 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```

### Down

```{r}
comp_list_genotype_sh_down_h3k4me3_rangeid <- res_long_h3k4me3_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")

comp_list_genotype_sh_down_rnapolii_rangeid <- res_long_rnapolii_df_any %>%
  filter(str_detect(comparison,"SH_genotype_ashr")) %>%
  filter(log2FoldChange < 0) %>%
  mutate(range_id = paste0(seqnames,":",start,"-",end)) %>%
  dplyr::select(range_id, comparison) %>%
  mutate(comparison = str_remove(comparison, "_SH_genotype_ashr")) %>%
  split(.$comparison) %>%
  map("range_id")
```


# GO terms for different comparisons
```{r}
go_universe_h3k4me3 <- as.data.frame(unique(res_gr_h3k4me3_genes)) %>%
  pull(entrez_id) %>%
  unique()

go_universe_rnapolii <- as.data.frame(unique(res_gr_rnapolii_genes)) %>%
  pull(entrez_id) %>%
  unique()


```





# Read RNA data

# Read data

```{r}
data_dir <- "../data_output/2024-1_diffexpr_input/"
```

DESeq files raw
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```

DESeq files fitted 

```{r}
deseq_obj_fitted <- readRDS("../data_output/2024-1_diffexpr_output/social_mutants_housing_lrt_deseq_obj_fitted.Rds")
```

Results joined files

```{r}
res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```

# Data re-shaping

## Add entrezid column
```{r}
symbol_etrez_map_df <- clusterProfiler::bitr(geneID = res_df$gene_name, fromType = "SYMBOL",toType ="ENTREZID",OrgDb = org.Dm.eg.db )
symbol_etrez_map <- symbol_etrez_map_df$ENTREZ 
names(symbol_etrez_map) <-  symbol_etrez_map_df$SYMBOL

res_df$entrezid <- symbol_etrez_map[res_df$gene_name]

```


## Pivot Longer

### Data transform for volcano plots
```{r}
log2fc_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("log2FoldChange")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

rawlog2fc_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("rawlog2FoldChange")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "rawlog2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"rawlog2FoldChange_" ))

padj_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("padj")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("pvalue")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("baseMean")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long,rawlog2fc_long, log2fc_long, padj_long, pval_long)
res_long_df <- purrr::reduce(res_long_list,left_join,by =c("gene_name","entrezid","comparison") )
```

## Make lists for different combinations of comparisons


Get all genes that are diff expressed in at least one comparison
```{r}
res_long_df_diff_any <- res_long_df %>%
  drop_na(padj) %>%
  filter(padj < 0.01)
```

## LRT 

```{r}
comp_list_housing_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

res_long_df_diff_any %>%
  filter(str_detect(comparison,"interaction_lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")
  
```


## Housing within the same genotype

### All
```{r}
comp_list_housing_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")

```
### Up
```{r}
comp_list_housing_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

### Down
```{r}
comp_list_housing_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

## GH: all to CS

### All
```{r}

comp_list_genotype_gh_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

### Up
```{r}
comp_list_genotype_gh_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

### Down
```{r}
comp_list_genotype_gh_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

## SH: all to CS


### All
```{r}

comp_list_genotype_sh_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

### Up
```{r}
comp_list_genotype_sh_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

### Down
```{r}
comp_list_genotype_sh_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

## LRT housing by genotype
```{r}
comp_list_lrt_interaction_gene_name <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"social_mutants_interaction_lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_lrt_interaction_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"social_mutants_interaction_lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
  split(.$comparison) %>%
  map("entrezid")

```
## LRT housing 
```{r}
comp_list_lrt_housing_gene_name <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"social_mutants_housing_lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_lrt_housing_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"social_mutants_housing_lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
  split(.$comparison) %>%
  map("entrezid")

```

## LRT genotype 
```{r}
comp_list_lrt_genotype_gene_name <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"social_mutants_genotype_lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_lrt_genotype_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"social_mutants_genotype_lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
  split(.$comparison) %>%
  map("entrezid")

```

# Venn diagram with comparisons:
 
## GH: all to CS, within the same genotype between RNAseq and CUT&RUN
```{r}

tr_range2gene <- function(res_id,gr_obj) {
  unique(gr_obj$gene_name[names(gr_obj) %in% res_id])
}
# Translate list gh all
comp_list_genotype_gh_all_h3k4me3_geneid <- map(comp_list_genotype_gh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list_genotype_gh_all_rnapolii_geneid <- map(comp_list_genotype_gh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list_genotype_gh_all_cutnrun_rna_list <- c(comp_list_genotype_gh_all_symbol,comp_list_genotype_gh_all_h3k4me3_geneid, comp_list_genotype_gh_all_rnapolii_geneid)

# Translate list gh up
comp_list_genotype_gh_up_h3k4me3_geneid <- map(comp_list_genotype_gh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list_genotype_gh_up_rnapolii_geneid <- map(comp_list_genotype_gh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list_genotype_gh_up_cutnrun_rna_list <- c(comp_list_genotype_gh_up_symbol,comp_list_genotype_gh_up_h3k4me3_geneid,comp_list_genotype_gh_up_rnapolii_geneid)

# Translate list gh down
comp_list_genotype_gh_down_h3k4me3_geneid <- map(comp_list_genotype_gh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list_genotype_gh_down_rnapolii_geneid <- map(comp_list_genotype_gh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list_genotype_gh_down_cutnrun_rna_list <- c(comp_list_genotype_gh_down_symbol,comp_list_genotype_gh_down_h3k4me3_geneid,comp_list_genotype_gh_down_rnapolii_geneid)

# Translate list sh all
comp_list_genotype_sh_all_h3k4me3_geneid <- map(comp_list_genotype_sh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list_genotype_sh_all_rnapolii_geneid <- map(comp_list_genotype_sh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list_genotype_sh_all_cutnrun_rna_list <- c(comp_list_genotype_sh_all_symbol,comp_list_genotype_sh_all_h3k4me3_geneid,comp_list_genotype_sh_all_rnapolii_geneid)

# Translate list sh up
comp_list_genotype_sh_up_h3k4me3_geneid <- map(comp_list_genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list_genotype_sh_up_rnapolii_geneid <- map(comp_list_genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list_genotype_sh_up_cutnrun_rna_list <- c(comp_list_genotype_sh_up_symbol,comp_list_genotype_sh_up_h3k4me3_geneid,comp_list_genotype_sh_up_rnapolii_geneid)

# Translate list sh down
comp_list_genotype_sh_down_h3k4me3_geneid <- map(comp_list_genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list_genotype_sh_down_rnapolii_geneid <- map(comp_list_genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list_genotype_sh_down_cutnrun_rna_list <- c(comp_list_genotype_sh_down_symbol,comp_list_genotype_sh_down_h3k4me3_geneid,comp_list_genotype_sh_down_rnapolii_geneid)


# Translate list gh down
comp_list_genotype_sh_down_h3k4me3_geneid <- map(comp_list_genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list_genotype_sh_down_rnapolii_geneid <- map(comp_list_genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list_genotype_sh_down_cutnrun_rna_list <- c(comp_list_genotype_sh_down_symbol,comp_list_genotype_sh_down_h3k4me3_geneid,comp_list_genotype_sh_down_rnapolii_geneid)



```

```{r}
# Combine RNA and chromatin lists 
comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list <- c(comp_list_lrt_interaction_gene_name,comp_list_genotype_gh_all_h3k4me3_geneid, comp_list_genotype_gh_all_rnapolii_geneid)

comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list <- c(comp_list_lrt_interaction_gene_name,comp_list_genotype_sh_all_h3k4me3_geneid, comp_list_genotype_sh_all_rnapolii_geneid)

comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list <- c(comp_list_lrt_housing_gene_name,comp_list_genotype_gh_all_h3k4me3_geneid, comp_list_genotype_gh_all_rnapolii_geneid)

comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list <- c(comp_list_lrt_housing_gene_name,comp_list_genotype_sh_all_h3k4me3_geneid, comp_list_genotype_sh_all_rnapolii_geneid)

comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list <- c(comp_list_lrt_genotype_gene_name,comp_list_genotype_gh_all_h3k4me3_geneid, comp_list_genotype_gh_all_rnapolii_geneid)

comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list <- c(comp_list_lrt_genotype_gene_name,comp_list_genotype_sh_all_h3k4me3_geneid, comp_list_genotype_sh_all_rnapolii_geneid)

```



### ALL 

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_list)
```

``


```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))
```

Genes 
```{r}
get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```

### UP 

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
get_overlap_genes(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut))

```


```{r}
get_overlap_genes(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```


```{r}
get_overlap_genes(comp_list_genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_up_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```


### DOWN 

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))
```
```{r}
get_overlap_genes(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut))

```


```{r}
get_overlap_genes(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```


```{r}
get_overlap_genes(comp_list_genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_gh_down_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```
## SH: all to a CS, within the same genotype between RNAseq and CUT&RUN

### ALL 

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_list)
```


```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))
```

Genes 
```{r}
get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```



### UP 

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh UP") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
get_overlap_genes(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_up_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```



### DOWN 

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
get_overlap_genes(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list_genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list_genotype_sh_down_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```



## Comparison of RNAseq LRT genotype:housing genes vs mutants CUT&RUN

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_interaction_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```


```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```


```{r}
get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_interaction_list),"dsx|DSX|lrt")]) %>%
  filter(social_mutants_interaction_lrt & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```


## Comparison of RNAseq LRT housing genes vs mutants CUT&RUN

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_housing_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```


```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_housing_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```

## Comparison of RNAseq LRT genotype genes vs mutants CUT&RUN

```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```



```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes <- get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_dsxmut | RNAPolII_dsxmut))

comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes %>%
  filter(H3K4me3_dsxmut)
```


```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go <- enrichGO(rownames(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


```




```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes <- get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_frumut | RNAPolII_frumut))

comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes
```


```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go <- enrichGO(rownames(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go)
```

```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go@result
```


```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes <- get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes
```


```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go <- enrichGO(rownames(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go)
```

```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go@result
```



```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes <- get_overlap_genes(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes
```

```{r}
comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go <- enrichGO(rownames(comp_list_genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


```




```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```
```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes <- get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_dsxmut | RNAPolII_dsxmut))

comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes %>%
  filter(H3K4me3_dsxmut)
```


```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go <- enrichGO(rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go)
```

```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go@result
```


```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes <- get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_frumut | RNAPolII_frumut))

comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes
```


```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go <- enrichGO(rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go)
```

```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go@result
```


```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes <- get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes
```


```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go <- enrichGO(rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go)
```

```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go@result
```



```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes <- get_overlap_genes(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes
```

```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go <- enrichGO(rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go)
```
```{r}
comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go@result
```


# GO terms of any overlaps above:

```{r}

comp_list_genotype_gh_all_cutnrun_rna_list_entrezid <- map(comp_list_genotype_gh_all_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list_genotype_gh_up_cutnrun_rna_list_entrezid <- map(comp_list_genotype_gh_up_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list_genotype_gh_down_cutnrun_rna_list_entrezid <- map(comp_list_genotype_gh_down_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list_genotype_sh_all_cutnrun_rna_list_entrezid <- map(comp_list_genotype_sh_all_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list_genotype_sh_up_cutnrun_rna_list_entrezid <- map(comp_list_genotype_gh_up_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list_genotype_sh_down_cutnrun_rna_list_entrezid <- map(comp_list_genotype_gh_down_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

```

### GH

#### ALL 

```{r}
comp_list_genotype_gh_all_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list_genotype_gh_all_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list_genotype_gh_all_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS GH ALL")
```

#### UP 

```{r}
comp_list_genotype_gh_up_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list_genotype_gh_up_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list_genotype_gh_up_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS GH UP")
```

#### Down 

```{r}
comp_list_genotype_gh_down_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list_genotype_gh_down_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list_genotype_gh_down_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS GH DOWN")
```

### SH

#### ALL 

```{r}
comp_list_genotype_sh_all_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list_genotype_sh_all_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list_genotype_sh_all_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS SH ALL")
```

#### UP 

```{r}
comp_list_genotype_sh_up_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list_genotype_sh_up_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list_genotype_sh_up_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS SH UP")
```

#### Down 

```{r}
comp_list_genotype_sh_down_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list_genotype_sh_down_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list_genotype_sh_down_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS SH DOWN")
```

```{r}
gene_mat <- get_overlap_genes(list("dsx" = rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes),
"fru" = rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes),
"Or67d" = rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes),
"Or47b" = rownames(comp_list_genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes))) %>%
  filter(rowSums(.)>=2)
gene_names_row_mat <- rownames(gene_mat)

gene_mat <- map_dfc(gene_mat, as.numeric) 
rownames(gene_mat) <-  gene_names_row_mat 


Heatmap(gene_mat %>%
  arrange(Or67d,Or47b),col = c("white","black"), cluster_rows = FALSE,cluster_columns = FALSE ) 

```


# Get tables for overlap genes




# Specific genes of any overlaps above:
## TPM or normed counts +p
## GVI view + stats