---
title: "GO term heatmaps"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```


```{r}
# Libraries

library(ComplexHeatmap) # Heatmaps
library(DESeq2) 
library(ggVennDiagram) 
library(clusterProfiler) # Go terms
library(org.Dm.eg.db) # GO annotation
library(tidyverse)
library(circlize) # Colors
```


```{r}
# Functions

# plot z score matrix
plot_heatmap <- function(mat, ...) {
  Heatmap(mat = t(scale(t(mat),center = TRUE,scale = TRUE)), # z score
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), ... )
}
# log2fc matrix
plot_heatmap_log2fc <- function(mat, ...) {
  Heatmap(mat = mat,
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "log2FC",
                                      legend_height = unit(2, "in")) , ... )
}


```

```{r}
data_dir <- "../data_output/2024-1_diffexpr_input/"
```


```{r}
#DESeq files raw
deseq_files <- list.files(data_dir,pattern = "[^$]+rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```



```{r}
#DESeq files fitted 
deseq_obj_fitted <- readRDS("../data_output/2024-1_diffexpr_output/social_mutants_housing_lrt_deseq_obj_fitted.Rds")
```

```{r}
# Results joined files

res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```


```{r}
# Data re-shaping

## Add entrezid column

symbol_etrez_map_df <- clusterProfiler::bitr(geneID = res_df$gene_name, fromType = "SYMBOL",toType ="ENTREZID",OrgDb = org.Dm.eg.db )
symbol_etrez_map <- symbol_etrez_map_df$ENTREZ 
names(symbol_etrez_map) <-  symbol_etrez_map_df$SYMBOL

res_df$entrezid <- symbol_etrez_map[res_df$gene_name]

```


```{r}
# Pivot Longer

## Data transform for volcano plots

log2fc_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("log2FoldChange")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

rawlog2fc_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("rawlog2FoldChange")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "rawlog2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"rawlog2FoldChange_" ))

padj_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("padj")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("pvalue")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("baseMean")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long,rawlog2fc_long, log2fc_long, padj_long, pval_long)
res_long_df <- purrr::reduce(res_long_list,left_join,by =c("gene_name","entrezid","comparison") )
```

```{r}

# Make lists for different combinations of comparisons


# Get all genes that are diff expressed in at least one comparison


res_long_df_diff_any <- res_long_df %>%
  drop_na(padj) %>%
  filter(padj < 0.05 & abs(log2FoldChange) > 0.2)
```

```{r}
# Housing within the same genotype

## All


comp_list_housing_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

```{r}

## Up

comp_list_housing_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")

```


```{r}
## Down

comp_list_housing_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

```{r}
## GH: all to CS

### All

comp_list_genotype_gh_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

```{r}

### Up

comp_list_genotype_gh_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

```{r}
### Down

comp_list_genotype_gh_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

```{r}

## SH: all to CS


### All

comp_list_genotype_sh_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

```{r}

### Up

comp_list_genotype_sh_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

```{r}
### Down

comp_list_genotype_sh_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```


```{r}
# Heatmaps:

## Data re-shaping

### Build norm counts z score matrix

norm_cts <- counts(deseq_obj_fitted,norm =TRUE)
```

```{r}
de_cs_genes_id <- res_long_df %>%
  dplyr::select(gene_name, comparison, padj, log2FoldChange) %>%
  filter(comparison == "CS_housing") %>%
  filter(padj < 0.05 & abs(log2FoldChange) > 0.2) %>%
  arrange(log2FoldChange) %>%
  pull(gene_name) %>%
  unique()

de_genotype_gh_genes_id <- res_long_df %>%
  dplyr::select(gene_name, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "GH_genotype")) %>%
  filter(padj < 0.05 & abs(log2FoldChange) > 0.2) %>%
  pull(gene_name) %>%
  unique()

de_genotype_sh_genes_id <- res_long_df %>%
  dplyr::select(gene_name, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "SH_genotype")) %>%
  filter(padj < 0.05 & abs(log2FoldChange) > 0.2) %>%
  pull(gene_name) %>%
  unique()

```


```{r}
# Norm counts median per group


# Remove rows with zero counts
norm_cts_filt <- norm_cts[rowSums(norm_cts) > 0,]

# Get mean matrix
norm_cts_median <- as.data.frame(norm_cts_filt) %>% # convert matrix to data frame, makes it compatible with dplyr
  rownames_to_column(var = "gene_symbol") %>% # move rownames to a new column, makes it compatible with dplyr 
  pivot_longer(cols = -gene_symbol, # make data.frame in tidy format
               names_to = "sample_name",
               values_to = "normalizedCounts") %>% 
  mutate(condition = str_remove(sample_name, "_R\\d$")) %>% # Make condition variables 
  group_by(gene_symbol, condition) %>% # Group by experimental condition 
  summarise(normalizedCounts_median = median(normalizedCounts)) %>% # Calculate mean per groups 
  pivot_wider(names_from = condition, # Return from tidy to matrix format 
              values_from = normalizedCounts_median)
# process matrix further as a numeric matrix format with rownames, compatible with ComplexHeatmap
norm_cts_median <- as.data.frame(norm_cts_median) 
rownames(norm_cts_median) <- norm_cts_median$gene_symbol
norm_cts_median <- norm_cts_median %>%
  dplyr::select(- gene_symbol)
norm_cts_median <- as.matrix(norm_cts_median)

# Get factor with genotype info to use to separate heatmap into subsections
genotype_split <-  str_split(colnames(norm_cts_median),"_",n = 2) %>% map_chr(1)

```

```{r}
### Build log2Fold change matrix
# Select only log2FoldChane variables

log2fc_mat_housing <- res_df %>%
  drop_na(padj_CS_housing) %>%
  filter(padj_CS_housing < 0.05 & abs(log2FoldChange_CS_housing) > 0.2) %>%
  dplyr::select(gene_name, starts_with("log2FoldChange") & contains("housing") & ! contains("lrt")) %>%
  arrange(log2FoldChange_CS_housing) %>%
  column_to_rownames(var = "gene_name") %>%
  as.matrix()

log2fc_mat_genotype_gh<- res_df %>%
    filter(padj_DSX_GH_genotype < 0.05 | 
           padj_FRU_GH_genotype < 0.05 |
           padj_Or67d_GH_genotype < 0.05 |
           padj_Or47b_GH_genotype) %>%
  dplyr::select(gene_name, starts_with("log2FoldChange") & contains("GH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "gene_name") %>%
  as.matrix()

log2fc_mat_genotype_sh<- res_df %>%
      filter(padj_DSX_SH_genotype < 0.05 | 
           padj_FRU_SH_genotype < 0.05 |
           padj_Or67d_SH_genotype < 0.05 |
           padj_Or47b_SH_genotype) %>%
  dplyr::select(gene_name, starts_with("log2FoldChange") & contains("SH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "gene_name") %>%
  as.matrix()

colnames(log2fc_mat_housing) <- str_remove(colnames(log2fc_mat_housing) ,"log2FoldChange_")
colnames(log2fc_mat_housing) <- str_remove(colnames(log2fc_mat_housing) ,"_housing")

colnames(log2fc_mat_genotype_gh) <- str_remove(colnames(log2fc_mat_genotype_gh) ,"log2FoldChange_")
colnames(log2fc_mat_genotype_gh) <- str_remove(colnames(log2fc_mat_genotype_gh) ,"_genotype")

colnames(log2fc_mat_genotype_sh) <- str_remove(colnames(log2fc_mat_genotype_sh) ,"log2FoldChange_")
colnames(log2fc_mat_genotype_sh) <- str_remove(colnames(log2fc_mat_genotype_sh) ,"_genotype")
```


```{r}
### Read target genes

#### go


symbol_ensembl_map_df <- clusterProfiler::bitr(geneID = res_df$gene_name, fromType = "SYMBOL",toType ="ENSEMBL",OrgDb = org.Dm.eg.db )
symbol_ensembl_map <- symbol_ensembl_map_df$SYMBOL 
names(symbol_ensembl_map) <-  symbol_ensembl_map_df$ENSEMBL




```



```{r}
# autophagy

autophagy_genes <- readLines("../data_input/gene_annotations/2024-02_autophagy_stress_response_go_terms/autophagy_go_terms.txt")

autophagy_genes <- symbol_ensembl_map[autophagy_genes]
autophagy_genes <- na.omit(autophagy_genes)
autophagy_genes <- autophagy_genes[autophagy_genes %in% res_df$gene_name]

```


```{r}
# stress response

oxidative_stress_esponse_genes <- readLines("../data_input/gene_annotations/2024-02_autophagy_stress_response_go_terms/response_to_oxidative_stress_go_terms.txt")
oxidative_stress_esponse_genes <- symbol_ensembl_map[oxidative_stress_esponse_genes]

oxidative_stress_esponse_genes <- na.omit(oxidative_stress_esponse_genes)

oxidative_stress_esponse_genes <- oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% res_df$gene_name]

```


```{r}
# ribosomal proteins

ribosomal_genes <- readLines("../data_input/gene_annotations/2024-02_autophagy_stress_response_go_terms/ribosomal_subunit_go_terms.txt")
ribosomal_genes <- symbol_ensembl_map[ribosomal_genes]

ribosomal_genes <- na.omit(ribosomal_genes)

ribosomal_genes <- ribosomal_genes[ribosomal_genes %in% res_df$gene_name]

```

# GO annotations

Annotations for go terms were obtained from:

Autophagy: https://flybase.org/cgi-bin/cvreport.pl?rel=is_a&id=GO:0006979

Response to oxidative stress: https://flybase.org/cgi-bin/cvreport.pl?rel=is_a&id=GO:0006979

Ribosomal subunit: https://flybase.org/cgi-bin/cvreport.pl?rel=is_a&id=GO:0044391


# Comparison: Housing SH/GH

The following heatmaps show Differential genes CantonS SH / CantonS GH, subset by whether they are annotated with a specific GO category.

Genes are considered differentially expressed if they are adjusted p value < 0.05, and absolute log2 fold change > 0.2.

## Z score matrix

Replicates were merged summarizing by the median per experimental group.

### autophagy


```{r }

plot_heatmap(norm_cts_median[autophagy_genes[autophagy_genes %in% de_cs_genes_id],], show_row_names = TRUE, cluster_rows = TRUE, column_title = "Autophagy\n CS_SH / CS_GH differentially expressed genes")

```

### oxidative stress response

```{r }

plot_heatmap(norm_cts_median[oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% de_cs_genes_id],,drop = FALSE], show_row_names = TRUE, cluster_rows = TRUE,  column_title = "Oxidative Stress Response \n CS_SH / CS_GH differentially expressed genes")

```

### ribosomal proteins

```{r }

plot_heatmap(norm_cts_median[ribosomal_genes[ribosomal_genes %in% de_cs_genes_id],,drop = FALSE], show_row_names = TRUE, cluster_rows = TRUE,  column_title = "Ribosomal Proteins \n CS_SH / CS_GH differentially expressed genes")

```

## log2FoldChange matrix

### autophagy

```{r fig.height= 3}

plot_heatmap_log2fc(log2fc_mat_housing[autophagy_genes[autophagy_genes %in% de_cs_genes_id],,drop = FALSE],
                    cluster_rows = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE, column_title = "Autophagy\n CS_SH / CS_GH differentially expressed genes")
```

### oxidative stress response

```{r fig.height= 3}

plot_heatmap_log2fc(log2fc_mat_housing[oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% de_cs_genes_id],,drop = FALSE],
                    cluster_rows = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE,  column_title = "Oxidative Stress Response \n CS_SH / CS_GH differentially expressed genes")
```

### ribosomal proteins

```{r fig.height= 3}

plot_heatmap_log2fc(log2fc_mat_housing[ribosomal_genes[ribosomal_genes %in% de_cs_genes_id],,drop = FALSE],
                    cluster_rows = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE,  column_title = "Ribosomal Proteins \n CS_SH / CS_GH differentially expressed genes")
```


# Comparison: each mutant GH vs CantonS GH

The following heatmaps show Differential genes Mutant GH / CantonS GH, subset by whether they are annotated with a specific GO category.

## Z score matrix

### autophagy

```{r fig.height= 7}
plot_heatmap(norm_cts_median[autophagy_genes[autophagy_genes %in% de_genotype_gh_genes_id],], show_row_names = TRUE, cluster_rows = TRUE, column_title = "Autophagy\n Mutant_GH / CS_GH differentially expressed genes")

```

### oxidative stress response

```{r fig.height= 8}
plot_heatmap(norm_cts_median[oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% de_genotype_gh_genes_id],], show_row_names = TRUE, cluster_rows = TRUE, column_title = "Oxidative stress response Mutant_GH / CS_GH differentially expressed genes")

```

### ribosomal proteins

```{r fig.height= 7}
plot_heatmap(norm_cts_median[ribosomal_genes[ribosomal_genes %in% de_genotype_gh_genes_id],], show_row_names = TRUE, cluster_rows = TRUE, column_title = "Ribosomal proteins \n Mutant_GH / CS_GH differentially expressed genes")

```

## log2FoldChange matrix

### autophagy

```{r fig.height= 7}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[autophagy_genes[autophagy_genes %in% de_genotype_gh_genes_id],],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE, column_title = "Autophagy\n Mutant_GH / CS_GH differentially expressed genes")
```

### oxidative stress response

```{r fig.height= 8}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% de_genotype_gh_genes_id],],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE, column_title = "Oxidative stress response \n Mutant_GH / CS_GH differentially expressed genes")
```

### ribosomal proteins

```{r fig.height= 7}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[ribosomal_genes[ribosomal_genes %in% de_genotype_gh_genes_id],],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE, column_title = "Ribosomal proteins \n Mutant_GH / CS_GH differentially expressed genes")
```

# Comparison: each mutant SH vs CantonS SH

The following heatmaps show Differential genes Mutant SH / CantonS SH, subset by whether they are annotated with a specific GO category

## Z score matrix

### autophagy

```{r fig.height= 10}
plot_heatmap(norm_cts_median[autophagy_genes[autophagy_genes %in% de_genotype_sh_genes_id],], show_row_names = TRUE, cluster_rows = TRUE, column_title = "Autophagy\n Mutant_SH / CS_SH differentially expressed genes")

```

### oxidative stress response

```{r fig.height= 10}
plot_heatmap(norm_cts_median[oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% de_genotype_sh_genes_id],], show_row_names = TRUE, cluster_rows = TRUE, column_title = "Oxidative stress response \n Mutant_SH / CS_SH differentially expressed genes")

```

### ribosomal proteins

```{r fig.height= 10}
plot_heatmap(norm_cts_median[ribosomal_genes[ribosomal_genes %in% de_genotype_sh_genes_id],], show_row_names = TRUE, cluster_rows = TRUE, column_title = "Ribosomal proteins \n Mutant_SH / CS_SH differentially expressed genes")

```

## log2FoldChange matrix

### autophagy

```{r fig.height= 10}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[autophagy_genes[autophagy_genes %in% de_genotype_sh_genes_id],],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE, column_title = "Autophagy\n Mutant_SH / CS_SH differentially expressed genes")
```

### oxidative stress response

```{r fig.height= 9}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% de_genotype_sh_genes_id],],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE, column_title = "Oxidative stress response \n Mutant_SH / CS_SH differentially expressed genes")
```

### ribosomal proteins

```{r fig.height= 10}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[ribosomal_genes[ribosomal_genes %in% de_genotype_sh_genes_id],],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE, column_title = "Ribosomal proteins \n Mutant_SH / CS_SH differentially expressed genes")
```

# DESEQ2 Results for each gene

Annotations for go terms were obtained from:

Autophagy: https://flybase.org/cgi-bin/cvreport.pl?rel=is_a&id=GO:0006979

Response to oxidative stress: https://flybase.org/cgi-bin/cvreport.pl?rel=is_a&id=GO:0006979

Ribosomal subunit: https://flybase.org/cgi-bin/cvreport.pl?rel=is_a&id=GO:0044391


## Autophagy

```{r}
res_df %>%
  filter(gene_name %in% autophagy_genes) %>%
  filter(padj_CS_housing <0.05 & abs(log2FoldChange_CS_housing ) > 0.2)
```

## Response to oxidative stress

```{r}
res_df %>%
  filter(gene_name %in% oxidative_stress_esponse_genes)
```

## Ribosomal subunit
```{r}
res_df %>%
  filter(gene_name %in% ribosomal_genes)
```
