---
title: "Bulk_RNAseq_fixed_and_clean"
author: "Chengcheng Du"
date: "2025-02-02"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r}
# Libraries
library(ComplexHeatmap) # Heatmaps
library(DESeq2) 
library(ggVennDiagram) 
library(clusterProfiler) # Go terms
library(org.Dm.eg.db) # GO annotation
library(tidyverse)
library(circlize) # Colors
library(ggfortify)
library(ggalt)
library(enrichplot)
library(ggplot2)
library(patchwork)
library(dplyr)
library(cowplot)

options(scipen = 999)
```

```{r}
# Functions
# plot z score matrix
plot_heatmap <- function(mat, plot_title, ...) {
  ComplexHeatmap::Heatmap(mat = t(scale(t(mat),center = TRUE,scale = TRUE)), # z score
          column_title = plot_title,
                          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
          raster_device = "agg_png", # Format to export the raster 
          ... ) 
}
# log2fc matrix
plot_heatmap_log2fc <- function(mat, ...) {
  ComplexHeatmap::Heatmap(mat = mat,
          heatmap_legend_param = list(title = "log2FC",
                                      legend_height = unit(2, "in")) , 
           raster_device = "agg_png", ... )
}

# Single gene plot
plot_norm_counts <- function(gene, dds) {
  DESeq2::plotCounts(gene, 
                     dds = dds,
                     transform = FALSE, # Don't plot y axis as log scale
                     returnData = TRUE, # Returns data frame instead of plot
                     intgroup = c("condition","genotype","housing","dissection")) %>% # Keep Sample info columns from dds and add to return data 
    mutate(genotype = factor(genotype, levels = c("CS","Or47b", "Or67d", "FRU", "DSX"))) %>%
    ggplot(aes(housing, count, color = condition)) +
    geom_jitter(width = 0.2, alpha = 0.7) + # Points 
    stat_summary() + # Mean 
    scale_color_manual(values = c("CS_GH" = "#76A3FE", 
                                "CS_SH" = "#9ACEFE",
                                "Or47b_GH" = "#12A012",
                                "Or47b_SH" = "#9DCF0C",
                                "Or67d_GH" = "#FE7A21",
                                "Or67d_SH" = "#FEA51F",
                                "FRU_GH" = "#0E9E9E",
                                "FRU_SH" = "#01CDCD",
                                "DSX_GH" = "#9B069B",
                                "DSX_SH" = "#CD0199"))+
    facet_grid(cols = vars(genotype)) +
    theme_light() +
    theme(aspect.ratio = 1, legend.position = "none") +
    ylab("Normalized Counts") +
    xlab(NULL) +
    ylim(0, NA) +
    ggtitle(gene) 
  
}


# Plot behavior data vs counts daa 
plot_regression_gene <- function(gene_name, dds) {
  
  counts_mat <- DESeq2::plotCounts(gene_name,dds = dds, transform = FALSE,
                                   intgroup = "CI", # Return Courtship index column also
                                   returnData = TRUE) # Get dataframe for gene counts 
  col_data <- as.data.frame(colData(dds)) # Get all sample information from dds transform to regular data frame
  col_data[,gene_name] <- counts_mat$count # Adding gene counts info 
  
  col_data_mean <- col_data %>% # Mean Courtship Index and counts per group
    group_by(genotype, housing) %>%
    summarise(mean_count = mean(.data[[gene_name]]), # Mean counts RNAseq
              mean_behavior = mean(CI)) %>% # Mean CI 
    ungroup()
  
  # Plot 
  col_data_mean %>%
    ggplot(aes(mean_count, mean_behavior)) + 
    geom_point(size = 3, aes(color = paste( genotype , housing))) +
    geom_smooth(color = "gray", method = "lm", se = FALSE) + # Regression line 
    ggtitle(gene_name) +
    xlab("Normalized Counts") +
    ylab("Courtship Index") +
    theme_classic() +
    theme(aspect.ratio = 1,legend.title = element_blank()) +
    ggpubr::stat_cor(
      aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))
    ) # Add stats to plot
}

# Get correlation of counts and courtship index for a given gene 
get_ci_counts_cor <- function(gene_name, dds) {
  col_data <- as.data.frame(colData(dds))
  counts_mat <- DESeq2::plotCounts(gene_name,dds = dds, transform = FALSE, intgroup = "CI", returnData = TRUE)
  
  col_data[,gene_name] <- counts_mat$count
  
  # Get correlation (pearson r)
  cor_res <- (col_data %>%
                group_by(genotype, housing) %>%
                summarise(mean_count = mean(.data[[gene_name]]),
                          mean_behavior = mean(CI)) %>%
                ungroup() %>%
                dplyr::select(starts_with("mean")) %>%
                cor())[1,2] # cor is the function for pearson r
  
  return(cor_res)
}

# Function to make table exportable in the html file 
print_go_table <- function(go_table){ 
  DT::datatable(go_table,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))} # Export as csv


#Plot GO with sign   
plot_go_terms_by_cluster <- function(go_df, cluster_order = NULL, plot_title = NULL) {
  # Step 1: Split and clean
  clusters <- split(go_df, go_df$Cluster)
  clusters <- clusters[sapply(clusters, function(df) {
    nrow(df) > 0 &&
      all(c("dummy_x", "Description", "GeneRatio", "p.adjust") %in% colnames(df)) &&
      any(!is.na(df$Description)) && any(!is.na(df$GeneRatio))
  })]

  # Optional: Custom cluster order
  if (!is.null(cluster_order)) {
    clusters <- clusters[cluster_order[cluster_order %in% names(clusters)]]
  }

  # Global color scale limits (fixed across all panels)
  global_min <- min(go_df$p.adjust, na.rm = TRUE)
  global_max <- max(go_df$p.adjust, na.rm = TRUE)

  # Step 2: Calculate heights
  heights <- sapply(clusters, nrow)
  heights <- heights / sum(heights)

  # Step 3: Create label panels
  label_plots <- lapply(names(clusters), function(cluster_name) {
    ggplot() +
      annotate("text", x = 0, y = 0, label = cluster_name,
               hjust = 0, vjust = 0.5, size = 3, fontface = "bold") +
      xlim(0, 1) +
      theme_void() +
      theme(plot.margin = margin(1, 1, 1, 1))
  })

  # Step 4: Create data plots with global color scale
  data_plots <- mapply(function(df, cluster_name) {
    df$Description <- reorder(df$Description, df$GeneRatio)

    ggplot(df, aes(x = dummy_x, y = Description)) +
      geom_point(aes(size = GeneRatio, color = p.adjust)) +
      scale_size(range = c(2, 5)) +
      scale_y_discrete(position = "right", labels = function(x) str_wrap(x, width = 50)) +
      scale_color_gradient(low = "red", high = "blue", limits = c(global_min, global_max)) +
      theme_minimal() +
      theme(
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 12),
        panel.border = element_rect(color = "grey", fill = NA, linewidth = 0.5),
        plot.margin = margin(0.5, 5, 0.5, 5)
      )
  }, clusters, names(clusters), SIMPLIFY = FALSE)

  # Step 5: Shared legend with same scale
  legend_plot <- ggplot(go_df, aes(x = dummy_x, y = reorder(Description, GeneRatio))) +
    geom_point(aes(size = GeneRatio, color = p.adjust)) +
    scale_color_gradient(low = "red", high = "blue", limits = c(global_min, global_max)) +
    theme_minimal() +
    theme(legend.position = "right")
  legend <- cowplot::get_legend(legend_plot)

  # Step 6: Layout
  left_col   <- wrap_plots(label_plots, ncol = 1, heights = heights)
  center_col <- wrap_plots(data_plots,  ncol = 1, heights = heights)

  main_plot <- (left_col | center_col | wrap_elements(full = legend)) +
    plot_layout(widths = c(0.6, 0.2, 0.2))

  # Step 7: Title
  if (!is.null(plot_title)) {
    final_plot <- main_plot + plot_annotation(title = plot_title)
  } else {
    final_plot <- main_plot
  }

  return(final_plot)
}

```

```{r}
# Color scheme
color_scheme <- list()
color_scheme$cs_gh <- "#76A3FE"
color_scheme$cs_sh <- "#9ACEFE"
color_scheme$Or47b_gh <- "#12A012"
color_scheme$Or47b_sh <- "#9DCF0C"
color_scheme$Or67d_gh <- "#FE7A21"
color_scheme$Or67d_sh <- "#FEA51F"
color_scheme$fru_gh <- "#0E9E9E"
color_scheme$fru_sh <- "#01CDCD"
color_scheme$dsx_gh <- "#9B069B"
color_scheme$dsx_sh <- "#CD0199"

```

```{r}
# Read data
# deseq obj
deseq_obj_fitted <- readRDS("../data_output/2024-1_diffexpr_output/deseq_obj_fitted_annotated.Rds")

```

```{r}
# Results joined files
res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```


```{r}
# VST for PCA
vsd_combat <- readRDS("../data_output/2024-1_diffexpr_output/vsd_combat.Rds")
```

```{r}
# Re-shaped data
# res_long_df
res_long_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/res_long_df.Rds")

res_long_df$comparison <- factor(res_long_df$comparison, levels = c("CS_housing","Or47b_housing", "Or67d_housing","FRU_housing", "DSX_housing", "Or47b_GH_genotype", "Or67d_GH_genotype", "FRU_GH_genotype", "DSX_GH_genotype", "Or47b_SH_genotype", "Or67d_SH_genotype", "FRU_SH_genotype", "DSX_SH_genotype", "social_mutants_housing_lrt", "social_mutants_genotype_lrt","social_mutants_interaction_lrt"))


# Lists of differentially expressed genes by comparison 
comp_list <- readRDS(file = "../data_output/2024-1_diffexpr_output/comp_list.Rds")


# Counts matrix for heatmaps
norm_cts <- readRDS(file = "../data_output/2024-1_diffexpr_output/norm_cts.Rds")
norm_cts_median <- readRDS(file = "../data_output/2024-1_diffexpr_output/norm_cts_median.Rds")
norm_cts_median <- norm_cts_median[, c("CS_GH","CS_SH","Or47b_GH","Or47b_SH","Or67d_GH","Or67d_SH","FRU_GH","FRU_SH","DSX_GH","DSX_SH")] 

log2fc_mat_housing <- readRDS(file = "../data_output/2024-1_diffexpr_output/log2fc_mat_housing.Rds")
log2fc_mat_genotype_gh <- readRDS(file = "../data_output/2024-1_diffexpr_output/log2fc_mat_genotype_gh.Rds")
log2fc_mat_genotype_sh <- readRDS(file = "../data_output/2024-1_diffexpr_output/log2fc_mat_genotype_sh.Rds")
```


```{r}
# Pairwise comparison data for LRT significant genes

pairwise_log2fc_interaction_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/pairwise_log2fc_interaction_df.Rds")
pairwise_log2fc_housing_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/pairwise_log2fc_housing_df.Rds")
pairwise_log2fc_genotype_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/pairwise_log2fc_genotype_df.Rds")

```


```{r}
# Pairwise comparison data for ashr significant genes
pairwise_log2fc_genotype_df_ashr_GH <- readRDS("../data_output/2024-1_diffexpr_output/pairwise_log2fc_genotype_df_ashr_GH.Rds")

pairwise_log2fc_genotype_df_ashr_SH <- readRDS("../data_output/2024-1_diffexpr_output/pairwise_log2fc_genotype_df_ashr_SH.Rds")
```



```{r}
#Enriched go terms

go_housing <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_housing.Rds")
go_genotype <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_genotype.Rds")

go_housing_all_simplify <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_housing_all_simplify.Rds")
go_genotype_gh_all_simplify <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_genotype_gh_all_simplify.Rds")
go_genotype_sh_all_simplify <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_genotype_sh_all_simplify.Rds")
go_housing_CS_simplify <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_housing_CS_simplify.Rds")

go_Ashr_sign_GH_simplify <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_Ashr_sign_GH_simplify.Rds")
go_Ashr_sign_SH_simplify <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_Ashr_sign_SH_simplify.Rds")

go_Ashr_sign_target <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_Ashr_sign_target.Rds")

go_Ashr_sign_SH_simplify_target <- readRDS(file =  "../data_output/2024-1_diffexpr_output/go_Ashr_sign_SH_simplify_target.Rds")

go_Ashr_sign_GH_simplify_target <- readRDS(file =  "../data_output/2024-1_diffexpr_output/go_Ashr_sign_GH_simplify_target.Rds")


go_lrt <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_lrt.Rds")
go_lrt_interaction_simplify <- readRDS("../data_output/2024-1_diffexpr_output/go_lrt_interaction_simplify.Rds")

```

```{r}
#Enriched reactome terms

reactome_housing <- readRDS(file = "../data_output/2024-1_diffexpr_output/reactome_housing.Rds")
reactome_genotype <- readRDS(file = "../data_output/2024-1_diffexpr_output/reactome_genotype.Rds")
reactome_lrt <- readRDS(file = "../data_output/2024-1_diffexpr_output/reactome_lrt.Rds")

```

```{r}
#Enriched KEGG terms

KEGG_housing <- readRDS(file = "../data_output/2024-1_diffexpr_output/kegg_housing.Rds")
KEGG_genotype <- readRDS(file = "../data_output/2024-1_diffexpr_output/kegg_genotype.Rds")
KEGG_lrt <- readRDS(file = "../data_output/2024-1_diffexpr_output/kegg_lrt.Rds")


```


```{r}
# Lists of gene names for differentially expressed genes
de <- readRDS(file = "../data_output/2024-1_diffexpr_output/de.Rds")
```


```{r}
# Data processing

### Read target genes

#### Fru

fru_ma_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 1-fruma_targets.csv")[,-2]
fru_mc_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 2-frumc_targets.csv")[,-2]
fru_mb_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 3-frumb_targets.csv")[,-2]


fru_ma_genes <- fru_ma_genes$FruMA
fru_mc_genes <- fru_mc_genes$FruMC
fru_mb_genes <- fru_mb_genes$FruMB

fru_target_genes <- unique(c(fru_ma_genes, fru_mc_genes, fru_mb_genes)) # Combine three different isoforms
```



```{r}
# Filtering differential genes to keep overlap with fru targets 
de$cs_genes_id_fru <- de$cs_genes_id[de$cs_genes_id %in% fru_target_genes]
de$genotype_gh_genes_id_fru <- de$genotype_gh_genes_id[de$genotype_gh_genes_id %in% fru_target_genes]
de$genotype_sh_genes_id_fru <- de$genotype_sh_genes_id[de$genotype_sh_genes_id %in% fru_target_genes]
```

```{r}
#### dsx
dsx_target_genes <- readxl::read_excel("../data_input/gene_annotations/dsx_target_genes.xlsx",sheet = 3)
dsx_target_genes <- dsx_target_genes$`Male_Fatbody_DamIDseq_Gene_Level_Occupancy> 0.9`
```

```{r}
# Filtering differential genes to keep overlap with dsx targets 
de$cs_genes_id_dsx <- de$cs_genes_id[de$cs_genes_id %in% dsx_target_genes]
de$genotype_gh_genes_id_dsx <- de$genotype_gh_genes_id[de$genotype_gh_genes_id %in% dsx_target_genes]
de$genotype_sh_genes_id_dsx <- de$genotype_sh_genes_id[de$genotype_sh_genes_id %in% dsx_target_genes]

```

```{r}
#### go
# Map of flybase id to gene name 
symbol_ensembl_map_df <- clusterProfiler::bitr(geneID = res_df$gene_name, fromType = "SYMBOL",toType ="ENSEMBL",OrgDb = org.Dm.eg.db )
symbol_ensembl_map <- symbol_ensembl_map_df$SYMBOL 
names(symbol_ensembl_map) <-  symbol_ensembl_map_df$ENSEMBL

```




# QC of the data: PCA plots between samples

```{r}
pca_data <- plotPCA(vsd_combat , intgroup = "condition", returnData = TRUE) 

ggplot(pca_data, aes(PC1, PC2, color = condition)) +
  geom_point(size = 2) +  # Adjust the size of the points
  theme_classic() +
  theme(aspect.ratio = 1)+
  ggtitle("PCA RNA-seq samples")
```

# Number of differentially expressed genes in pairwise comparisons 

## Differentially expressed genes between housing conditions in each genotype (GH / SH)

```{r}
res_long_df_housing <- res_long_df %>% 
  # First do data processing
  dplyr::select(comparison, padj, log2FoldChange) %>% # Keep relevant columns 
  dplyr::filter(!str_detect(comparison,"lrt") & str_detect(comparison,"housing")) %>% # Filtering comparisons of interest
  drop_na(padj) %>% # Filter out genes
  dplyr::filter(padj < 0.05 & abs(log2FoldChange) > 0.1)  %>% # get differential genes
  mutate(log2fc_sign = ifelse(sign(log2FoldChange) > 0,"UP", "DOWN")) %>% # Add log2fc sign variable 
  group_by(comparison, log2fc_sign) %>%
  summarise(n_diff = dplyr::n()) %>% # Count number of genes per group
  ungroup() %>%
  mutate(comparison = paste(comparison, log2fc_sign)) 

# Split comparison by direction
res_long_df_housing$comparison <- factor(res_long_df_housing$comparison, levels = c("DSX_housing UP", "DSX_housing DOWN", "FRU_housing UP", "FRU_housing DOWN", "Or67d_housing UP", "Or67d_housing DOWN", "Or47b_housing UP", "Or47b_housing DOWN", "CS_housing UP", "CS_housing DOWN"))

  ggplot(res_long_df_housing,aes(n_diff, comparison)) + 
  geom_col(aes(fill = log2fc_sign)) + # barplots 
  scale_fill_manual(values = c("UP"="#ff7777","DOWN" ="skyblue")) +
  theme_classic() +
  geom_text(aes(label = n_diff),nudge_x = 5, size = 3) + # Add number of genes to bars
  theme(aspect.ratio = 1) +
  ggtitle("Number of differential genes between GH / SH") +
  xlab("Number of genes padj < 0.05 & abs(log2FoldChange) > 0.1")

```


## Differentially expressed genes between genotype in each housing condition (Mutant / CS)

### Group Housed:

```{r}
res_long_df_genotype_GH <-res_long_df %>% 
  dplyr::select(comparison, padj, log2FoldChange) %>%
  dplyr::filter(!str_detect(comparison,"lrt") & str_detect(comparison,"GH_genotype")) %>%
  drop_na(padj) %>%
  dplyr::filter(padj < 0.05 & abs(log2FoldChange) > 0.1)  %>%
  mutate(log2fc_sign = ifelse(sign(log2FoldChange) > 0,"UP", "DOWN")) %>%
  group_by(comparison, log2fc_sign) %>%
  summarise(n_diff = dplyr::n()) %>%
  ungroup() %>%
  mutate(comparison = paste(comparison, log2fc_sign)) %>%
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff))

# Split comparison by direction
res_long_df_genotype_GH$comparison <- factor(res_long_df_genotype_GH$comparison, levels = c("DSX_GH_genotype UP", "DSX_GH_genotype DOWN", "FRU_GH_genotype UP", "FRU_GH_genotype DOWN", "Or67d_GH_genotype UP", "Or67d_GH_genotype DOWN", "Or47b_GH_genotype UP", "Or47b_GH_genotype DOWN", "CS_GH_genotype UP", "CS_GH_genotype DOWN"))
  
  ggplot(res_long_df_genotype_GH, aes(n_diff, comparison)) +
  geom_col(aes(fill = log2fc_sign)) +
  scale_fill_manual(values = c("UP"="#ff7777","DOWN" ="skyblue")) +
  theme_classic() +
  geom_text(aes(label = n_diff),nudge_x = 50, # Might need to change this depending on the number of genes
            size = 3) + 
  theme(aspect.ratio = 1) +
  ggtitle("Number of differential genes between Mutant GH / CantonS GH") +
  xlab("Number of genes padj < 0.05 & abs(log2FoldChange) > 0.1")


```


### Single Housed:

```{r}
res_long_df_genotype_SH <-res_long_df %>% 
  dplyr::select(comparison, padj, log2FoldChange) %>%
  dplyr::filter(!str_detect(comparison,"lrt") & str_detect(comparison,"SH_genotype")) %>%
  drop_na(padj) %>%
  dplyr::filter(padj < 0.05 & abs(log2FoldChange) > 0.1)  %>%
  mutate(log2fc_sign = ifelse(sign(log2FoldChange) > 0,"UP", "DOWN")) %>%
  group_by(comparison, log2fc_sign) %>%
  summarise(n_diff = dplyr::n()) %>%
  ungroup() %>%
  mutate(comparison = paste(comparison, log2fc_sign)) %>%
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff))

# Split comparison by direction
res_long_df_genotype_SH$comparison <- factor(res_long_df_genotype_SH$comparison, levels = c("DSX_SH_genotype UP", "DSX_SH_genotype DOWN", "FRU_SH_genotype UP", "FRU_SH_genotype DOWN", "Or67d_SH_genotype UP", "Or67d_SH_genotype DOWN", "Or47b_SH_genotype UP", "Or47b_SH_genotype DOWN", "CS_SH_genotype UP", "CS_SH_genotype DOWN"))
  
  ggplot(res_long_df_genotype_SH, aes(n_diff, comparison)) +
  geom_col(aes(fill = log2fc_sign)) +
  scale_fill_manual(values = c("UP"="#ff7777","DOWN" ="skyblue")) +
  theme_classic() +
  geom_text(aes(label = n_diff),nudge_x = 150, # Might need to change this depending on the number of genes
            size = 3) + 
    xlim(0, 2300)+
  theme(aspect.ratio = 1) +
  ggtitle("Number of differential genes between Mutant SH / CantonS SH") +
  xlab("Number of genes padj < 0.05 & abs(log2FoldChange) > 0.1")

```


# Venn diagram with (at least) three groups of DEGs:

## Housing within the same genotype

### All differential genes (without considerign sign of fold change) 

```{r}
# Input for venn diagrams is list of sets of genes 
ggVennDiagram::ggVennDiagram(comp_list$housing_all_symbol, 
                             label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() + # Change this if you want a different color scheme
  ggtitle("Housing within genotype All")
```

### Differential genes Up (fold change > 0.1, e.g. higher in GH, lower in SH)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$housing_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Housing within genotype UP") 
```

### Differential genes Down (fold change < -0.1, e.g. lower in GH, higher in SH)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$housing_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Housing within genotype DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```

## GH: each Mutant GH / CS GH

### All differential genes (without considerign sign of fold change) 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Up (fold change > 0.1, e.g. higher in Mutant, lower in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Down (fold change < -0.1, e.g. lower in Mutant, higher in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```


## SH: each Mutant SH / CS SH

### All differential genes (without considerign sign of fold change) 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Up (fold change > 0.1, e.g. higher in Mutant, lower in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Down (fold change < -0.1, e.g. lower in Mutant, higher in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() + 
  ggtitle("Mutant vs CantonS SH DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```


# GO and Pathway terms for different comparisons

Note: All GO plots showing only Top 3 most enriched terms per group. See each table for full results. 

## Housing within the same genotype

### All differential genes (without considerign sign of fold change) 


#GO
Dotplot 

```{r}
# ALL
dotplot(go_housing$all_entrezid,
        showCategory = 15, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') +  scale_y_discrete(labels = function(x) str_wrap(x, width = 50)) +
  ggtitle("GO terms housing ALL top15")


dotplot(go_housing_all_simplify,
        showCategory = 15, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 50)) +
  ggtitle("GO terms housing ALL simplify top15")


#Or only
Or_only <- c("CS", "Or47b", "Or67d")

Or_only_go <- go_housing$all_entrezid %>%
  filter(grepl(paste(Or_only, collapse = "|"), Cluster))

dotplot(Or_only_go,
        showCategory = 15, # Number of top go terms to plot, based on p adjust value
by='GeneRatio')  + scale_y_discrete(labels = function(x) str_wrap(x, width = 55)) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) +
  ggtitle("GO terms housing Or top15")


#TF only
TF_only <- c("CS", "FRU", "DSX")

TF_only_go <- go_housing$all_entrezid %>%
  filter(grepl(paste(TF_only, collapse = "|"), Cluster))

dotplot(TF_only_go,
        showCategory = 15, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 55)) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) +
  ggtitle("GO terms housing TF top15")

```


concept network

```{r}
cnetplot(go_housing$all_entrezid,showCategory = 15, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("GO terms housing ALL top15")

cnetplot(go_housing_all_simplify,showCategory = 15, by='GeneRatio', node_label="category", legend_n = 3) +
  ggtitle("GO terms housing ALL simplify top15") 

cnetplot(go_housing_CS_simplify,showCategory = 15, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("GO terms housing CS simplify top15") 

go_housing_all_emap <- pairwise_termsim(go_housing$all_entrezid)   
base_family <- "Arial"  # change to a locally installed font
set.seed(98)
emapplot(go_housing_all_emap,  showCategory = 15, pie="Count",legend_n = 2, cex_line = 0.2, layout = "nicely")+
  ggtitle("GO terms housing ALL top15") +
  ggraph::theme_graph(base_family = base_family) +
     theme(text = element_text(family = base_family))  # belt & suspenders

```
#Reactome

```{r}
dotplot(reactome_housing$all_entrezid,showCategory = 10, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+
  ggtitle("Reactome Pathway housing ALL top10")
```

```{r}
cnetplot(reactome_housing$all_entrezid,showCategory = 10, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("Reactome Pathway terms housing ALL top10")
```

#KEGG
```{r}
 dotplot(KEGG_housing$all_entrezid, showCategory = 10, by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+
  ggtitle("KEGG terms housing ALL top10")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 

```

```{r}
cnetplot(KEGG_housing$all_entrezid,showCategory = 10, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("KEGG terms housing ALL top10")
```

Full table of GO Results:


```{r}
print_go_table(go_housing$all_entrezid@compareClusterResult)
print_go_table(go_housing_all_simplify@compareClusterResult)
```


Full table of Reactome Results:

```{r}
print_go_table(reactome_housing$all_entrezid@compareClusterResult)
```
Full table of KEGG Results:

```{r}
print_go_table(KEGG_housing$all_entrezid@compareClusterResult)
```


## GH: each Mutant GH / CS GH

### All differential genes (without considerign sign of fold change) 
#GO
dotplot

```{r}
dotplot(go_genotype$gh_all_entrezid,showCategory = 10, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH ALL top10")

dotplot(go_genotype_gh_all_simplify,showCategory = 10, by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) +
  ggtitle("GO terms Mutant vs CantonS GH ALL simplify top10")

#Or only
Or_only_go_genotype_gh <- go_genotype$gh_all_entrezid %>%
  filter(grepl(paste(Or_only, collapse = "|"), Cluster))

dotplot(Or_only_go_genotype_gh,
        showCategory = 10, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 55))+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) +
  ggtitle("GO Or Mutant vs CS GH top10")


#TF only
TF_only_go_genotype_gh <- go_genotype$gh_all_entrezid %>%
  filter(grepl(paste(TF_only, collapse = "|"), Cluster))

dotplot(TF_only_go_genotype_gh,
        showCategory = 10, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 55))+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) +
  ggtitle("GO TF Mutant vs CS GH top10")

```
Concept network plot

```{r}
cnetplot(go_genotype$gh_all_entrezid,showCategory =10, node_label="category", legend_n = 2) +
  ggtitle("GO terms Mutant vs CantonS GH ALL top10")

cnetplot(go_genotype_gh_all_simplify,showCategory =3, node_label="category", legend_n = 2) +
  ggtitle("GO terms Mutant vs CantonS GH ALL simplify top3")

go_genotype_gh_all_emap <- pairwise_termsim(go_genotype$gh_all_entrezid)   
base_family <- "Arial"  # change to a locally installed font
set.seed(103)
emapplot(go_genotype_gh_all_emap,  showCategory = 10, pie="Count",legend_n = 2, cex_line = 0.2, layout = "nicely")+
  ggtitle("GO terms Mutant vs CantonS GH ALL top10") +
  ggraph::theme_graph(base_family = base_family) +
     theme(text = element_text(family = base_family))  # belt & suspenders


```

#Reactome

```{r}
dotplot(reactome_genotype$gh_all_entrezid,showCategory = 10, by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+ 
  ggtitle("Reactome Pathway terms Mutant vs CantonS GH ALL top10")
```


```{r}
cnetplot(reactome_genotype$gh_all_entrezid,showCategory = 10, node_label="category", legend_n = 2) +
  ggtitle("Reactome Pathway terms Mutant vs CantonS GH ALL top10")
```

#KEGG
```{r}
 dotplot(KEGG_genotype$gh_all_entrezid, showCategory = 10, by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+
  ggtitle("KEGG terms Mutant vs CantonS GH ALL top10")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 

```

```{r}
cnetplot(KEGG_genotype$gh_all_entrezid,showCategory = 10, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("KEGG terms Mutant vs CantonS GH ALL top10")

```



Full table of GO Results:

```{r}
print_go_table(go_genotype$gh_all_entrezid@compareClusterResult)
print_go_table(go_genotype_gh_all_simplify@compareClusterResult)

```

Full table of Reactome Results:

```{r}
print_go_table(reactome_genotype$gh_all_entrezid@compareClusterResult)
```

Full table of KEGG Results:

```{r}
print_go_table(KEGG_genotype$gh_all_entrezid@compareClusterResult)
```

## SH: each Mutant SH / CS SH

### All differential genes (without considerign sign of fold change) 

dotplot

```{r}

dotplot(go_genotype$sh_all_entrezid,showCategory = 10, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH ALL top10")

dotplot(go_genotype_sh_all_simplify,showCategory = 10, by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+
  ggtitle("GO terms Mutant vs CantonS SH ALL simplify top10") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 

#Or only
Or_only_go_genotype_sh <- go_genotype$sh_all_entrezid %>%
  filter(grepl(paste(Or_only, collapse = "|"), Cluster))

dotplot(Or_only_go_genotype_sh,
        showCategory = 10, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 55))+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) +
  ggtitle("GO Or Mutant vs CS SH top10")


#TF only
TF_only_go_genotype_sh <- go_genotype$sh_all_entrezid %>%
  filter(grepl(paste(TF_only, collapse = "|"), Cluster))

dotplot(TF_only_go_genotype_sh,
        showCategory = 10, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 55))+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + 
  ggtitle("GO TF Mutant vs CS SH top10")

```



Concept Network Plot

```{r}

cnetplot(go_genotype$sh_all_entrezid,showCategory = 10, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("GO terms Mutant vs CantonS SH ALL top10")

cnetplot(go_genotype_sh_all_simplify, showCategory = 3,by='GeneRatio', node_label="category", legend_n = 3) +
  ggtitle("GO terms Mutant vs CantonS SH ALL simplify top3")

go_genotype_sh_all_emap <- pairwise_termsim(go_genotype$sh_all_entrezid)   
base_family <- "Arial"  # change to a locally installed font
set.seed(97)
emapplot(go_genotype_sh_all_emap,  showCategory = 10, pie="Count",legend_n = 3, cex_line = 0.2, layout = "nicely")+
  ggtitle("GO terms Mutant vs CantonS SH ALL top10") +
  ggraph::theme_graph(base_family = base_family) +
     theme(text = element_text(family = base_family))  # belt & suspenders


```

#Reactome
```{r}

dotplot(reactome_genotype$sh_all_entrezid,showCategory = 10, by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+
  ggtitle("Reactome Pathway terms Mutant vs CantonS SH ALL top10")

```


```{r}

cnetplot(reactome_genotype$sh_all_entrezid,showCategory = 10, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("Reactome Pathway terms Mutant vs CantonS SH ALL top10")

```

#KEGG
```{r}
dotplot(KEGG_genotype$sh_all_entrezid, showCategory = 10, by='GeneRatio') +scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+
  ggtitle("KEGG terms Mutant vs CantonS SH ALL top10")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 

```

```{r}
cnetplot(KEGG_genotype$sh_all_entrezid,showCategory = 10, by='GeneRatio', node_label="category", legend_n = 2) +
  ggtitle("KEGG terms Mutant vs CantonS SH ALL top10")
```



Full table of GO Results:

```{r}
print_go_table(go_genotype$sh_all_entrezid@compareClusterResult)
print_go_table(go_genotype_sh_all_simplify@compareClusterResult)

```


Full table of Reactome Results:

```{r}
print_go_table(reactome_genotype$sh_all_entrezid@compareClusterResult)
```

Full table of KEGG Results:

```{r}
print_go_table(KEGG_genotype$sh_all_entrezid@compareClusterResult)
```


# Heatmaps:

### Housing within the same genotype

#### Z score median

the replicates were combined in a single column by taking the median of all 3 replicate values.

##### All genes that are differentially expressed in GH CS / SH CS comparison 

rows clustered 

```{r fig.height=13}
plot_heatmap(norm_cts_median[de$cs_genes_id,], "DEGs in GH CS/SH CS comparison", cluster_columns = FALSE, show_row_names = F, cluster_rows = TRUE) 

plot_heatmap(norm_cts_median[de$cs_genes_id, c("CS_GH","CS_SH","Or47b_GH","Or47b_SH","Or67d_GH", "Or67d_SH")], "DEGs in GH CS/SH CS comparison Or", cluster_columns = FALSE, show_row_names = F, cluster_rows = TRUE) 

plot_heatmap(norm_cts_median[de$cs_genes_id, c("CS_GH","CS_SH","FRU_GH","FRU_SH","DSX_GH", "DSX_SH")], "DEGs in GH CS/SH CS comparison TF", cluster_columns = FALSE, show_row_names = F, cluster_rows = TRUE) 


```

##### DEGs in GH CS/SH CS comparison with fru dsx label

```{r}
genes <- rownames(norm_cts_median[de$cs_genes_id,])

# Logical vectors
is_in_fru <- genes %in% fru_target_genes
is_in_dsx <- genes %in% dsx_target_genes

# Create a data frame for annotation
annotation_df <- data.frame(
  fru_target = ifelse(is_in_fru, "Yes", "No"),
  dsx_target = ifelse(is_in_dsx, "Yes", "No")
)
rownames(annotation_df) <- genes

ann_colors <- list(
  fru_target = c("Yes" = "#08B6B6", "No" = "white"),
  dsx_target = c("Yes" = "#B4049A", "No" = "white")
)

row_anno <- rowAnnotation(
  df = annotation_df,
  col = ann_colors,
  show_annotation_name = TRUE,
  annotation_name_side = "bottom",
  width = unit(1, "cm"),
  show_legend = FALSE
)



ht <- ComplexHeatmap::Heatmap(mat = t(scale(t(norm_cts_median[de$cs_genes_id,]),center = TRUE,scale = TRUE)), # z score
          column_title = "DEGs in GH CS/SH CS comparison with fru dsx label",
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
                                      raster_device = "agg_png", # Format to export the raster 
                                      cluster_columns = FALSE,
                                      show_row_names = FALSE
          ) 
ht + row_anno
```


##### fru/dsx target DEGs in GH CS/SH CS comparison with fru dsx label

```{r}
genes <- unique(c(de$cs_genes_id_fru, de$cs_genes_id_dsx))

# Logical vectors
is_in_fru <- genes %in% fru_target_genes
is_in_dsx <- genes %in% dsx_target_genes

# Create a data frame for annotation
annotation_df <- data.frame(
  fru_target = ifelse(is_in_fru, "Yes", "No"),
  dsx_target = ifelse(is_in_dsx, "Yes", "No")
)
rownames(annotation_df) <- genes

ann_colors <- list(
  fru_target = c("Yes" = "#08B6B6", "No" = "white"),
  dsx_target = c("Yes" = "#B4049A", "No" = "white")
)

row_anno <- rowAnnotation(
  df = annotation_df,
  col = ann_colors,
  show_annotation_name = TRUE,
  annotation_name_side = "bottom",
  width = unit(1, "cm"),
  show_legend = FALSE
)



ht <- ComplexHeatmap::Heatmap(mat = t(scale(t(norm_cts_median[genes,]),center = TRUE,scale = TRUE)), # z score
          column_title = "fru/dsx target DEGs in GH CS/SH CS comparison with fru dsx label",
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
                                      raster_device = "agg_png", # Format to export the raster 
                                      cluster_columns = FALSE,
                                      show_row_names = FALSE
          ) 
ht + row_anno
```

##### fru/dsx target DEGs in all mutant/CS comparison with fru dsx label

```{r}
genes <- unique(c(de$genotype_gh_genes_id_fru, de$genotype_gh_genes_id_dsx, de$genotype_sh_genes_id_fru, de$genotype_sh_genes_id_dsx))

# Logical vectors
is_in_fru <- genes %in% fru_target_genes
is_in_dsx <- genes %in% dsx_target_genes

# Create a data frame for annotation
annotation_df <- data.frame(
  fru_target = ifelse(is_in_fru, "Yes", "No"),
  dsx_target = ifelse(is_in_dsx, "Yes", "No")
)
rownames(annotation_df) <- genes

ann_colors <- list(
  fru_target = c("Yes" = "#08B6B6", "No" = "white"),
  dsx_target = c("Yes" = "#B4049A", "No" = "white")
)

row_anno <- rowAnnotation(
  df = annotation_df,
  col = ann_colors,
  show_annotation_name = TRUE,
  annotation_name_side = "bottom",
  width = unit(1, "cm"),
  show_legend = FALSE
)



ht <- ComplexHeatmap::Heatmap(mat = t(scale(t(norm_cts_median[genes,]),center = TRUE,scale = TRUE)), # z score
          column_title = "fru/dsx target DEGs in all mutants/CS comparison with fru dsx label",
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
                                      raster_device = "agg_png", # Format to export the raster 
                                      cluster_columns = FALSE,
                                      show_row_names = FALSE
          ) 
ht + row_anno
```




##### fru: differential genes subset by whether they are fru targets

rows clustered

```{r fig.height=8}
plot_heatmap(norm_cts_median[de$cs_genes_id_fru,], "DEGs in GH CS/SH CS comparison fru target",show_row_names = TRUE, cluster_columns = FALSE, cluster_rows = TRUE)

#circadian overlap GO_0007623_circadian_rhythm
GO_0007623_circadian_rhythm_table <- read.delim("../data_input/gene_annotations/GO_0007623_circadian_rhythm_table.txt", header=FALSE, comment.char="#")

fru_target_circadian_genes <- de$cs_genes_id_fru[de$cs_genes_id_fru %in% GO_0007623_circadian_rhythm_table$V3]

plot_heatmap(norm_cts_median[fru_target_circadian_genes,], "DEGs in GH CS/SH CS comparison fru target GO_0007623 circadian rhythm genes",show_row_names = TRUE, cluster_columns = FALSE, cluster_rows = TRUE)

```

##### dsx: differential genes subset by whether they are dsx targets

clustered rows

```{r}
plot_heatmap(norm_cts_median[de$cs_genes_id_dsx,],"DEGs in GH CS/SH CS comparison dsx target",cluster_columns = FALSE, show_row_names = TRUE, cluster_rows = TRUE)

dsx_target_circadian_genes <- de$cs_genes_id_dsx[de$cs_genes_id_dsx %in% GO_0007623_circadian_rhythm_table$V3]

plot_heatmap(norm_cts_median[dsx_target_circadian_genes,], "DEGs in GH/SH CS comparison fru/dsx target circadian rhythm genes",show_row_names = TRUE, cluster_columns = FALSE, cluster_rows = TRUE)
```


### GH: each Mutant GH / CS GH

#### Z score all reps

##### All genes that are differentially expressed in Mutant GH / CS GH comparison 

cluster rows 

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id,str_detect(colnames(norm_cts_median),"GH")],"DEGs in Mutant GH/CS GH comparison", cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)

DEGs_Or_GH <- norm_cts_median[de$genotype_Or_gh_genes_id,c("CS_GH","Or47b_GH","Or67d_GH")]
DEGs_Or_GH <- DEGs_Or_GH[rowSums(DEGs_Or_GH != 0) > 0, ]
plot_heatmap(DEGs_Or_GH,"DEGs in Or mut GH/CS GH comparison", cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)


DEGs_TF_GH <- norm_cts_median[de$genotype_TF_gh_genes_id,c("CS_GH","FRU_GH","DSX_GH")]
DEGs_TF_GH <- DEGs_TF_GH[rowSums(DEGs_TF_GH != 0) > 0, ]
plot_heatmap(DEGs_TF_GH,"DEGs in TF mut GH/CS GH comparison", cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)


```


##### DEGs in GH mutant/CS comparison with fru dsx label

```{r}
genes <- rownames(norm_cts_median[de$genotype_gh_genes_id,str_detect(colnames(norm_cts_median),"GH")])

# Logical vectors
is_in_fru <- genes %in% fru_target_genes
is_in_dsx <- genes %in% dsx_target_genes

# Create a data frame for annotation
annotation_df <- data.frame(
  fru_target = ifelse(is_in_fru, "Yes", "No"),
  dsx_target = ifelse(is_in_dsx, "Yes", "No")
)
rownames(annotation_df) <- genes

ann_colors <- list(
  fru_target = c("Yes" = "#08B6B6", "No" = "white"),
  dsx_target = c("Yes" = "#B4049A", "No" = "white")
)

row_anno <- rowAnnotation(
  df = annotation_df,
  col = ann_colors,
  show_annotation_name = TRUE,
  annotation_name_side = "bottom",
  width = unit(1, "cm"),
  show_legend = FALSE
)



ht <- ComplexHeatmap::Heatmap(mat = t(scale(t(norm_cts_median[de$genotype_gh_genes_id,str_detect(colnames(norm_cts_median),"GH")]),center = TRUE,scale = TRUE)), # z score
          column_title = "DEGs in GH Mutant/CS comparison with fru dsx label",
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
                                      raster_device = "agg_png", # Format to export the raster 
                                      cluster_columns = FALSE,
                                      show_row_names = FALSE
          ) 
ht + row_anno
```

##### fru/dsx target DEGs in GH mutant/CS comparison with fru dsx label

```{r}
genes <- unique(c(de$genotype_gh_genes_id_fru, de$genotype_gh_genes_id_dsx))

DEG_GH <- norm_cts_median[genes, str_detect(colnames(norm_cts_median), "GH")] %>% as.data.frame() %>%
  filter(rowSums(.) != 0) %>% as.matrix()

genes <- rownames(DEG_GH)

# Logical vectors
is_in_fru <- genes %in% fru_target_genes
is_in_dsx <- genes %in% dsx_target_genes

# Create a data frame for annotation
annotation_df <- data.frame(
  fru_target = ifelse(is_in_fru, "Yes", "No"),
  dsx_target = ifelse(is_in_dsx, "Yes", "No")
)
rownames(annotation_df) <- genes

ann_colors <- list(
  fru_target = c("Yes" = "#08B6B6", "No" = "white"),
  dsx_target = c("Yes" = "#B4049A", "No" = "white")
)

row_anno <- rowAnnotation(
  df = annotation_df,
  col = ann_colors,
  show_annotation_name = TRUE,
  annotation_name_side = "bottom",
  width = unit(1, "cm"),
  show_legend = FALSE
)



ht <- ComplexHeatmap::Heatmap(mat = t(scale(t(DEG_GH),center = TRUE,scale = TRUE)), # z score
          column_title = "fru/dsx target DEGs in GH mutant/CS comparison with fru dsx label",
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
                                      raster_device = "agg_png", # Format to export the raster 
                                      cluster_columns = FALSE,
                                      show_row_names = FALSE
          ) 
ht + row_anno
```



##### fru: differential genes subset by whether they are fru targets


cluster rows  

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id_fru,],"DEGs in Mutant GH/CS GH comparison fru target", cluster_columns = FALSE, show_row_names = T, cluster_rows = TRUE)
```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id_dsx,], "DEGs in Mutant GH/CS GH comparison dsx target", cluster_columns = FALSE, show_row_names = T, cluster_rows = TRUE)
```


### SH: each Mutant SH / CS SH

#### Z score all reps

##### All genes that are differentially expressed  

cluster rows

```{r}
DEG_SH <- norm_cts_median[de$genotype_sh_genes_id, str_detect(colnames(norm_cts_median), "SH")] %>% as.data.frame() %>%
  filter(rowSums(.) != 0) %>% as.matrix()
plot_heatmap(DEG_SH,"DEGs in Mutant SH/CS SH comparison",cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)

DEGs_Or_SH <- norm_cts_median[de$genotype_Or_sh_genes_id,c("CS_SH","Or47b_SH","Or67d_SH")]
DEGs_Or_SH <- DEGs_Or_SH[rowSums(DEGs_Or_SH != 0) > 0, ]
plot_heatmap(DEGs_Or_SH,"DEGs in Or mut SH/CS SH comparison", cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)


DEGs_TF_SH <- norm_cts_median[de$genotype_TF_sh_genes_id,c("CS_SH","FRU_SH","DSX_SH")]
DEGs_TF_SH <- DEGs_TF_SH[rowSums(DEGs_TF_SH != 0) > 0, ]
plot_heatmap(DEGs_TF_SH,"DEGs in TF mut SH/CS SH comparison", cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)

```


##### DEGs in SH mutant/CS comparison with fru dsx label

```{r}

DEG_SH <- norm_cts_median[de$genotype_sh_genes_id, str_detect(colnames(norm_cts_median), "SH")] %>% as.data.frame() %>%
  filter(rowSums(.) != 0) %>% as.matrix()

genes <- rownames(DEG_SH)

# Logical vectors
is_in_fru <- genes %in% fru_target_genes
is_in_dsx <- genes %in% dsx_target_genes

# Create a data frame for annotation
annotation_df <- data.frame(
  fru_target = ifelse(is_in_fru, "Yes", "No"),
  dsx_target = ifelse(is_in_dsx, "Yes", "No")
)
rownames(annotation_df) <- genes

ann_colors <- list(
  fru_target = c("Yes" = "#08B6B6", "No" = "white"),
  dsx_target = c("Yes" = "#B4049A", "No" = "white")
)

row_anno <- rowAnnotation(
  df = annotation_df,
  col = ann_colors,
  show_annotation_name = TRUE,
  annotation_name_side = "bottom",
  width = unit(1, "cm"),
  show_legend = FALSE
)

ht <- ComplexHeatmap::Heatmap(mat = t(scale(t(DEG_SH),center = TRUE,scale = TRUE)), # z score
          column_title = "DEGs in SH Mutant/CS comparison with fru dsx label",
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
                                      raster_device = "agg_png", # Format to export the raster 
                                      cluster_columns = FALSE,
                                      show_row_names = FALSE
          ) 
ht + row_anno
```

##### fru/dsx target DEGs in SH mutant/CS comparison with fru dsx label

```{r}
genes <- unique(c(de$genotype_sh_genes_id_fru, de$genotype_sh_genes_id_dsx))

DEG_SH <- norm_cts_median[genes, str_detect(colnames(norm_cts_median), "SH")] %>% as.data.frame() %>%
  filter(rowSums(.) != 0) %>% as.matrix()

genes <- rownames(DEG_SH)

# Logical vectors
is_in_fru <- genes %in% fru_target_genes
is_in_dsx <- genes %in% dsx_target_genes

# Create a data frame for annotation
annotation_df <- data.frame(
  fru_target = ifelse(is_in_fru, "Yes", "No"),
  dsx_target = ifelse(is_in_dsx, "Yes", "No")
)
rownames(annotation_df) <- genes

ann_colors <- list(
  fru_target = c("Yes" = "#08B6B6", "No" = "white"),
  dsx_target = c("Yes" = "#B4049A", "No" = "white")
)

row_anno <- rowAnnotation(
  df = annotation_df,
  col = ann_colors,
  show_annotation_name = TRUE,
  annotation_name_side = "bottom",
  width = unit(1, "cm"),
  show_legend = FALSE
)



ht <- ComplexHeatmap::Heatmap(mat = t(scale(t(DEG_SH),center = TRUE,scale = TRUE)), # z score
          column_title = "fru/dsx target DEGs in SH mutant/CS comparison with fru dsx label",
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
                                      raster_device = "agg_png", # Format to export the raster 
                                      cluster_columns = FALSE,
                                      show_row_names = FALSE
          ) 
ht + row_anno
```



##### fru: differential genes subset by whether they are fru targets

cluster rows

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id_fru,], "DEGs in Mutant SH/CS SH comparison fru target",cluster_columns = FALSE, show_row_names = T, cluster_rows = TRUE)
```


##### dsx: differential genes subset by whether they are dsx targets

cluster rows

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id_dsx,],"DEGs in Mutant SH/CS SH comparison dsx target", cluster_columns = FALSE, show_row_names = T, cluster_rows = TRUE)
```


# Volcano plots for different comparisons

## Housing within the same genotype

```{r}

res_long_df %>%
  dplyr::filter(str_detect(comparison,"housing")) %>%
  dplyr::filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing")) %>% # removing "housing" from genotype names
    mutate(comparison = factor(comparison, levels = c("CS","Or47b", "Or67d", "FRU", "DSX"))) %>%
  ggplot(aes(log2FoldChange, -log10(padj),color = padj < 0.05 & abs(log2FoldChange) > 0.1 )) + # cutoffs for padj and log2foldchange
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) + # modify for rows if needed 
  ylim(c(0,15)) + # cap padj values
  xlim(c(-5,5)) + # Cap log2foldchange
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("GH / SH within each genotype") + 
  scale_color_manual(values = c("FALSE" = "gray","TRUE" = "blue"))


res_long_df %>%
  dplyr::filter(str_detect(comparison,"housing")) %>%
  dplyr::filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing")) %>% # removing "housing" from genotype names
  mutate(comparison = factor(comparison, levels = c("CS","Or47b", "Or67d", "FRU", "DSX"))) %>%
  mutate(DEG_direction = case_when(
    padj < 0.05 & log2FoldChange > 0.1 ~ "Up",     # red
    padj < 0.05 & log2FoldChange < -0.1 ~ "Down",  # blue
    TRUE ~ "NS"                                    # gray
  )) %>%
  ggplot(aes(log2FoldChange, -log10(padj), color = DEG_direction)) +
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,15)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("GH / SH within each genotype") + 
  scale_color_manual(values = c("Up" = "#ff7777", "Down" = "skyblue", "NS" = "gray"))


```

## GH: each Mutant GH / CS GH

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(str_detect(comparison, "GH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_GH_genotype")) %>%
  mutate(comparison = factor(comparison, levels = c("Or47b", "Or67d", "FRU", "DSX"))) %>%
  ggplot(aes(log2FoldChange, -log10(padj),color = padj < 0.05 & abs(log2FoldChange) > 0.1 )) +
  geom_point(size = 0.5, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,15)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("Mutant / CantonS within GH") + 
  scale_color_manual(values = c("FALSE" = "gray","TRUE" = "blue"))
  

res_long_df %>%
   filter(str_detect(comparison,"genotype")) %>%
    filter(str_detect(comparison, "GH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_GH_genotype")) %>%
  mutate(comparison = factor(comparison, levels = c("Or47b", "Or67d", "FRU", "DSX"))) %>%
  mutate(DEG_direction = case_when(
    padj < 0.05 & log2FoldChange > 0.1 ~ "Up",     # red
    padj < 0.05 & log2FoldChange < -0.1 ~ "Down",  # blue
    TRUE ~ "NS"                                    # gray
  )) %>%
  ggplot(aes(log2FoldChange, -log10(padj), color = DEG_direction)) +
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,15)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("Mutant / CantonS within GH") + 
  scale_color_manual(values = c("Up" = "#ff7777", "Down" = "skyblue", "NS" = "gray"))





```


## SH: each Mutant SH / CS SH

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(str_detect(comparison, "SH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_SH_genotype")) %>%  
  mutate(comparison = factor(comparison, levels = c("Or47b", "Or67d", "FRU", "DSX"))) %>%
  ggplot(aes(log2FoldChange, -log10(padj),color = padj < 0.05 & abs(log2FoldChange) > 0.1 )) +
  geom_point(size = 0.5, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,15)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("Mutant / CantonS within SH") + 
  scale_color_manual(values = c("FALSE" = "gray","TRUE" = "blue"))
  

res_long_df %>%
   filter(str_detect(comparison,"genotype")) %>%
    filter(str_detect(comparison, "SH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_SH_genotype")) %>%
  mutate(comparison = factor(comparison, levels = c("Or47b", "Or67d", "FRU", "DSX"))) %>%
  mutate(DEG_direction = case_when(
    padj < 0.05 & log2FoldChange > 0.1 ~ "Up",     # red
    padj < 0.05 & log2FoldChange < -0.1 ~ "Down",  # blue
    TRUE ~ "NS"                                    # gray
  )) %>%
  ggplot(aes(log2FoldChange, -log10(padj), color = DEG_direction)) +
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,15)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("Mutant / CantonS within SH") + 
  scale_color_manual(values = c("Up" = "#ff7777", "Down" = "skyblue", "NS" = "gray"))




```



# sign combination GO
## Heatmap of Ashr genotype significant genes log2FoldChange of Mutant GH / CantonS GH
```{r}
pairwise_log2fc_genotype_df_genes <- pairwise_log2fc_genotype_df_ashr_GH %>%
  dplyr::select(gene_name, sign_paste_genotype_gh) %>%
  unique()

sort(table(pairwise_log2fc_genotype_df_genes$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  geom_text(aes(label = value),nudge_x = -50, size = 3) +
  scale_x_reverse() +  # Reverse bar direction
  scale_y_discrete(position = "right") +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes genotype GH")

pairwise_log2fc_genotype_df_ngenes <- pairwise_log2fc_genotype_df_ashr_GH %>%
  group_by(sign_paste_genotype_gh) %>%
  summarise(n_genes = dplyr::n())

#heatmap all
pairwise_log2fc_genotype_top_sign_combinations <- pairwise_log2fc_genotype_df_ngenes %>%
  slice_max(order_by = n_genes, n = 27) %>%
  pull(sign_paste_genotype_gh) %>%
  unique()

pairwise_log2fc_genotype_df_join <- left_join(pairwise_log2fc_genotype_df_ashr_GH, pairwise_log2fc_genotype_df_ngenes, by = "sign_paste_genotype_gh")

pairwise_log2fc_genotype_df_join %>%
  dplyr::filter(sign_paste_genotype_gh %in% pairwise_log2fc_genotype_top_sign_combinations) %>%
  dplyr::mutate(sign_paste_genotype_gh = fct_reorder(sign_paste_genotype_gh, dplyr::desc(n_genes))) %>%
  dplyr::mutate(
    genotype = factor(genotype, levels = c("Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste_genotype_gh), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.2, "lines"),   # tweak spacing between panels
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("Ashr GH genotype all")  +
  theme(axis.text.y = element_blank())


#heatmap top16
pairwise_log2fc_genotype_top_sign_combinations <- pairwise_log2fc_genotype_df_ngenes %>%
  slice_max(order_by = n_genes, n = 30) %>%
  pull(sign_paste_genotype_gh) %>%
  unique()

pairwise_log2fc_genotype_df_join <- left_join(pairwise_log2fc_genotype_df_ashr_GH, pairwise_log2fc_genotype_df_ngenes, by = "sign_paste_genotype_gh")

pairwise_log2fc_genotype_df_join %>%
  dplyr::filter(sign_paste_genotype_gh %in% pairwise_log2fc_genotype_top_sign_combinations) %>%
  dplyr::mutate(sign_paste_genotype_gh = fct_reorder(sign_paste_genotype_gh, dplyr::desc(n_genes))) %>%
  dplyr::mutate(
    genotype = factor(genotype, levels = c("Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste_genotype_gh), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.2, "lines"),   # tweak spacing between panels
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("Ashr GH genotype top16")  +
  theme(axis.text.y = element_blank())


# GO terms
ordered_names <- table(pairwise_log2fc_genotype_df_ashr_GH$sign_paste_genotype_gh) %>%
     sort(decreasing = TRUE) %>%
     enframe() %>%
     mutate(name = as.factor(name)) %>%
     mutate(name = fct_reorder(name, value, .desc = TRUE)) %>%
     arrange(desc(value)) %>%
     pull(name) %>%
     as.character()

# Convert to data frame
go_Ashr_sign_GH_simplify_df <- as.data.frame(go_Ashr_sign_GH_simplify)
#go_Ashr_sign_GH_simplify_df <- filter(go_Ashr_sign_GH_simplify_df, go_Ashr_sign_GH_simplify_df$ONTOLOGY == "BP")

# Get top GO terms per cluster 
top_go_df <- go_Ashr_sign_GH_simplify_df %>%
  group_by(Cluster) %>%
  top_n(-2, p.adjust) %>%
  ungroup() %>%
  mutate(
    GeneRatio = sapply(GeneRatio, function(x) eval(parse(text = x))), 
    Description = str_wrap(Description, width = 50),
    dummy_x = "GO"
  )
top_go_df$Cluster <- factor(top_go_df$Cluster, levels = ordered_names)
top_go_df <- top_go_df[top_go_df$Count >= 2, ]


plot_go_terms_by_cluster(top_go_df, plot_title = "Top 2 GO terms mutant/CS GH" ) #Version5 axis.text.y = element_text(size = 10)

#All GO terms in one
dotplot(go_Ashr_sign_SH_simplify,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms Mutant/CantonS GH") +
  theme(axis.text.x = element_text(angle = 90,  hjust=0.5))


```

## Heatmap of Ashr genotype significant genes log2FoldChange of Mutant SH / CantonS SH
```{r}
pairwise_log2fc_genotype_df_genes <- pairwise_log2fc_genotype_df_ashr_SH %>%
  dplyr::select(gene_name, sign_paste_genotype_sh) %>%
  unique()

sort(table(pairwise_log2fc_genotype_df_genes$sign_paste_genotype_sh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  geom_text(aes(label = value),nudge_x = -55, size = 3) +
  scale_x_reverse() +  # Reverse bar direction
  scale_y_discrete(position = "right") +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes genotype SH")

pairwise_log2fc_genotype_df_ngenes <- pairwise_log2fc_genotype_df_ashr_SH %>%
  group_by(sign_paste_genotype_sh) %>%
  summarise(n_genes = dplyr::n())

#Heatmap all
pairwise_log2fc_genotype_top_sign_combinations <- pairwise_log2fc_genotype_df_ngenes %>%
  slice_max(order_by = n_genes, n = 30) %>%
  pull(sign_paste_genotype_sh) %>%
  unique()

pairwise_log2fc_genotype_df_join <- left_join(pairwise_log2fc_genotype_df_ashr_SH, pairwise_log2fc_genotype_df_ngenes, by = "sign_paste_genotype_sh")

pairwise_log2fc_genotype_df_join %>%
  dplyr::filter(sign_paste_genotype_sh %in% pairwise_log2fc_genotype_top_sign_combinations) %>%
  dplyr::mutate(sign_paste_genotype_sh = fct_reorder(sign_paste_genotype_sh, dplyr::desc(n_genes))) %>%
  dplyr::mutate(
    genotype = factor(genotype, levels = c("Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste_genotype_sh), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.2, "lines"),
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("Ashr SH genotype all")  +
  theme(axis.text.y = element_blank())

#Heatmap top16
pairwise_log2fc_genotype_top_sign_combinations <- pairwise_log2fc_genotype_df_ngenes %>%
  slice_max(order_by = n_genes, n = 16) %>%
  pull(sign_paste_genotype_sh) %>%
  unique()

pairwise_log2fc_genotype_df_join <- left_join(pairwise_log2fc_genotype_df_ashr_SH, pairwise_log2fc_genotype_df_ngenes, by = "sign_paste_genotype_sh")

pairwise_log2fc_genotype_df_join %>%
  dplyr::filter(sign_paste_genotype_sh %in% pairwise_log2fc_genotype_top_sign_combinations) %>%
  dplyr::mutate(sign_paste_genotype_sh = fct_reorder(sign_paste_genotype_sh, dplyr::desc(n_genes))) %>%
  dplyr::mutate(
    genotype = factor(genotype, levels = c("Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste_genotype_sh), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.2, "lines"),
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("Ashr SH genotype top16")  +
  theme(axis.text.y = element_blank())


# GO terms
ordered_names <- table(pairwise_log2fc_genotype_df_ashr_SH$sign_paste_genotype_sh) %>%
     sort(decreasing = TRUE) %>%
     enframe() %>%
     mutate(name = as.factor(name)) %>%
     mutate(name = fct_reorder(name, value, .desc = TRUE)) %>%
     arrange(desc(value)) %>%
     pull(name) %>%
     as.character()

# Convert to data frame
go_Ashr_sign_SH_simplify_df <- as.data.frame(go_Ashr_sign_SH_simplify)
#go_Ashr_sign_SH_simplify_df <- filter(go_Ashr_sign_SH_simplify_df, go_Ashr_sign_SH_simplify_df$ONTOLOGY == "BP")

# Get top GO terms per cluster 
top_go_df <- go_Ashr_sign_SH_simplify_df %>%
  group_by(Cluster) %>%
  top_n(-2, p.adjust) %>%
  ungroup() %>%
  mutate(
    GeneRatio = sapply(GeneRatio, function(x) eval(parse(text = x))),  # convert "1/10" to 0.1
    Description = str_wrap(Description, width = 50),
    dummy_x = "GO"
  )
top_go_df$Cluster <- factor(top_go_df$Cluster, levels = ordered_names)
top_go_df <- top_go_df[top_go_df$Count >= 2, ]


plot_go_terms_by_cluster(top_go_df, plot_title = "Top 2 GO terms mutant/CS SH" ) #Version5 axis.text.y = element_text(size = 10)


#All GO terms in one
dotplot(go_Ashr_sign_SH_simplify,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms Mutant/CantonS SH") +
  theme(axis.text.x = element_text(angle = 90,  hjust=0.5))

```

### Heatmap of log2FoldChange of CS GH / CS SH 

```{r}
log2fc_mat_housing <- log2fc_mat_housing[, c("CS", "Or47b", "Or67d", "FRU", "DSX")]  # change to your desired order

col_fun <- colorRamp2(c(-2, 0, 2), c("blue", "white", "red"))

Heatmap(
  mat = log2fc_mat_housing,
  col = col_fun,
  heatmap_legend_param = list(
    title = "log2FoldChange",
    legend_height = unit(2, "in")
  ),
  raster_device = "agg_png",
  cluster_columns = FALSE,
  show_row_names = FALSE,
  cluster_rows = F,
  column_title = "log2FC of DEGs in CS GH/CS SH comparison"
)

```




### Heatmap of LRT interaction significant genes log2FoldChange of GH / SH within each genotye 

```{r }
## housing by genotype interaction

pairwise_log2fc_interaction_df_genes <- pairwise_log2fc_interaction_df %>%
  dplyr::select(gene_name, sign_paste) %>%
  unique()

sort(table(pairwise_log2fc_interaction_df_genes$sign_paste)) %>%
  enframe() %>%
  dplyr::mutate(name = as.factor(name)) %>%
  dplyr::mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes housing:genotype interaction") +
  geom_text(aes(label = value), nudge_x = -0.5, size = 3) +
  scale_x_reverse() +  # Reverse bar direction
  scale_y_discrete(position = "right")

# Heatmaps
pairwise_log2fc_interaction_df_ngenes <- pairwise_log2fc_interaction_df %>%
  group_by(sign_paste) %>%
  summarise(n_genes = dplyr::n())

#Heatmap all
pairwise_log2fc_interaction_top_sign_combinations <- pairwise_log2fc_interaction_df_ngenes %>%
  slice_max(order_by = n_genes, n = 30) %>%
  pull(sign_paste) %>%
  unique()

pairwise_log2fc_interaction_df_join <- left_join(pairwise_log2fc_interaction_df, pairwise_log2fc_interaction_df_ngenes, by = "sign_paste")

pairwise_log2fc_interaction_df_join %>%
  dplyr::filter(sign_paste %in% pairwise_log2fc_interaction_top_sign_combinations) %>%
  dplyr::mutate(
    sign_paste = fct_reorder(sign_paste, dplyr::desc(n_genes)),
    genotype = factor(genotype, levels = c("CS", "Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
      log2FoldChange > 0.5 ~ 0.5,
      log2FoldChange < -0.5 ~ -0.5,
      TRUE ~ log2FoldChange
    )
  ) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.1, "lines"),
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT housing:genotype interaction all")



#Heatmap top16
pairwise_log2fc_interaction_top_sign_combinations <- pairwise_log2fc_interaction_df_ngenes %>%
  slice_max(order_by = n_genes, n = 16) %>%
  pull(sign_paste) %>%
  unique()

pairwise_log2fc_interaction_df_join <- left_join(pairwise_log2fc_interaction_df, pairwise_log2fc_interaction_df_ngenes, by = "sign_paste")

pairwise_log2fc_interaction_df_join %>%
  dplyr::filter(sign_paste %in% pairwise_log2fc_interaction_top_sign_combinations) %>%
  dplyr::mutate(
    sign_paste = fct_reorder(sign_paste, dplyr::desc(n_genes)),
    genotype = factor(genotype, levels = c("CS", "Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
      log2FoldChange > 0.5 ~ 0.5,
      log2FoldChange < -0.5 ~ -0.5,
      TRUE ~ log2FoldChange
    )
  ) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.1, "lines"),
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT housing:genotype interaction top16")


# GO terms

ordered_names <- table(pairwise_log2fc_interaction_df_genes$sign_paste) %>%
     sort(decreasing = TRUE) %>%
     enframe() %>%
     mutate(name = as.factor(name)) %>%
     mutate(name = fct_reorder(name, value, .desc = TRUE)) %>%
     arrange(desc(value)) %>%
     pull(name) %>%
     as.character()


# Convert to data frame
go_lrt_df <- as.data.frame(go_lrt_interaction_simplify)
#go_lrt_df <- filter(go_lrt_df, go_lrt_df$ONTOLOGY == "BP")

# Get top GO terms per cluster 
top_go_df <- go_lrt_df %>%
  group_by(Cluster) %>%
  top_n(-3, p.adjust) %>%
  ungroup() %>%
  mutate(
    GeneRatio = sapply(GeneRatio, function(x) eval(parse(text = x))),  # convert "1/10" to 0.1
    Description = str_wrap(Description, width = 50),
    dummy_x = "GO"
  )
top_go_df$Cluster <- factor(top_go_df$Cluster, levels = ordered_names)
top_go_df <- top_go_df[top_go_df$Count >= 2, ]


plot_go_terms_by_cluster(top_go_df, plot_title = "Top 3 GO terms housing genotype interaction" )

#All GO terms in one
dotplot(go_lrt$interaction,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms LRT housing:genotype interaction") +
  theme(axis.text.x = element_text(angle = 90, hjust=0.5))

```

# sign combination GO - fru/dsx targets
## Heatmap of Ashr genotype significant genes log2FoldChange of Mutant GH / CantonS GH - fru/dsx target
```{r}
genes <- unique(c(de$genotype_gh_genes_id_fru, de$genotype_gh_genes_id_dsx))

#numbers
pairwise_log2fc_genotype_df_genes <- pairwise_log2fc_genotype_df_ashr_GH %>%
  dplyr::select(gene_name, sign_paste_genotype_gh) %>%
  unique()

pairwise_log2fc_genotype_df_genes <- pairwise_log2fc_genotype_df_genes %>% filter(pairwise_log2fc_genotype_df_genes$gene_name %in% genes)

sort(table(pairwise_log2fc_genotype_df_genes$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  geom_text(aes(label = value),nudge_x = -20, size = 3) +
  scale_x_reverse() +  # Reverse bar direction
  scale_y_discrete(position = "right") +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes genotype GH fru dsx target")


#heatmap all
pairwise_log2fc_genotype_df_ashr_GH_target <- pairwise_log2fc_genotype_df_ashr_GH %>% filter(pairwise_log2fc_genotype_df_ashr_GH$gene_name %in% genes)

pairwise_log2fc_genotype_df_ngenes <- pairwise_log2fc_genotype_df_ashr_GH_target %>%
  group_by(sign_paste_genotype_gh) %>%
  summarise(n_genes = dplyr::n())

pairwise_log2fc_genotype_top_sign_combinations <- pairwise_log2fc_genotype_df_ngenes %>%
  slice_max(order_by = n_genes, n = 30) %>%
  pull(sign_paste_genotype_gh) %>%
  unique()

pairwise_log2fc_genotype_df_join <- left_join(pairwise_log2fc_genotype_df_ashr_GH_target, pairwise_log2fc_genotype_df_ngenes, by = "sign_paste_genotype_gh")

pairwise_log2fc_genotype_df_join %>%
  dplyr::filter(sign_paste_genotype_gh %in% pairwise_log2fc_genotype_top_sign_combinations) %>%
  dplyr::mutate(sign_paste_genotype_gh = fct_reorder(sign_paste_genotype_gh, dplyr::desc(n_genes))) %>%
  dplyr::mutate(
    genotype = factor(genotype, levels = c("Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste_genotype_gh), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.2, "lines"),   # tweak spacing between panels
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("Ashr GH genotype all fru/dsx targets")  +
  theme(axis.text.y = element_blank())

# GO terms
## Ashr by sign 

# go_Ashr_sign_target <- list()
# 
# Ashr_sign_genotype_GH_entrezid_target <- pairwise_log2fc_genotype_df_ashr_GH_target %>%
#   dplyr::select(entrezid, sign_paste_genotype_gh) %>%
#   split(.$sign_paste_genotype_gh) %>%
#   map("entrezid") %>%
#   map(unique)
# 
# go_Ashr_sign_target$genotype_GH <- compareCluster(geneClusters = Ashr_sign_genotype_GH_entrezid_target,
#                                   OrgDb = org.Dm.eg.db,
#                                   fun = enrichGO, qvalueCutoff = 0.05, readable = TRUE, ont = "ALL")
# 
# 
# go_Ashr_sign_GH_simplify_target <- clusterProfiler::simplify(go_Ashr_sign_target$genotype_GH, cutoff = 0.6)
# 
# write_rds(go_Ashr_sign_GH_simplify_target, "../data_output/2024-1_diffexpr_output/go_Ashr_sign_GH_simplify_target.Rds")

ordered_names <- table(pairwise_log2fc_genotype_df_ashr_GH_target$sign_paste_genotype_gh) %>%
     sort(decreasing = TRUE) %>%
     enframe() %>%
     mutate(name = as.factor(name)) %>%
     mutate(name = fct_reorder(name, value, .desc = TRUE)) %>%
     arrange(desc(value)) %>%
     pull(name) %>%
     as.character()

# Convert to data frame
go_Ashr_sign_GH_simplify_target_df <- as.data.frame(go_Ashr_sign_GH_simplify_target)


# Get top GO terms per cluster 
top_go_df <- go_Ashr_sign_GH_simplify_target_df %>%
  group_by(Cluster) %>%
  top_n(-2, p.adjust) %>%
  ungroup() %>%
  mutate(
    GeneRatio = sapply(GeneRatio, function(x) eval(parse(text = x))), 
    Description = str_wrap(Description, width = 50),
    dummy_x = "GO"
  )
top_go_df$Cluster <- factor(top_go_df$Cluster, levels = ordered_names)
top_go_df <- top_go_df[top_go_df$Count >= 2, ]


GO_mutant_GH_fru_dsx_target <- plot_go_terms_by_cluster(top_go_df, plot_title = "Top 2 GO terms mutant/CS GH fru dsx target" ) #Version5 axis.text.y = element_text(size = 12)


GO_mutant_GH_fru_dsx_target

#All GO terms in one
dotplot(go_Ashr_sign_GH_simplify_target,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms Mutant/CantonS GH fru dsx target") +
  theme(axis.text.x = element_text(angle = 90,  hjust=0.5))


```

## Heatmap of Ashr genotype significant genes log2FoldChange of Mutant SH / CantonS SH - fru/dsx target
```{r}
genes <- unique(c(de$genotype_sh_genes_id_fru, de$genotype_sh_genes_id_dsx))

#numbers
pairwise_log2fc_genotype_df_genes <- pairwise_log2fc_genotype_df_ashr_SH %>%
  dplyr::select(gene_name, sign_paste_genotype_sh) %>%
  unique()

pairwise_log2fc_genotype_df_genes <- pairwise_log2fc_genotype_df_genes %>% filter(pairwise_log2fc_genotype_df_genes$gene_name %in% genes)

sort(table(pairwise_log2fc_genotype_df_genes$sign_paste_genotype_sh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  geom_text(aes(label = value),nudge_x = -50, size = 3) +
  scale_x_reverse() +  # Reverse bar direction
  scale_y_discrete(position = "right") +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes genotype SH fru dsx target")


#heatmap all
pairwise_log2fc_genotype_df_ashr_SH_target <- pairwise_log2fc_genotype_df_ashr_SH %>% filter(pairwise_log2fc_genotype_df_ashr_SH$gene_name %in% genes)

pairwise_log2fc_genotype_df_ngenes <- pairwise_log2fc_genotype_df_ashr_SH_target %>%
  group_by(sign_paste_genotype_sh) %>%
  summarise(n_genes = dplyr::n())

pairwise_log2fc_genotype_top_sign_combinations <- pairwise_log2fc_genotype_df_ngenes %>%
  slice_max(order_by = n_genes, n = 30) %>%
  pull(sign_paste_genotype_sh) %>%
  unique()

pairwise_log2fc_genotype_df_join <- left_join(pairwise_log2fc_genotype_df_ashr_SH_target, pairwise_log2fc_genotype_df_ngenes, by = "sign_paste_genotype_sh")

pairwise_log2fc_genotype_df_join %>%
  dplyr::filter(sign_paste_genotype_sh %in% pairwise_log2fc_genotype_top_sign_combinations) %>%
  dplyr::mutate(sign_paste_genotype_sh = fct_reorder(sign_paste_genotype_sh, dplyr::desc(n_genes))) %>%
  dplyr::mutate(
    genotype = factor(genotype, levels = c("Or47b", "Or67d", "FRU", "DSX")),
    log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white", high = "red", low = "blue") +
  facet_grid(rows = vars(sign_paste_genotype_sh), switch = "y", scales = "free_y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.border = element_rect(color = "gray", fill = NA, linewidth = 0.6),  # adds the visible frame
    strip.background = element_blank(),  # cleaner strip
    panel.spacing = unit(0.2, "lines"),   # tweak spacing between panels
    legend.position = "bottom", 
    legend.direction = "horizontal"
  ) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("Ashr SH genotype all fru/dsx targets")  +
  theme(axis.text.y = element_blank())

# GO terms
## Ashr by sign 

# Ashr_sign_genotype_SH_entrezid_target <- pairwise_log2fc_genotype_df_ashr_SH_target %>%
#   dplyr::select(entrezid, sign_paste_genotype_sh) %>%
#   split(.$sign_paste_genotype_sh) %>%
#   map("entrezid") %>%
#   map(unique)
# 
# go_Ashr_sign_target$genotype_SH <- compareCluster(geneClusters = Ashr_sign_genotype_SH_entrezid_target,
#                                   OrgDb = org.Dm.eg.db,
#                                   fun = enrichGO, qvalueCutoff = 0.05, readable = TRUE, ont = "ALL")
# 
# go_Ashr_sign_SH_simplify_target <- clusterProfiler::simplify(go_Ashr_sign_target$genotype_SH, cutoff = 0.6)
# 
# write_rds(go_Ashr_sign_target, "../data_output/2024-1_diffexpr_output/go_Ashr_sign_target.Rds")
# 
# write_rds(go_Ashr_sign_SH_simplify_target, "../data_output/2024-1_diffexpr_output/go_Ashr_sign_SH_simplify_target.Rds")

ordered_names <- table(pairwise_log2fc_genotype_df_ashr_SH_target$sign_paste_genotype_sh) %>%
     sort(decreasing = TRUE) %>%
     enframe() %>%
     mutate(name = as.factor(name)) %>%
     mutate(name = fct_reorder(name, value, .desc = TRUE)) %>%
     arrange(desc(value)) %>%
     pull(name) %>%
     as.character()

# Convert to data frame
go_Ashr_sign_SH_simplify_target_df <- as.data.frame(go_Ashr_sign_SH_simplify_target)


# Get top GO terms per cluster 
top_go_df <- go_Ashr_sign_SH_simplify_target_df %>%
  group_by(Cluster) %>%
  top_n(-2, p.adjust) %>%
  ungroup() %>%
  mutate(
    GeneRatio = sapply(GeneRatio, function(x) eval(parse(text = x))), 
    Description = str_wrap(Description, width = 50),
    dummy_x = "GO"
  )
top_go_df$Cluster <- factor(top_go_df$Cluster, levels = ordered_names)
top_go_df <- top_go_df[top_go_df$Count >= 2, ]


GO_mutant_SH_fru_dsx_target <- plot_go_terms_by_cluster(top_go_df, plot_title = "Top 2 GO terms mutant/CS SH fru dsx target") #Version5 axis.text.y = element_text(size = 12)


GO_mutant_SH_fru_dsx_target

#All GO terms in one
dotplot(go_Ashr_sign_SH_simplify_target,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms Mutant/CantonS SH fru dsx target") +
  theme(axis.text.x = element_text(angle = 90,  hjust=0.5))


```




# Normalized counts for specific genes 

```{r}
GOI_counts <- c("fru", "dsx","Dsk", "tim","Clk","cry","Act5C", "betaTub56D", "RpL13A", "RpLP0","RpL21", "RpS29", "Hmt4-20", "CCT4", "TSG101")
map(GOI_counts, plot_norm_counts , dds = deseq_obj_fitted)

plot_heatmap(norm_cts_median[GOI_counts,],"GOI",  show_row_names = T, cluster_rows = F,cluster_columns = FALSE)


```


```{r}

defense <- c("CecA2", "CecC", "DptA", "Dro", "AttA", "Mtk", "BomS2", "CBP", "Tg", "SPH93", "BomBc1", "BomBc2", "DptB", "GNBP-like3", "Dso1", "BomS5", "BomT2", "BomS3", "AttC", "AttB", "PGRP-SC2", "IM18", "Dso2", "Drs")

plot_heatmap(norm_cts_median[defense,],"CS DEGs GO:0006952 defense response",  show_row_names = T, cluster_rows = F,cluster_columns = FALSE)

```



# export to csv/excel
```{r eval=FALSE, include=FALSE}
#write.csv(norm_cts, "../data_output/2024-1_diffexpr_output/normalized_counts.csv")

#all_genes
writexl::write_xlsx(res_df, "../data_output/2024-1_diffexpr_output/all_data.xlsx")

#DEGs_housing
max_ln_DEGs_housing <- max(lengths(comp_list$housing_all_symbol))
df_fixed_DEGs_housing <- as.data.frame(do.call(cbind, lapply(comp_list$housing_all_symbol, `length<-`, max_ln_DEGs_housing)))
writexl::write_xlsx(df_fixed_DEGs_housing, "../data_output/2024-1_diffexpr_output/DEGs_housing.xlsx")

#DEGs_genotype_GH
max_ln_DEGs_genotype_GH <- max(lengths(comp_list$genotype_gh_all_symbol))
df_fixed_DEGs_genotype_GH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_gh_all_symbol, `length<-`, max_ln_DEGs_genotype_GH)))
writexl::write_xlsx(df_fixed_DEGs_genotype_GH, "../data_output/2024-1_diffexpr_output/DEGs_genotype_GH.xlsx")

#DEGs_genotype_SH
max_ln_DEGs_genotype_SH <- max(lengths(comp_list$genotype_sh_all_symbol))
df_fixed_DEGs_genotype_SH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_sh_all_symbol, `length<-`, max_ln_DEGs_genotype_SH)))
writexl::write_xlsx(df_fixed_DEGs_genotype_SH, "../data_output/2024-1_diffexpr_output/DEGs_genotype_SH.xlsx")


#GO_housing
df_GO_housing <- as.data.frame(go_housing$all_entrezid@compareClusterResult)
writexl::write_xlsx(df_GO_housing, "../data_output/2024-1_diffexpr_output/GO_housing.xlsx")

#GO_genotype_GH
df_GO_genotype_GH <- as.data.frame(go_genotype$gh_all_entrezid@compareClusterResult)
writexl::write_xlsx(df_GO_genotype_GH, "../data_output/2024-1_diffexpr_output/GO_genotype_GH.xlsx")

#GO_genotype_SH
df_GO_genotype_SH <- as.data.frame(go_genotype$sh_all_entrezid@compareClusterResult)
writexl::write_xlsx(df_GO_genotype_SH, "../data_output/2024-1_diffexpr_output/GO_genotype_SH.xlsx")


#KEGG_housing
df_KEGG_housing <- as.data.frame(KEGG_housing$all_entrezid@compareClusterResult)
writexl::write_xlsx(df_KEGG_housing, "../data_output/2024-1_diffexpr_output/KEGG_housing.xlsx")

#KEGG_genotype_GH
df_KEGG_genotype_GH <- as.data.frame(KEGG_genotype$gh_all_entrezid@compareClusterResult)
writexl::write_xlsx(df_KEGG_genotype_GH, "../data_output/2024-1_diffexpr_output/KEGG_genotype_GH.xlsx")

#KEGG_genotype_SH
df_KEGG_genotype_SH <- as.data.frame(KEGG_genotype$sh_all_entrezid@compareClusterResult)
writexl::write_xlsx(df_KEGG_genotype_SH, "../data_output/2024-1_diffexpr_output/KEGG_genotype_SH.xlsx")


#reactome_housing
df_reactome_housing <- as.data.frame(reactome_housing$all_entrezid@compareClusterResult)
writexl::write_xlsx(df_reactome_housing, "../data_output/2024-1_diffexpr_output/reactome_housing.xlsx")

#reactome_genotype_GH
df_reactome_genotype_GH <- as.data.frame(reactome_genotype$gh_all_entrezid@compareClusterResult)
writexl::write_xlsx(df_reactome_genotype_GH, "../data_output/2024-1_diffexpr_output/reactome_genotype_GH.xlsx")

#reactome_genotype_SH
df_reactome_genotype_SH <- as.data.frame(reactome_genotype$sh_all_entrezid@compareClusterResult)
writexl::write_xlsx(df_reactome_genotype_SH, "../data_output/2024-1_diffexpr_output/reactome_genotype_SH.xlsx")


#DEGs_with_directions_GH
writexl::write_xlsx(pairwise_log2fc_genotype_df_ashr_GH, "../data_output/2024-1_diffexpr_output/DEGs_with_directions_GH.xlsx")

#DEGs_with_directions_SH
writexl::write_xlsx(pairwise_log2fc_genotype_df_ashr_SH, "../data_output/2024-1_diffexpr_output/DEGs_with_directions_SH.xlsx")

#GO_DEGs_with_directions_GH
writexl::write_xlsx(go_Ashr_sign_GH_simplify_df, "../data_output/2024-1_diffexpr_output/GO_DEGs_with_directions_GH.xlsx")

#GO_DEGs_with_directions_SH
writexl::write_xlsx(go_Ashr_sign_SH_simplify_df, "../data_output/2024-1_diffexpr_output/GO_DEGs_with_directions_SH.xlsx")



#DEGs_with_directions_GH_target
writexl::write_xlsx(pairwise_log2fc_genotype_df_ashr_GH_target, "../data_output/2024-1_diffexpr_output/DEGs_with_directions_GH_target.xlsx")

#DEGs_with_directions_SH_target
writexl::write_xlsx(pairwise_log2fc_genotype_df_ashr_SH_target, "../data_output/2024-1_diffexpr_output/DEGs_with_directions_SH_target.xlsx")

#GO_DEGs_with_directions_GH_target
writexl::write_xlsx(go_Ashr_sign_GH_simplify_target_df, "../data_output/2024-1_diffexpr_output/GO_DEGs_with_directions_GH_target.xlsx")

#GO_DEGs_with_directions_SH_target
writexl::write_xlsx(go_Ashr_sign_SH_simplify_target_df, "../data_output/2024-1_diffexpr_output/GO_DEGs_with_directions_SH_target.xlsx")



#log2FC_housing
df <- as.data.frame(log2fc_mat_housing)
df <- cbind(gene = rownames(df), df)
writexl::write_xlsx(df, "../data_output/2024-1_diffexpr_output/log2FC_housing.xlsx")

#log2FC_genotype_GH
df <- as.data.frame(log2fc_mat_genotype_gh)
df <- cbind(gene = rownames(df), df)
writexl::write_xlsx(df, "../data_output/2024-1_diffexpr_output/log2FC_genotype_GH.xlsx")

#log2FC_genotype_SH
df <- as.data.frame(log2fc_mat_genotype_sh)
df <- cbind(gene = rownames(df), df)
writexl::write_xlsx(df, "../data_output/2024-1_diffexpr_output/log2FC_genotype_SH.xlsx")

```



