---
title: "Figure 3 Correlation of the changes on transcriptome and chromatin"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
date: '2024-02-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```


```{r}
# Libraries
library(tidyverse)
library(ComplexHeatmap) # Heatmaps
library(DESeq2) 
library(ggVennDiagram) 
library(clusterProfiler) # Go terms
library(org.Dm.eg.db) # GO annotation
library(circlize) # Colors

```


```{r}
# Functions
get_genes_in_set <- function(gene_set, gene_universe) {
  return(map_lgl(gene_universe, ~ .x %in% gene_set))
}

get_overlap_genes <- function(named_list_gene_sets) {
  # Get all unique genes
  gene_universe <- na.omit(unique(unlist(named_list_gene_sets))) # Collapse list of vectors into a single vector, get unique genes
  
  named_list_gene_sets <- map(named_list_gene_sets, # For each list:
                              # For each gene:
                              # Is gene in list? -> get logical for each list
                              get_genes_in_set,
                              gene_universe = gene_universe)
  
  # Return lgl matrix of presence / absence for each gene
  named_list_gene_sets <- as.data.frame(named_list_gene_sets)
  rownames(named_list_gene_sets) <- gene_universe
  return(named_list_gene_sets)
  
}
# Convert symbol to entrezid
tr_symbol2entrezid <- function(.x, symbol_etrez_map){
  symbol_etrez_map[.x]
}

```


```{r}
# Read chromatin data

# Read data

data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```


```{r}
# DESeq files
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```

```{r}
# Results joined files

res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```


```{r}
# Long data frames for volcano plots
res_long_h3k4me3_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_h3k4me3_df.Rds")
res_long_rnapolii_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_rnapolii_df.Rds")

```



```{r}

# Read RNA data

# Read data

data_dir <- "../data_output/2024-1_diffexpr_input/"
```

```{r}
# DESeq files raw

deseq_files <- list.files(data_dir,pattern = "[^$]+rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


```{r}
# DESeq files fitted 

deseq_obj_fitted <- readRDS("../data_output/2024-1_diffexpr_output/social_mutants_housing_lrt_deseq_obj_fitted.Rds")
```


```{r}
# Results joined files

res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```

```{r}
# Comparisons list
comp_list <- readRDS( "../data_output/2024-01_diffbind_cutnrun/comp_list.Rds")
# Lists of differentially expressed genes by comparison 
comp_list <- c(comp_list,readRDS(file = "../data_output/2024-1_diffexpr_output/comp_list.Rds"))

```

```{r}
# Ranges connected to genes
res_gr_h3k4me3_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_genes.Rds")
res_gr_rnapolii_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes.Rds")

```

```{r}
# res_long_df
res_long_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/res_long_df.Rds")
res_long_df_diff_any <- res_long_df %>%
  drop_na(padj) %>%
  filter(padj < 0.05)

```



```{r}
# Make lists for venn diagrams 

# Venn diagram with comparisons:
 
## GH: all to CS, within the same genotype between RNAseq and CUT&RUN

tr_range2gene <- function(res_id,gr_obj) {
  unique(gr_obj$SYMBOL[gr_obj$range_id %in% res_id])
}
# All genes without considering direction of change
# Translate list gh all from rangeid to gene name
comp_list$genotype_gh_all_h3k4me3_geneid <- map(comp_list$genotype_gh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_all_rnapolii_geneid <- map(comp_list$genotype_gh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_all_cutnrun_rna_list <- c(comp_list$genotype_gh_all_symbol,comp_list$genotype_gh_all_h3k4me3_geneid, comp_list$genotype_gh_all_rnapolii_geneid)


# Genes that go up

# Translate list gh up
comp_list$genotype_gh_up_h3k4me3_geneid <- map(comp_list$genotype_gh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_up_rnapolii_geneid <- map(comp_list$genotype_gh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_up_cutnrun_rna_list <- c(comp_list$genotype_gh_up_symbol,comp_list$genotype_gh_up_h3k4me3_geneid,comp_list$genotype_gh_up_rnapolii_geneid)

# Genes that go DOWN

# Translate list gh down
comp_list$genotype_gh_down_h3k4me3_geneid <- map(comp_list$genotype_gh_down_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_down_rnapolii_geneid <- map(comp_list$genotype_gh_down_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_down_cutnrun_rna_list <- c(comp_list$genotype_gh_down_symbol,comp_list$genotype_gh_down_h3k4me3_geneid,comp_list$genotype_gh_down_rnapolii_geneid)

# Same but for Single House

# ALL

# Translate list sh all
comp_list$genotype_sh_all_h3k4me3_geneid <- map(comp_list$genotype_sh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_all_rnapolii_geneid <- map(comp_list$genotype_sh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_all_cutnrun_rna_list <- c(comp_list$genotype_sh_all_symbol,comp_list$genotype_sh_all_h3k4me3_geneid,comp_list$genotype_sh_all_rnapolii_geneid)

# UP

# Translate list sh up
comp_list$genotype_sh_up_h3k4me3_geneid <- map(comp_list$genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_up_rnapolii_geneid <- map(comp_list$genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_up_cutnrun_rna_list <- c(comp_list$genotype_sh_up_symbol,comp_list$genotype_sh_up_h3k4me3_geneid,comp_list$genotype_sh_up_rnapolii_geneid)

# Translate list sh down
comp_list$genotype_sh_down_h3k4me3_geneid <- map(comp_list$genotype_sh_down_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_down_rnapolii_geneid <- map(comp_list$genotype_sh_down_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_down_cutnrun_rna_list <- c(comp_list$genotype_sh_down_symbol,comp_list$genotype_sh_down_h3k4me3_geneid,comp_list$genotype_sh_down_rnapolii_geneid)

# Down


# Translate list gh down
comp_list$genotype_sh_down_h3k4me3_geneid <- map(comp_list$genotype_sh_down_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_down_rnapolii_geneid <- map(comp_list$genotype_sh_down_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_down_cutnrun_rna_list <- c(comp_list$genotype_sh_down_symbol,comp_list$genotype_sh_down_h3k4me3_geneid,comp_list$genotype_sh_down_rnapolii_geneid)

#remove NA
remove_na_recursive <- function(lst) {
  lapply(lst, function(x) {
    if (is.list(x)) {
      remove_na_recursive(x)  # Recursively clean nested lists
    } else {
      x[!is.na(x)]  # Remove NA from atomic vectors
    }
  })
}

comp_list <- remove_na_recursive (comp_list)

```





# Venn diagram with comparisons:
## GH: all to CS, within the same genotype between RNAseq and CUT&RUN

### ALL 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list)
```


```{r}
# Subset comparisons lists by specific genotype 
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
   scale_fill_viridis_c() +
   ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

```

Genes 

```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```

### UP 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("dsxmut vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("frumut vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("Or47bmut vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("Or67dmut vs CantonS GH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
GH_everything_up <- list()

GH_everything_up$GH_Or47b_up <- get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut)) %>%
  row.names()

GH_everything_up$GH_Or67d_up <-
get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut)) %>%
  row.names()

GH_everything_up$GH_fru_up <- get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut)) %>%
  row.names()

GH_everything_up$GH_dsx_up <- get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut)) %>%
  row.names()

```


### DOWN 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("dsxmut vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("frumut vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("Or47bmut vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("Or67dmut vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))
```



```{r}
GH_everything_down <- list()

GH_everything_down$GH_Or47b_down <- get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut)) %>%
  row.names()

GH_everything_down$GH_Or67d_down <-
get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut)) %>%
  row.names()

GH_everything_down$GH_fru_down <- get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut)) %>%
  row.names()

GH_everything_down$GH_dsx_down <- get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut)) %>%
  row.names()

```


## SH: all to a CS, within the same genotype between RNAseq and CUT&RUN

### ALL 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list)
```


```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 6 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))
```

Genes 
```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```



### UP 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("dsxmut vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("frumut vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("Or47bmut vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#fee2e2", high = "#ff7777")+
  ggtitle("Or67dmut vs CantonS sh UP") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
SH_everything_up <- list()

SH_everything_up$SH_Or47b_up <- get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut)) %>%
  row.names()

SH_everything_up$SH_Or67d_up <-
get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut)) %>%
  row.names()

SH_everything_up$SH_fru_up <- get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut)) %>%
  row.names()

SH_everything_up$SH_dsx_up <- get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut)) %>%
  row.names()

```




### DOWN 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("dsxmut vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("frumut vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("Or47bmut vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "black", label_size = 6 ) +
  scale_fill_gradient(low = "#d8eff8", high = "skyblue2")+
  ggtitle("Or67dmut vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))
```


```{r}
SH_everything_down <- list()

SH_everything_down$SH_Or47b_down <- get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut)) %>%
  row.names()

SH_everything_down$SH_Or67d_down <-
get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut)) %>%
  row.names()

SH_everything_down$SH_fru_down <- get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut)) %>%
  row.names()

SH_everything_down$SH_dsx_down <- get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut)) %>%
  row.names()

```


# GO terms of pairwise comparisons overlaps:

```{r}
symbol_etrez_map_df <- clusterProfiler::bitr(geneID = res_df$gene_name, fromType = "SYMBOL",toType ="ENTREZID",OrgDb = org.Dm.eg.db )
symbol_etrez_map <- symbol_etrez_map_df$ENTREZ 
names(symbol_etrez_map) <-  symbol_etrez_map_df$SYMBOL

entrezid <- list()
entrezid$GH_everything_up$GH_Or47b_up <- map(GH_everything_up$GH_Or47b_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$GH_everything_up$GH_Or67d_up <- map(GH_everything_up$GH_Or67d_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$GH_everything_up$GH_fru_up <- map(GH_everything_up$GH_fru_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$GH_everything_up$GH_dsx_up <- map(GH_everything_up$GH_dsx_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)


entrezid$GH_everything_down$GH_Or47b_down <- map(GH_everything_down$GH_Or47b_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$GH_everything_down$GH_Or67d_down <- map(GH_everything_down$GH_Or67d_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$GH_everything_down$GH_fru_down <- map(GH_everything_down$GH_fru_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$GH_everything_down$GH_dsx_down <- map(GH_everything_down$GH_dsx_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)


entrezid$SH_everything_up$SH_Or47b_up <- map(SH_everything_up$SH_Or47b_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$SH_everything_up$SH_Or67d_up <- map(SH_everything_up$SH_Or67d_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$SH_everything_up$SH_fru_up <- map(SH_everything_up$SH_fru_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$SH_everything_up$SH_dsx_up <- map(SH_everything_up$SH_dsx_up, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)


entrezid$SH_everything_down$SH_Or47b_down <- map(SH_everything_down$SH_Or47b_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$SH_everything_down$SH_Or67d_down <- map(SH_everything_down$SH_Or67d_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$SH_everything_down$SH_fru_down <- map(SH_everything_down$SH_fru_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

entrezid$SH_everything_down$SH_dsx_down <- map(SH_everything_down$SH_dsx_down, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)



```

### GH


#### UP 

```{r}
GO_list <- list()
GO_list$GH_everything_up_GO <-  compareCluster(geneClusters = entrezid$GH_everything_up,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$GH_everything_up_GO,showCategory = 15, by='GeneRatio') +theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) +  ggtitle("GO terms Mutant vs CS GH UP") 
```

```{r}
GO_list$GH_everything_up_GO@compareClusterResult
```


#### Down 

```{r}
GO_list$GH_everything_down_GO <-  compareCluster(geneClusters = entrezid$GH_everything_down,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$GH_everything_down_GO,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 40)) +theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11))+  ggtitle("GO terms Mutant vs CS GH DOWN")
```

```{r}
GO_list$GH_everything_down_GO@compareClusterResult
```



#Or only

```{r}
Or_GO_everything_GH <- list()
Or_GO_everything_GH$GH_Or47b_up <- entrezid$GH_everything_up$GH_Or47b_up
Or_GO_everything_GH$GH_Or47b_down <- entrezid$GH_everything_down$GH_Or47b_down
Or_GO_everything_GH$GH_Or67d_up <- entrezid$GH_everything_up$GH_Or67d_up
Or_GO_everything_GH$GH_Or67d_down <- entrezid$GH_everything_down$GH_Or67d_down

GO_list$Or_GO_everything_GH_GO <-  compareCluster(geneClusters = Or_GO_everything_GH,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$Or_GO_everything_GH_GO,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + 
 ggtitle("GO terms Or Mutant vs CS GH top15")


Or_GO_everything_GH_simp <- clusterProfiler::simplify(GO_list$Or_GO_everything_GH_GO, cutoff = 0.5)

dotplot(Or_GO_everything_GH_simp,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + ggtitle("GO terms Or Mutant vs CS GH top15 simplify")


```


#TF only

```{r}
TF_GO_everything_GH <- list()
TF_GO_everything_GH$GH_fru_up <- entrezid$GH_everything_up$GH_fru_up
TF_GO_everything_GH$GH_fru_down <- entrezid$GH_everything_down$GH_fru_down
TF_GO_everything_GH$GH_dsx_up <- entrezid$GH_everything_up$GH_dsx_up
TF_GO_everything_GH$GH_dsx_down <- entrezid$GH_everything_down$GH_dsx_down

GO_list$TF_GO_everything_GH_GO <-  compareCluster(geneClusters = TF_GO_everything_GH,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$TF_GO_everything_GH_GO,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + 
 ggtitle("GO terms TF Mutant vs CS GH top15")

TF_GO_everything_GH_simp <- clusterProfiler::simplify(GO_list$TF_GO_everything_GH_GO, cutoff = 0.5)

dotplot(TF_GO_everything_GH_simp,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 50))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + ggtitle("GO terms TF Mutant vs CS GH top15 simplify")

```




### SH


#### UP 

```{r}
GO_list$SH_everything_up_GO <-  compareCluster(geneClusters = entrezid$SH_everything_up,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$SH_everything_up_GO,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 40)) +theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + 
  ggtitle("GO terms Mutant vs CS SH UP")

GO_list$SH_everything_up_GO@compareClusterResult
```

#### Down 

```{r}
GO_list$SH_everything_down_GO <-  compareCluster(geneClusters = entrezid$SH_everything_down,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$SH_everything_down_GO,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 40))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + 
 ggtitle("GO terms Mutant vs CS SH DOWN")

GO_list$SH_everything_down_GO@compareClusterResult
  
```


#Or only

```{r}
Or_GO_everything_SH <- list()
Or_GO_everything_SH$SH_Or47b_up <- entrezid$SH_everything_up$SH_Or47b_up
Or_GO_everything_SH$SH_Or47b_down <- entrezid$SH_everything_down$SH_Or47b_down
Or_GO_everything_SH$SH_Or67d_up <- entrezid$SH_everything_up$SH_Or67d_up
Or_GO_everything_SH$SH_Or67d_down <- entrezid$SH_everything_down$SH_Or67d_down

GO_list$Or_GO_everything_SH_GO <-  compareCluster(geneClusters = Or_GO_everything_SH,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$Or_GO_everything_SH_GO,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 55))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + 
 ggtitle("GO terms Or Mutant vs CS SH top15")

Or_GO_everything_SH_simp <- clusterProfiler::simplify(GO_list$Or_GO_everything_SH_GO, cutoff = 0.5)

dotplot(Or_GO_everything_SH_simp, showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 55))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + ggtitle("GO terms Or Mutant vs CS SH top15 simplify")

```


#TF only

```{r}
TF_GO_everything_SH <- list()
TF_GO_everything_SH$SH_fru_up <- entrezid$SH_everything_up$SH_fru_up
TF_GO_everything_SH$SH_fru_down <- entrezid$SH_everything_down$SH_fru_down
TF_GO_everything_SH$SH_dsx_up <- entrezid$SH_everything_up$SH_dsx_up
TF_GO_everything_SH$SH_dsx_down <- entrezid$SH_everything_down$SH_dsx_down

GO_list$TF_GO_everything_SH_GO <-  compareCluster(geneClusters = TF_GO_everything_SH,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")

dotplot(GO_list$TF_GO_everything_SH_GO,showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 60))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + 
 ggtitle("GO terms TF Mutant vs CS SH top15")

TF_GO_everything_SH_simp <- clusterProfiler::simplify(GO_list$TF_GO_everything_SH_GO, cutoff = 0.5)

dotplot(TF_GO_everything_SH_simp, showCategory = 15, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 60))+ theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) + ggtitle("GO terms TF Mutant vs CS SH top15 simplify")
```








# Heatmap summarizing all genes with at least one concordant RNA/chromatin change


This heatmap contains any gene that:
- Is differentially expressed in any mutant SH / CantonS SH pairwise comparison in RNA-seq. 
- Overlaps a differential peak in any mutant SH / CantonS SH pairwise comparison in CUT&RUN.

Only single house comparison 

```{r}
genotype_sh_up_cutnrun_rna_list <- comp_list$genotype_sh_up_cutnrun_rna_list
genotype_sh_down_cutnrun_rna_list <- comp_list$genotype_sh_down_cutnrun_rna_list                      

# ADD direction to sample names
names(genotype_sh_up_cutnrun_rna_list) <- paste0(names(genotype_sh_up_cutnrun_rna_list), "_UP")
names(genotype_sh_down_cutnrun_rna_list)<- paste0(names(genotype_sh_down_cutnrun_rna_list), "_DOWN")


genotype_sh_overlap_genes <- get_overlap_genes(c(genotype_sh_up_cutnrun_rna_list, genotype_sh_down_cutnrun_rna_list))

# Find genes that show overlap of RNA and CUT&RUN 
gene_mat <- genotype_sh_overlap_genes %>%
  filter( (DSX_SH_UP & (H3K4me3_dsxmut_UP | RNAPolII_dsxmut_UP)) |
            (DSX_SH_DOWN & (H3K4me3_dsxmut_DOWN | RNAPolII_dsxmut_DOWN)) |
            (FRU_SH_UP & (H3K4me3_frumut_UP | RNAPolII_frumut_UP)) | 
            (FRU_SH_DOWN & (H3K4me3_frumut_DOWN | RNAPolII_frumut_DOWN)) |
            (Or47b_SH_UP & (H3K4me3_Or47bmut_UP | RNAPolII_Or47bmut_UP)) | 
            (Or47b_SH_DOWN & (H3K4me3_Or47bmut_DOWN | RNAPolII_Or47bmut_DOWN)) |
            (Or67d_SH_UP & (H3K4me3_Or67dmut_UP | RNAPolII_Or67dmut_UP)) | 
            (Or67d_SH_DOWN & (H3K4me3_Or67dmut_DOWN | RNAPolII_Or67dmut_DOWN)) 
  )

# Adding back the rownames to matrix
SYMBOLs_row_mat <- rownames(gene_mat)

# Changing the type of variables 
gene_mat <- map_dfc(gene_mat, as.numeric) 
gene_mat <- gene_mat[, c("Or47b_SH_UP", "H3K4me3_Or47bmut_UP", "RNAPolII_Or47bmut_UP", 
                         "Or47b_SH_DOWN", "H3K4me3_Or47bmut_DOWN", "RNAPolII_Or47bmut_DOWN",
                         "Or67d_SH_UP", "H3K4me3_Or67dmut_UP", "RNAPolII_Or67dmut_UP",
                         "Or67d_SH_DOWN", "H3K4me3_Or67dmut_DOWN", "RNAPolII_Or67dmut_DOWN",
                         "FRU_SH_UP", "H3K4me3_frumut_UP", "RNAPolII_frumut_UP",
                         "FRU_SH_DOWN", "H3K4me3_frumut_DOWN", "RNAPolII_frumut_DOWN",
                         "DSX_SH_UP", "H3K4me3_dsxmut_UP","RNAPolII_dsxmut_UP",
                         "DSX_SH_DOWN","H3K4me3_dsxmut_DOWN","RNAPolII_dsxmut_DOWN"  )]
rownames(gene_mat) <-  SYMBOLs_row_mat 



mat_df <- as.data.frame(gene_mat)
mat_df$gene <- row.names(gene_mat)
mat_df_long <- reshape2::melt(mat_df, id.vars="gene")


# Define the columns for red and blue
red_columns <- c("Or47b_SH_UP", "H3K4me3_Or47bmut_UP", "RNAPolII_Or47bmut_UP",
                 "Or67d_SH_UP", "H3K4me3_Or67dmut_UP", "RNAPolII_Or67dmut_UP", 
                 "FRU_SH_UP", "H3K4me3_frumut_UP", "RNAPolII_frumut_UP",
                 "DSX_SH_UP", "H3K4me3_dsxmut_UP", "RNAPolII_dsxmut_UP")

blue_columns <- c("Or47b_SH_DOWN", "H3K4me3_Or47bmut_DOWN", "RNAPolII_Or47bmut_DOWN",
                  "Or67d_SH_DOWN", "H3K4me3_Or67dmut_DOWN", "RNAPolII_Or67dmut_DOWN",
                  "FRU_SH_DOWN", "H3K4me3_frumut_DOWN", "RNAPolII_frumut_DOWN",
                  "DSX_SH_DOWN", "H3K4me3_dsxmut_DOWN", "RNAPolII_dsxmut_DOWN")

# Create the 'color' column
mat_df_long <- mat_df_long %>%
  mutate(color = case_when(
    variable %in% red_columns & value == 1 ~ "#ff7777",    # Red for specific variables with value 1
    variable %in% blue_columns & value == 1 ~ "skyblue",  # Blue for other specific variables with value 1
    TRUE ~ "white"                                    # Default to white for others
  ))

Concordant_RNA_chromatin_SH <- ggplot(mat_df_long, aes(x = variable, y = gene, fill = color)) +
  geom_tile(color = "white") +
  scale_fill_identity() +  # Use the colors directly from the data
  theme_minimal() +
  labs(title = "Concordant RNA/chromatin change SH",
       x = "condition",
       y = "genes") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

Concordant_RNA_chromatin_SH

```

Only group house comparison 

```{r}
genotype_gh_up_cutnrun_rna_list <- comp_list$genotype_gh_up_cutnrun_rna_list
genotype_gh_down_cutnrun_rna_list <- comp_list$genotype_gh_down_cutnrun_rna_list                      

# ADD direction to sample names
names(genotype_gh_up_cutnrun_rna_list) <- paste0(names(genotype_gh_up_cutnrun_rna_list), "_UP")
names(genotype_gh_down_cutnrun_rna_list)<- paste0(names(genotype_gh_down_cutnrun_rna_list), "_DOWN")


genotype_gh_overlap_genes <- get_overlap_genes(c(genotype_gh_up_cutnrun_rna_list, genotype_gh_down_cutnrun_rna_list))

# Find genes that show overlap of RNA and CUT&RUN 
gene_mat <- genotype_gh_overlap_genes %>%
  filter( (DSX_GH_UP & (H3K4me3_dsxmut_UP | RNAPolII_dsxmut_UP)) |
            (DSX_GH_DOWN & (H3K4me3_dsxmut_DOWN | RNAPolII_dsxmut_DOWN)) |
            (FRU_GH_UP & (H3K4me3_frumut_UP | RNAPolII_frumut_UP)) | 
            (FRU_GH_DOWN & (H3K4me3_frumut_DOWN | RNAPolII_frumut_DOWN)) |
            (Or47b_GH_UP & (H3K4me3_Or47bmut_UP | RNAPolII_Or47bmut_UP)) | 
            (Or47b_GH_DOWN & (H3K4me3_Or47bmut_DOWN | RNAPolII_Or47bmut_DOWN)) |
            (Or67d_GH_UP & (H3K4me3_Or67dmut_UP | RNAPolII_Or67dmut_UP)) | 
            (Or67d_GH_DOWN & (H3K4me3_Or67dmut_DOWN | RNAPolII_Or67dmut_DOWN)) 
  )

# Adding back the rownames to matrix
SYMBOLs_row_mat <- rownames(gene_mat)

# Changing the type of variables 
gene_mat <- map_dfc(gene_mat, as.numeric) 
gene_mat <- gene_mat[, c("Or47b_GH_UP", "H3K4me3_Or47bmut_UP", "RNAPolII_Or47bmut_UP", 
                         "Or47b_GH_DOWN", "H3K4me3_Or47bmut_DOWN", "RNAPolII_Or47bmut_DOWN",
                         "Or67d_GH_UP", "H3K4me3_Or67dmut_UP", "RNAPolII_Or67dmut_UP",
                         "Or67d_GH_DOWN", "H3K4me3_Or67dmut_DOWN", "RNAPolII_Or67dmut_DOWN",
                         "FRU_GH_UP", "H3K4me3_frumut_UP", "RNAPolII_frumut_UP",
                         "FRU_GH_DOWN", "H3K4me3_frumut_DOWN", "RNAPolII_frumut_DOWN",
                         "DSX_GH_UP", "H3K4me3_dsxmut_UP","RNAPolII_dsxmut_UP",
                         "DSX_GH_DOWN","H3K4me3_dsxmut_DOWN","RNAPolII_dsxmut_DOWN"  )]
rownames(gene_mat) <-  SYMBOLs_row_mat 



mat_df <- as.data.frame(gene_mat)
mat_df$gene <- row.names(gene_mat)
mat_df_long <- reshape2::melt(mat_df, id.vars="gene")


# Define the columns for red and blue
red_columns <- c("Or47b_GH_UP", "H3K4me3_Or47bmut_UP", "RNAPolII_Or47bmut_UP",
                 "Or67d_GH_UP", "H3K4me3_Or67dmut_UP", "RNAPolII_Or67dmut_UP", 
                 "FRU_GH_UP", "H3K4me3_frumut_UP", "RNAPolII_frumut_UP",
                 "DSX_GH_UP", "H3K4me3_dsxmut_UP", "RNAPolII_dsxmut_UP")

blue_columns <- c("Or47b_GH_DOWN", "H3K4me3_Or47bmut_DOWN", "RNAPolII_Or47bmut_DOWN",
                  "Or67d_GH_DOWN", "H3K4me3_Or67dmut_DOWN", "RNAPolII_Or67dmut_DOWN",
                  "FRU_GH_DOWN", "H3K4me3_frumut_DOWN", "RNAPolII_frumut_DOWN",
                  "DSX_GH_DOWN", "H3K4me3_dsxmut_DOWN", "RNAPolII_dsxmut_DOWN")

# Create the 'color' column
mat_df_long <- mat_df_long %>%
  mutate(color = case_when(
    variable %in% red_columns & value == 1 ~ "#ff7777",    # Red for specific variables with value 1
    variable %in% blue_columns & value == 1 ~ "skyblue",  # Blue for other specific variables with value 1
    TRUE ~ "white"                                    # Default to white for others
  ))

Concordant_RNA_chromatin_GH <- ggplot(mat_df_long, aes(x = variable, y = gene, fill = color)) +
  geom_tile(color = "white") +
  scale_fill_identity() +  # Use the colors directly from the data
  theme_minimal() +
  labs(title = "Concordant RNA/chromatin change GH",
       x = "condition",
       y = "genes") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

Concordant_RNA_chromatin_GH

```

