---
title: "Figure 2 Chromatin changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
date: '2024-02-13'
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r}
# Libraries
library(stringr)
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
library(circlize)
library(clusterProfiler)
library(csaw)
options(scipen = 999)
```

```{r}
# Functions
get_lgl_from_rownames <- function(row_names, genes_to_subset) {
  return((str_split(row_names,pattern = "-",n = 2) %>% map_chr(1)) %in% genes_to_subset)
}

# plot z score matrix
plot_heatmap <- function(mat, plot_title, ...) {
  # Define the desired column order
  desired_order <- c("CS_GH", "CS_SH", "Or47bmut_GH", "Or47bmut_SH",
                     "Or67dmut_GH", "Or67dmut_SH", "frumut_GH", "frumut_SH",
                     "dsxmut_GH", "dsxmut_SH")

  # Find matching column names and reorder them
  matching_cols <- colnames(mat)[str_detect(colnames(mat), paste(desired_order, collapse = "|"))]

  # Reorder columns based on `desired_order`
  ordered_cols <- unlist(lapply(desired_order, function(x) matching_cols[str_detect(matching_cols, x)]))

  # Subset the matrix with the new column order
  mat_reordered <- mat[, ordered_cols, drop = FALSE]

  # Plot the heatmap
  ComplexHeatmap::Heatmap(mat = t(scale(t(mat_reordered),center = TRUE,scale = TRUE)), # z score
           cluster_columns = FALSE,
           column_title = plot_title,
           heatmap_legend_param = list(title = "Z score",
                                       legend_height = unit(2, "in")), # size of legend
           raster_device = "agg_png", # Format to export the raster 
           ... ) 
}


# log2fc matrix
plot_heatmap_log2fc <- function(mat, ...) {
  Heatmap(mat = mat,
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "log2FC",
                                      legend_height = unit(2, "in")) , ... )
}


# Data table that is exportable to CSV file
print_exportable_genes <- function(genes){
  DT::datatable(genes,extensions = 'Buttons',
                options = list(dom= 'Bfrtip',buttons = c('copy', 'csv')))
}

```

```{r}
# Read data

data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```

```{r}
# DESeq files for lrt
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```

```{r}
# Results joined files
res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```

```{r}
# VST data for PCA
vsd_h3k4me3 <- readRDS("../data_output/2024-01_diffbind_cutnrun/vsd_h3k4me3.Rds")
vsd_rnapolii <- readRDS("../data_output/2024-01_diffbind_cutnrun/vsd_rnapolii.Rds")

```

```{r}
# Long data frames for volcano plots
res_long_h3k4me3_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_h3k4me3_df.Rds")
res_long_rnapolii_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_rnapolii_df.Rds")


#Gr files 
res_gr_h3k4me3 <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3.Rds")
res_gr_rnapolii <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii.Rds")


res_gr_h3k4me3_all_uscs_anno <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_all_uscs_anno.Rds")
res_gr_rnapolii_all_uscs_anno <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_all_uscs_anno.Rds")


```

```{r}
# Normalized counts for heatmaps
norm_cts_h3k4me3 <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3.Rds")
norm_cts_rnapolii <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii.Rds")

# Median counts for heatmaps

norm_cts_h3k4me3_median <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3_median.Rds")
norm_cts_rnapolii_median <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii_median.Rds")

# Differential peaks
de_genotype <- readRDS( "../data_output/2024-01_diffbind_cutnrun/de_genotype.Rds")

# log2fc matrix
log2fc_mat_h3k4me3_genotype_gh <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_gh.Rds")
log2fc_mat_h3k4me3_genotype_sh <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_sh.Rds")
log2fc_mat_rnapolii_genotype_gh <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_gh.Rds")
log2fc_mat_rnapolii_genotype_sh <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_sh.Rds")

```

```{r}
# Ranges connected to genes
res_gr_h3k4me3_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_genes.Rds")
res_gr_rnapolii_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes.Rds")

```

```{r}
# Comparisons list
comp_list <- readRDS( "../data_output/2024-01_diffbind_cutnrun/comp_list.Rds")

```



```{r}
#comp_list_add_gene_name
 
## GH: all to CS, within the same genotype between RNAseq and CUT&RUN

tr_range2gene <- function(res_id,gr_obj) {
  unique(gr_obj$SYMBOL[gr_obj$range_id %in% res_id])
}
# All genes without considering direction of change
# Translate list gh all from rangeid to gene name
comp_list$genotype_gh_all_h3k4me3_geneid <- map(comp_list$genotype_gh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_all_rnapolii_geneid <- map(comp_list$genotype_gh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_all_cutnrun_rna_list <- c(comp_list$genotype_gh_all_symbol,comp_list$genotype_gh_all_h3k4me3_geneid, comp_list$genotype_gh_all_rnapolii_geneid)


# Genes that go up

# Translate list gh up
comp_list$genotype_gh_up_h3k4me3_geneid <- map(comp_list$genotype_gh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_up_rnapolii_geneid <- map(comp_list$genotype_gh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_up_cutnrun_rna_list <- c(comp_list$genotype_gh_up_symbol,comp_list$genotype_gh_up_h3k4me3_geneid,comp_list$genotype_gh_up_rnapolii_geneid)

# Genes that go DOWN

# Translate list gh down
comp_list$genotype_gh_down_h3k4me3_geneid <- map(comp_list$genotype_gh_down_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_down_rnapolii_geneid <- map(comp_list$genotype_gh_down_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_down_cutnrun_rna_list <- c(comp_list$genotype_gh_down_symbol,comp_list$genotype_gh_down_h3k4me3_geneid,comp_list$genotype_gh_down_rnapolii_geneid)

# Same but for Single House

# ALL

# Translate list sh all
comp_list$genotype_sh_all_h3k4me3_geneid <- map(comp_list$genotype_sh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_all_rnapolii_geneid <- map(comp_list$genotype_sh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_all_cutnrun_rna_list <- c(comp_list$genotype_sh_all_symbol,comp_list$genotype_sh_all_h3k4me3_geneid,comp_list$genotype_sh_all_rnapolii_geneid)

# UP

# Translate list sh up
comp_list$genotype_sh_up_h3k4me3_geneid <- map(comp_list$genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_up_rnapolii_geneid <- map(comp_list$genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_up_cutnrun_rna_list <- c(comp_list$genotype_sh_up_symbol,comp_list$genotype_sh_up_h3k4me3_geneid,comp_list$genotype_sh_up_rnapolii_geneid)

# Translate list sh down
comp_list$genotype_sh_down_h3k4me3_geneid <- map(comp_list$genotype_sh_down_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_down_rnapolii_geneid <- map(comp_list$genotype_sh_down_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_down_cutnrun_rna_list <- c(comp_list$genotype_sh_down_symbol,comp_list$genotype_sh_down_h3k4me3_geneid,comp_list$genotype_sh_down_rnapolii_geneid)

# Down


# Translate list gh down
comp_list$genotype_sh_down_h3k4me3_geneid <- map(comp_list$genotype_sh_down_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_down_rnapolii_geneid <- map(comp_list$genotype_sh_down_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_down_cutnrun_rna_list <- c(comp_list$genotype_sh_down_symbol,comp_list$genotype_sh_down_h3k4me3_geneid,comp_list$genotype_sh_down_rnapolii_geneid)

#remove NA
remove_na_recursive <- function(lst) {
  lapply(lst, function(x) {
    if (is.list(x)) {
      remove_na_recursive(x)  # Recursively clean nested lists
    } else {
      x[!is.na(x)]  # Remove NA from atomic vectors
    }
  })
}

comp_list <- remove_na_recursive (comp_list)

```


```{r}
# Read pairwise log2fc matrices for LRT results plots
pairwise_log2fc_h3k4me3_df <- readRDS( "../data_output/2024-01_diffbind_cutnrun/pairwise_log2fc_h3k4me3_df.Rds")
pairwise_log2fc_rnapolii_df <- readRDS( "../data_output/2024-01_diffbind_cutnrun/pairwise_log2fc_rnapolii_df.Rds")
```

```{r}
# Normalized counts matrices but rows correspond to one gene only
norm_cts_h3k4me3_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3_gene.Rds")
norm_cts_h3k4me3_median_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3_median_gene.Rds")
norm_cts_rnapolii_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii_gene.Rds")
norm_cts_rnapolii_median_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii_median_gene.Rds")
log2fc_mat_h3k4me3_genotype_gh_gene <- readRDS("../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_gh_gene.Rds")
log2fc_mat_rnapolii_genotype_gh_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_gh_gene.Rds")
log2fc_mat_h3k4me3_genotype_sh_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_sh_gene.Rds")
log2fc_mat_rnapolii_genotype_sh_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_sh_gene.Rds")
```

```{r}
# Peaks that are differential in at least one comparison
diff_ranges <- readRDS( "../data_output/2024-01_diffbind_cutnrun/diff_ranges.Rds")
```

```{r}
# Read fru and dsx target genes 
fru_ma_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 1-fruma_targets.csv")[,-2]
fru_mc_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 2-frumc_targets.csv")[,-2]
fru_mb_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 3-frumb_targets.csv")[,-2]


fru_ma_genes <- fru_ma_genes$FruMA
fru_mc_genes <- fru_mc_genes$FruMC
fru_mb_genes <- fru_mb_genes$FruMB

fru_target_genes <- unique(c(fru_ma_genes, fru_mc_genes, fru_mb_genes))

dsx_target_genes <- readxl::read_excel("../data_input/gene_annotations/dsx_target_genes.xlsx",sheet = 3)
dsx_target_genes <- dsx_target_genes$`Male_Fatbody_DamIDseq_Gene_Level_Occupancy> 0.9`

```

```{r}
# Go terms

res_gr_h3k4me3_genes_go <- readRDS(file = "../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_genes_go.Rds")
res_gr_h3k4me3_genes_go@compareClusterResult$Cluster <- factor(res_gr_h3k4me3_genes_go@compareClusterResult$Cluster, levels = c("Or47bmut_GH", "Or47bmut_SH", "Or67dmut_GH", "Or67dmut_SH", "frumut_GH", "frumut_SH","dsxmut_GH", "dsxmut_SH" ))



res_gr_rnapolii_genes_go <- readRDS(file = "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes_go.Rds")
res_gr_rnapolii_genes_go@compareClusterResult$Cluster <- factor(res_gr_rnapolii_genes_go@compareClusterResult$Cluster, levels = c("Or47bmut_GH", "Or47bmut_SH", "Or67dmut_GH", "Or67dmut_SH", "frumut_GH", "frumut_SH","dsxmut_GH", "dsxmut_SH" ))



res_gr_rnapolii_genes_go_simplify <- readRDS(file = "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes_go_simplify.Rds")
res_gr_rnapolii_genes_go_simplify@compareClusterResult$Cluster <- factor(res_gr_rnapolii_genes_go_simplify@compareClusterResult$Cluster, levels = c("Or47bmut_GH", "Or47bmut_SH", "Or67dmut_GH", "Or67dmut_SH", "frumut_GH", "frumut_SH","dsxmut_GH", "dsxmut_SH" ))





```


```{r}
# reactome terms
res_gr_rnapolii_genes_reactome <- readRDS(file = "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes_reactome.Rds")
#res_gr_h3k4me3_genes_reactome <- readRDS(file = "../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_genes_reactome.Rds")

res_gr_rnapolii_genes_reactome@compareClusterResult$Cluster <- factor(res_gr_rnapolii_genes_reactome@compareClusterResult$Cluster, levels = c("Or47bmut_GH", "Or47bmut_SH", "Or67dmut_GH", "Or67dmut_SH", "frumut_GH", "frumut_SH","dsxmut_GH", "dsxmut_SH" ))

```


```{r}
# KEGG terms
res_gr_rnapolii_genes_KEGG <- readRDS(file = "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes_KEGG.Rds")
#res_gr_h3k4me3_genes_KEGG <- readRDS(file = "../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_genes_KEGG.Rds")

res_gr_rnapolii_genes_KEGG@compareClusterResult$Cluster <- factor(res_gr_rnapolii_genes_KEGG@compareClusterResult$Cluster, levels = c("Or47bmut_GH", "Or47bmut_SH", "Or67dmut_GH", "Or67dmut_SH", "frumut_GH", "frumut_SH","dsxmut_GH", "dsxmut_SH" ))


```

# QC of the data: PCA plots between samples

```{r}
pca_data <- plotPCA(vsd_h3k4me3 , intgroup = "condition", returnData = TRUE) 

ggplot(pca_data, aes(PC1, PC2, color = condition)) +
  geom_point(size = 2) +  # Adjust the size of the points
  theme_classic() +
  theme(aspect.ratio = 1)+
  ggtitle("PCA H3K4me3")
```

```{r}
pca_data <- plotPCA(vsd_rnapolii , intgroup = "condition", returnData = TRUE) 

ggplot(pca_data, aes(PC1, PC2, color = condition)) +
  geom_point(size = 2) +  # Adjust the size of the points
  theme_classic() +
  theme(aspect.ratio = 1)+
  ggtitle("PCA RNAPolII")

```


# Pairwise tests

## Volcano plots for different comparisons

## Housing within the same genotype

```{r}
res_long_h3k4me3_df_housing_all <- res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"housing")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_"))

res_long_h3k4me3_df_housing_all$comparison <- factor(res_long_h3k4me3_df_housing_all$comparison, levels = c("CS","Or47bmut", "Or67dmut","frumut", "dsxmut"))

  ggplot(res_long_h3k4me3_df_housing_all, aes(log2FoldChange, -log10(pvalue),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey")) +
  facet_grid(cols = vars(comparison)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3 pairwise")
```

```{r}
res_long_rnapolii_df_housing_all <- res_long_rnapolii_df %>%
  filter(str_detect(comparison,"housing")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_"))

res_long_rnapolii_df_housing_all$comparison <- factor(res_long_rnapolii_df_housing_all$comparison, levels = c("CS","Or47bmut", "Or67dmut","frumut", "dsxmut"))

  ggplot(res_long_rnapolii_df_housing_all, aes(log2FoldChange, -log10(pvalue),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "grey")) +
  facet_grid(cols = vars(comparison)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("RNAPolII pairwise")
```

## GH: all to CS

Pairwise mutant GH / CantonS GH 

```{r}
res_long_h3k4me3_df_genotype_GH <- res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "GH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_"))

res_long_h3k4me3_df_genotype_GH$comparison <- factor(res_long_h3k4me3_df_genotype_GH$comparison, levels = c("Or47bmut_GH", "Or67dmut_GH","frumut_GH", "dsxmut_GH"))

  res_long_h3k4me3_df_genotype_GH %>%
  mutate(DEP_direction = case_when(
    padj < 0.01 & log2FoldChange > 0.01 ~ "Up",     # red
    padj < 0.01 & log2FoldChange < -0.01 ~ "Down",  # blue
    TRUE ~ "NS"                                    # gray
  )) %>%
  ggplot(aes(log2FoldChange, -log10(padj), color = DEP_direction)) +
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,10)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "right") +
  ggtitle("H3K4me3 Mutant vs CS GH") + 
  scale_color_manual(values = c("Up" = "#ff7777", "Down" = "skyblue", "NS" = "gray"))


```



## SH: all to a CS

```{r}

res_long_h3k4me3_df_genotype_SH <- res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "SH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_"))

res_long_h3k4me3_df_genotype_SH$comparison <- factor(res_long_h3k4me3_df_genotype_SH$comparison, levels = c("Or47bmut_SH", "Or67dmut_SH","frumut_SH", "dsxmut_SH"))


res_long_h3k4me3_df_genotype_SH %>%
  mutate(DEP_direction = case_when(
    padj < 0.01 & log2FoldChange > 0.01 ~ "Up",     # red
    padj < 0.01 & log2FoldChange < -0.01 ~ "Down",  # blue
    TRUE ~ "NS"                                    # gray
  )) %>%
  ggplot(aes(log2FoldChange, -log10(padj), color = DEP_direction)) +
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,10)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "right") +
  ggtitle("H3K4me3 Mutant vs CS SH") + 
  scale_color_manual(values = c("Up" = "#ff7777", "Down" = "skyblue", "NS" = "gray"))


  
  

```
#RNAPolII

```{r}
res_long_rnapolii_df_genotype_GH <- res_long_rnapolii_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "GH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_"))

res_long_rnapolii_df_genotype_GH$comparison <- factor(res_long_rnapolii_df_genotype_GH$comparison, levels = c("Or47bmut_GH", "Or67dmut_GH","frumut_GH", "dsxmut_GH"))

  
res_long_rnapolii_df_genotype_GH %>%
  mutate(DEP_direction = case_when(
    padj < 0.01 & log2FoldChange > 0.01 ~ "Up",     # red
    padj < 0.01 & log2FoldChange < -0.01 ~ "Down",  # blue
    TRUE ~ "NS"                                    # gray
  )) %>%
  ggplot(aes(log2FoldChange, -log10(padj), color = DEP_direction)) +
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,10)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "right") +
  ggtitle("RNAPolII Mutant vs CS GH") + 
  scale_color_manual(values = c("Up" = "#ff7777", "Down" = "skyblue", "NS" = "gray"))


```




```{r}

res_long_rnapolii_df_genotype_SH <- res_long_rnapolii_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "SH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_"))

res_long_rnapolii_df_genotype_SH$comparison <- factor(res_long_rnapolii_df_genotype_SH$comparison, levels = c("Or47bmut_SH", "Or67dmut_SH","frumut_SH", "dsxmut_SH"))

  res_long_rnapolii_df_genotype_SH %>%
  mutate(DEP_direction = case_when(
    padj < 0.01 & log2FoldChange > 0.01 ~ "Up",     # red
    padj < 0.01 & log2FoldChange < -0.01 ~ "Down",  # blue
    TRUE ~ "NS"                                    # gray
  )) %>%
  ggplot(aes(log2FoldChange, -log10(padj), color = DEP_direction)) +
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,10)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "right") +
  ggtitle("RNAPolII Mutant vs CS SH") + 
  scale_color_manual(values = c("Up" = "#ff7777", "Down" = "skyblue", "NS" = "gray"))


```



# Table of genes matched to differential CUT&RUN peaks:all peaks

The table contains:
-Deseq results of all peaks that were linked to the nearest gene (distance from peak to nearest gene is shown in distance column)

```{r}
res_gr_h3k4me3_genes %>%
  unique()%>%
  as.data.frame() %>%
  drop_na(SYMBOL) %>%
  dplyr::select(SYMBOL, distanceToTSS, (starts_with("log2Fold")|starts_with("padj"))) %>% 
arrange(SYMBOL) %>%
  DT::datatable(extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))
```


# Stats of connection of peaks to genes  

## H3K4me3 Peak annotation 

```{r}
library(ChIPseeker) # Annotation functions for peaks
library(TxDb.Dmelanogaster.UCSC.dm6.ensGene) # Fly transcripts, promoters annotation
library(GenomicRanges) # Reperesent ranges in R 
library(plyranges)
library(org.Dm.eg.db)
library(GenomicFeatures)
library(clusterProfiler)
library(SummarizedExperiment)


ChIPseeker::plotAnnoBar(res_gr_h3k4me3_all_uscs_anno)
ChIPseeker::plotDistToTSS(res_gr_h3k4me3_all_uscs_anno)
ChIPseeker::upsetplot(res_gr_h3k4me3_all_uscs_anno)


```



## RNAPolII Peak annotation 

```{r}

ChIPseeker::plotAnnoBar(res_gr_rnapolii_all_uscs_anno)
ChIPseeker::plotDistToTSS(res_gr_rnapolii_all_uscs_anno)
ChIPseeker::upsetplot(res_gr_rnapolii_all_uscs_anno)

```

# Heatmaps:

### GH vs wt

#### Z score median

##### for all DEGs

H3K4me3

```{r fig.height=10}
plot_heatmap(norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),diff_ranges$h3k4me3_gh_genes),str_detect(colnames(norm_cts_h3k4me3_median_gene),"GH")], "H3K4me3 mutant/CS GH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 

#Or only
DEPs_Or_GH <- union(comp_list$genotype_gh_all_h3k4me3_geneid$H3K4me3_Or47bmut,comp_list$genotype_gh_all_h3k4me3_geneid$H3K4me3_Or67dmut) 
DEPs_Or_GH_matrix <- norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),DEPs_Or_GH),str_detect(colnames(norm_cts_h3k4me3_median_gene),"CS_GH|Or47bmut_GH|Or67dmut_GH")]
DEPs_Or_GH_matrix <- DEPs_Or_GH_matrix[rowSums(DEPs_Or_GH_matrix != 0) > 0, ]

plot_heatmap(DEPs_Or_GH_matrix, "H3K4me3 Or mutant/CS GH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 

#TF only
DEPs_TF_GH <- union(comp_list$genotype_gh_all_h3k4me3_geneid$H3K4me3_frumut,comp_list$genotype_gh_all_h3k4me3_geneid$H3K4me3_dsxmut) 
DEPs_TF_GH_matrix <- norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),DEPs_TF_GH),str_detect(colnames(norm_cts_h3k4me3_median_gene),"CS_GH|frumut_GH|dsxmut_GH")]
DEPs_TF_GH_matrix <- DEPs_TF_GH_matrix[rowSums(DEPs_TF_GH_matrix != 0) > 0, ]

plot_heatmap(DEPs_TF_GH_matrix, "H3K4me3 TF mutant/CS GH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 


```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_gh_genes))
```

RNAPolII 

```{r fig.height=10}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_gh_genes),str_detect(colnames(norm_cts_rnapolii_median_gene),"GH")],"RNAPolII mutant/CS GH different peaks linked to genes" ,show_row_names = F, cluster_rows = TRUE) 


#Or only
DEPs_Or_GH <- union(comp_list$genotype_gh_all_rnapolii_geneid$RNAPolII_Or47bmut,comp_list$genotype_gh_all_rnapolii_geneid$RNAPolII_Or67dmut) 
DEPs_Or_GH_matrix <- norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),DEPs_Or_GH),str_detect(colnames(norm_cts_rnapolii_median_gene),"CS_GH|Or47bmut_GH|Or67dmut_GH")]
DEPs_Or_GH_matrix <- DEPs_Or_GH_matrix[rowSums(DEPs_Or_GH_matrix != 0) > 0, ]

plot_heatmap(DEPs_Or_GH_matrix, "RNAPolII Or mutant/CS GH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 

#TF only
DEPs_TF_GH <- union(comp_list$genotype_gh_all_rnapolii_geneid$RNAPolII_frumut,comp_list$genotype_gh_all_rnapolii_geneid$RNAPolII_dsxmut) 
DEPs_TF_GH_matrix <- norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),DEPs_TF_GH),str_detect(colnames(norm_cts_rnapolii_median_gene),"CS_GH|frumut_GH|dsxmut_GH")]
DEPs_TF_GH_matrix <- DEPs_TF_GH_matrix[rowSums(DEPs_TF_GH_matrix != 0) > 0, ]

plot_heatmap(DEPs_TF_GH_matrix, "RNAPolII TF mutant/CS GH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 


```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_gh_genes))
```

#### log2FC

##### for all DEGs

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_gh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```
Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_gh_gene)))
```

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_gh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_gh_gene)))
```




### SH vs wt

H3K4me3

#### Z score median

##### for all DEGs

H3K4me3

```{r fig.height=10}
plot_heatmap(norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),diff_ranges$h3k4me3_sh_genes),str_detect(colnames(norm_cts_h3k4me3_median_gene),"SH")], "H3K4me3 mutant/CS SH different peaks linked to genes", show_row_names = F, cluster_rows = TRUE) 

#Or only
DEPs_Or_SH <- union(comp_list$genotype_sh_all_h3k4me3_geneid$H3K4me3_Or47bmut,comp_list$genotype_sh_all_h3k4me3_geneid$H3K4me3_Or67dmut) 
DEPs_Or_SH_matrix <- norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),DEPs_Or_SH),str_detect(colnames(norm_cts_h3k4me3_median_gene),"CS_SH|Or47bmut_SH|Or67dmut_SH")]
DEPs_Or_SH_matrix <- DEPs_Or_SH_matrix[rowSums(DEPs_Or_SH_matrix != 0) > 0, ]

plot_heatmap(DEPs_Or_SH_matrix, "H3K4me3 Or mutant/CS SH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 

#TF only
DEPs_TF_SH <- union(comp_list$genotype_sh_all_h3k4me3_geneid$H3K4me3_frumut,comp_list$genotype_sh_all_h3k4me3_geneid$H3K4me3_dsxmut) 
DEPs_TF_SH_matrix <- norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),DEPs_TF_SH),str_detect(colnames(norm_cts_h3k4me3_median_gene),"CS_SH|frumut_SH|dsxmut_SH")]
DEPs_TF_SH_matrix <- DEPs_TF_SH_matrix[rowSums(DEPs_TF_SH_matrix != 0) > 0, ]

plot_heatmap(DEPs_TF_SH_matrix, "H3K4me3 TF mutant/CS SH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 




```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_sh_genes))
```

RNAPolII 

```{r fig.height=10}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_sh_genes),str_detect(colnames(norm_cts_rnapolii_median_gene),"SH")], "RNAPolII mutant/CS SH different peaks linked to genes", show_row_names = F, cluster_rows = TRUE) 

#Or only
DEPs_Or_SH <- union(comp_list$genotype_sh_all_rnapolii_geneid$RNAPolII_Or47bmut,comp_list$genotype_sh_all_rnapolii_geneid$RNAPolII_Or67dmut) 
DEPs_Or_SH_matrix <- norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),DEPs_Or_SH),str_detect(colnames(norm_cts_rnapolii_median_gene),"CS_SH|Or47bmut_SH|Or67dmut_SH")]
DEPs_Or_SH_matrix <- DEPs_Or_SH_matrix[rowSums(DEPs_Or_SH_matrix != 0) > 0, ]

plot_heatmap(DEPs_Or_SH_matrix, "RNAPolII Or mutant/CS SH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 

#TF only
DEPs_TF_SH <- union(comp_list$genotype_sh_all_rnapolii_geneid$RNAPolII_frumut,comp_list$genotype_sh_all_rnapolii_geneid$RNAPolII_dsxmut) 
DEPs_TF_SH_matrix <- norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),DEPs_TF_SH),str_detect(colnames(norm_cts_rnapolii_median_gene),"CS_SH|frumut_SH|dsxmut_SH")]
DEPs_TF_SH_matrix <- DEPs_TF_SH_matrix[rowSums(DEPs_TF_SH_matrix != 0) > 0, ]

plot_heatmap(DEPs_TF_SH_matrix, "RNAPolII TF mutant/CS SH different peaks linked to genes",show_row_names = F, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_sh_genes))
```


#### log2FC

##### for all DEGs

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_sh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```
Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_sh_gene)))
```

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_sh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_sh_gene)))
```

# Venn diagram with (at least) three groups of DEGs:

## Plot venn diagrams

## GH: all to CS

### All

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Up

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

## SH: all to a CS

### All

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Up

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH DOWN H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH DOWN RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

# GO terms for different comparisons, distance-based gene to peak connections

```{r}
dotplot(res_gr_h3k4me3_genes_go,showCategory = Inf, by='GeneRatio') +
  ggtitle("GO terms H3K4me3")
```


Get GO Table with genes:

```{r}
DT::datatable(res_gr_h3k4me3_genes_go@compareClusterResult,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))
```


```{r}

dotplot(res_gr_rnapolii_genes_go,showCategory = Inf, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 35))+  ggtitle("GO terms RNAPolII") +  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 


cnetplot(res_gr_rnapolii_genes_go,showCategory = Inf, by='GeneRatio', node_label = "category", layout = "kk", label_cex = 0.8, legend_n = 2) +
  ggtitle("GO terms RNAPolII")

#Get GO Table with genes:
DT::datatable(res_gr_rnapolii_genes_go@compareClusterResult,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))


#Or only 
Or_only <- c("CS", "Or47b", "Or67d")
Or_only_go_genotype <- res_gr_rnapolii_genes_go %>%
  filter(grepl(paste(Or_only, collapse = "|"), Cluster))

dotplot(Or_only_go_genotype,showCategory = Inf, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 35))+  ggtitle("GO terms RNAPolII Or") +  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 


#TF only 
TF_only <- c("CS", "fru", "dsx")
TF_only_go_genotype <- res_gr_rnapolii_genes_go %>%
  filter(grepl(paste(TF_only, collapse = "|"), Cluster))

dotplot(TF_only_go_genotype,showCategory = Inf, by='GeneRatio') + scale_y_discrete(labels = function(x) str_wrap(x, width = 35))+  ggtitle("GO terms RNAPolII TF") +  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 



```

#Reactome
#no h3k4me3 reactome 

```{r}
dotplot(res_gr_rnapolii_genes_reactome,showCategory = Inf, by='GeneRatio') +
  ggtitle("reactome terms RNAPolII") +theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11), axis.title.y = element_text(size = 11)) 

cnetplot(res_gr_rnapolii_genes_reactome,showCategory = Inf, by='GeneRatio', layout = "kk", label_cex = 5.5, ledgend_n = 2) + ggtitle("reactome terms RNAPolII")

#Get GO Table with genes:
DT::datatable(res_gr_rnapolii_genes_reactome@compareClusterResult,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))

```



#KEGG
#no h3k4me3 KEGG 
```{r}
dotplot(res_gr_rnapolii_genes_KEGG,showCategory = Inf, by='GeneRatio') +
  ggtitle("KEGG terms RNAPolII")


#Get GO Table with genes:
DT::datatable(res_gr_rnapolii_genes_KEGG@compareClusterResult,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))

```




# Venn diagram 


### All differential genes (without considerign sign of fold change) 

```{r}
# GH 
comp_list$genotype_gh_all_h3k4me3_geneid <- comp_list$genotype_gh_all_h3k4me3_geneid[c("H3K4me3_Or47bmut","H3K4me3_Or67dmut","H3K4me3_frumut","H3K4me3_dsxmut")]


comp_list$genotype_sh_all_h3k4me3_geneid <- comp_list$genotype_sh_all_h3k4me3_geneid[c("H3K4me3_Or47bmut","H3K4me3_Or67dmut","H3K4me3_frumut","H3K4me3_dsxmut")]

comp_list$genotype_gh_all_rnapolii_geneid <- comp_list$genotype_gh_all_rnapolii_geneid[c("RNAPolII_Or47bmut","RNAPolII_Or67dmut","RNAPolII_frumut","RNAPolII_dsxmut")]

comp_list$genotype_sh_all_rnapolii_geneid <- comp_list$genotype_sh_all_rnapolii_geneid[c("RNAPolII_Or47bmut","RNAPolII_Or67dmut","RNAPolII_frumut","RNAPolII_dsxmut")]


ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_h3k4me3_geneid, 
                             label_alpha = 0, label = "count", label_color = "white", label_size = 8 ) +
  scale_fill_viridis_c() + scale_x_continuous(expand = expansion(mult = .1)) +
  ggtitle("H3K4me3 GH mutants vs CS genes")

#  
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_rnapolii_geneid, 
                             label_alpha = 0, label = "count", label_color = "white", label_size = 8 ) +
  scale_fill_viridis_c() + scale_x_continuous(expand = expansion(mult = .1)) +
  ggtitle("RNAPolII GH mutants vs CS genes")

# SH 
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_h3k4me3_geneid, 
                             label_alpha = 0, label = "count", label_color = "white", label_size = 8 ) +
  scale_fill_viridis_c() + scale_x_continuous(expand = expansion(mult = .1)) +
  ggtitle("H3K4me3 SH mutants vs CS genes")

#  
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_rnapolii_geneid, 
                             label_alpha = 0, label = "count", label_color = "white", label_size = 8 ) +
  scale_fill_viridis_c() + scale_x_continuous(expand = expansion(mult = .1)) +
  ggtitle("RNAPolII SH mutants vs CS genes")


```

# export to csv/excel
```{r eval=FALSE, include=FALSE}
#all_peaks_genes_H3K4me3
writexl::write_xlsx(res_gr_h3k4me3_genes, "../data_output/2024-01_diffbind_cutnrun/all_peaks_genes_H3K4me3.xlsx")

#all_peaks_genes_RNAPolII
writexl::write_xlsx(res_gr_rnapolii_genes, "../data_output/2024-01_diffbind_cutnrun/all_peaks_genes_RNAPolII.xlsx")


#DEPs_H3K4me3_GH
max_ln_DEPs_H3K4me3_GH <- max(lengths(comp_list$genotype_gh_all_h3k4me3_rangeid))
df_fixed_DEPs_H3K4me3_GH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_gh_all_h3k4me3_rangeid, `length<-`, max_ln_DEPs_H3K4me3_GH)))
writexl::write_xlsx(df_fixed_DEPs_H3K4me3_GH, "../data_output/2024-01_diffbind_cutnrun/DEPs_H3K4me3_GH.xlsx")

#DEPs_H3K4me3_SH
max_ln_DEPs_H3K4me3_SH <- max(lengths(comp_list$genotype_sh_all_h3k4me3_rangeid))
df_fixed_DEPs_H3K4me3_SH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_sh_all_h3k4me3_rangeid, `length<-`, max_ln_DEPs_H3K4me3_SH)))
writexl::write_xlsx(df_fixed_DEPs_H3K4me3_SH, "../data_output/2024-01_diffbind_cutnrun/DEPs_H3K4me3_SH.xlsx")


#DEPs_RNAPolII_GH
max_ln_DEPs_RNAPolII_GH <- max(lengths(comp_list$genotype_gh_all_rnapolii_rangeid))
df_fixed_DEPs_RNAPolII_GH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_gh_all_rnapolii_rangeid, `length<-`, max_ln_DEPs_RNAPolII_GH)))
writexl::write_xlsx(df_fixed_DEPs_RNAPolII_GH, "../data_output/2024-01_diffbind_cutnrun/DEPs_RNAPolII_GH.xlsx")

#DEPs_RNAPolII_SH
max_ln_DEPs_RNAPolII_SH <- max(lengths(comp_list$genotype_sh_all_rnapolii_rangeid))
df_fixed_DEPs_RNAPolII_SH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_sh_all_rnapolii_rangeid, `length<-`, max_ln_DEPs_RNAPolII_SH)))
writexl::write_xlsx(df_fixed_DEPs_RNAPolII_SH, "../data_output/2024-01_diffbind_cutnrun/DEPs_RNAPolII_SH.xlsx")


#genes_H3K4me3_GH
max_ln_genes_H3K4me3_GH <- max(lengths(comp_list$genotype_gh_all_h3k4me3_geneid))
df_fixed_genes_H3K4me3_GH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_gh_all_h3k4me3_geneid, `length<-`, max_ln_genes_H3K4me3_GH)))
writexl::write_xlsx(df_fixed_genes_H3K4me3_GH, "../data_output/2024-01_diffbind_cutnrun/genes_H3K4me3_GH.xlsx")

#genes_H3K4me3_SH
max_ln_genes_H3K4me3_SH <- max(lengths(comp_list$genotype_sh_all_h3k4me3_geneid))
df_fixed_genes_H3K4me3_SH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_sh_all_h3k4me3_geneid, `length<-`, max_ln_genes_H3K4me3_SH)))
writexl::write_xlsx(df_fixed_genes_H3K4me3_SH, "../data_output/2024-01_diffbind_cutnrun/genes_H3K4me3_SH.xlsx")


#genes_RNAPolII_GH
max_ln_genes_RNAPolII_GH <- max(lengths(comp_list$genotype_gh_all_rnapolii_geneid))
df_fixed_genes_RNAPolII_GH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_gh_all_rnapolii_geneid, `length<-`, max_ln_genes_RNAPolII_GH)))
writexl::write_xlsx(df_fixed_genes_RNAPolII_GH, "../data_output/2024-01_diffbind_cutnrun/genes_RNAPolII_GH.xlsx")

#genes_RNAPolII_SH
max_ln_genes_RNAPolII_SH <- max(lengths(comp_list$genotype_sh_all_rnapolii_geneid))
df_fixed_genes_RNAPolII_SH <- as.data.frame(do.call(cbind, lapply(comp_list$genotype_sh_all_rnapolii_geneid, `length<-`, max_ln_genes_RNAPolII_SH)))
writexl::write_xlsx(df_fixed_genes_RNAPolII_SH, "../data_output/2024-01_diffbind_cutnrun/genes_RNAPolII_SH.xlsx")


#H3K4me3_GO
df_H3K4me3_GO <- as.data.frame(res_gr_h3k4me3_genes_go@compareClusterResult)
writexl::write_xlsx(df_H3K4me3_GO, "../data_output/2024-01_diffbind_cutnrun/H3K4me3_GO.xlsx")


#RNAPolII_GO
df_RNAPolII_GO <- as.data.frame(res_gr_rnapolii_genes_go@compareClusterResult)
writexl::write_xlsx(df_RNAPolII_GO, "../data_output/2024-01_diffbind_cutnrun/RNAPolII_GO.xlsx")

#RNAPolII_KEGG
df_RNAPolII_KEGG <- as.data.frame(res_gr_rnapolii_genes_KEGG@compareClusterResult)
writexl::write_xlsx(df_RNAPolII_KEGG, "../data_output/2024-01_diffbind_cutnrun/RNAPolII_KEGG.xlsx")

#RNAPolII_reactome
df_RNAPolII_reactome <- as.data.frame(res_gr_rnapolii_genes_reactome@compareClusterResult)
writexl::write_xlsx(df_RNAPolII_reactome, "../data_output/2024-01_diffbind_cutnrun/RNAPolII_reactome.xlsx")



```






