---
title: "Figure 1 RNA-seq changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r}
# Libraries
library(ComplexHeatmap) # Heatmaps
library(DESeq2) 
library(ggVennDiagram) 
library(clusterProfiler) # Go terms
library(org.Dm.eg.db) # GO annotation
library(tidyverse)
library(circlize) # Colors

options(scipen = 999)
```

```{r}
# Functions
# plot z score matrix
plot_heatmap <- function(mat, ...) {
  ComplexHeatmap::Heatmap(mat = t(scale(t(mat),center = TRUE,scale = TRUE)), # z score
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), # size of legend
          raster_device = "agg_png", # Format to export the raster 
          ... )
}
# log2fc matrix
plot_heatmap_log2fc <- function(mat, ...) {
  ComplexHeatmap::Heatmap(mat = mat,
          heatmap_legend_param = list(title = "log2FC",
                                      legend_height = unit(2, "in")) , 
           raster_device = "agg_png", ... )
}
# Single gene plot
plot_norm_counts <- function(gene, dds) {
  DESeq2::plotCounts(gene, 
                     dds = dds,
                     transform = FALSE, # Don't plot y axis as log scale
                     returnData = TRUE, # Returns data frame instead of plot
                     intgroup = c("condition","genotype","housing","dissection")) %>% # Keep Sample info columns from dds and add to return data
    ggplot(aes(housing, count, color = condition)) +
    geom_jitter(width = 0.2, alpha = 0.7) + # Points 
    stat_summary() + # Mean 
    facet_grid(cols = vars(genotype)) +
    theme_light() +
    theme(aspect.ratio = 1, legend.position = "none") +
    ylab("Normalized Counts") +
    xlab(NULL) +
    ggtitle(gene) 
  
}

# Plot behavior data vs counts daa 
plot_regression_gene <- function(gene_name, dds) {
  
  counts_mat <- DESeq2::plotCounts(gene_name,dds = dds, transform = FALSE,
                                   intgroup = "CI", # Return Courtship index column also
                                   returnData = TRUE) # Get dataframe for gene counts 
  col_data <- as.data.frame(colData(dds)) # Get all sample information from dds transform to regular data frame
  col_data[,gene_name] <- counts_mat$count # Adding gene counts info 
  
  col_data_mean <- col_data %>% # Mean Courtship Index and counts per group
    group_by(genotype, housing) %>%
    summarise(mean_count = mean(.data[[gene_name]]), # Mean counts RNAseq
              mean_behavior = mean(CI)) %>% # Mean CI 
    ungroup()
  
  # Plot 
  col_data_mean %>%
    ggplot(aes(mean_count, mean_behavior)) + 
    geom_point(size = 3, aes(color = paste( genotype , housing))) +
    geom_smooth(color = "gray", method = "lm", se = FALSE) + # Regression line 
    ggtitle(gene_name) +
    xlab("Normalized Counts") +
    ylab("Courtship Index") +
    theme_classic() +
    theme(aspect.ratio = 1,legend.title = element_blank()) +
    ggpubr::stat_cor(
      aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))
    ) # Add stats to plot
}

# Get correlation of counts and courtship index for a given gene 
get_ci_counts_cor <- function(gene_name, dds) {
  col_data <- as.data.frame(colData(dds))
  counts_mat <- DESeq2::plotCounts(gene_name,dds = dds, transform = FALSE, intgroup = "CI", returnData = TRUE)
  
  col_data[,gene_name] <- counts_mat$count
  
  # Get correlation (pearson r)
  cor_res <- (col_data %>%
                group_by(genotype, housing) %>%
                summarise(mean_count = mean(.data[[gene_name]]),
                          mean_behavior = mean(CI)) %>%
                ungroup() %>%
                dplyr::select(starts_with("mean")) %>%
                cor())[1,2] # cor is the function for pearson r
  
  return(cor_res)
}

# Function to make table exportable in the html file 
print_go_table <- function(go_table){ 
  DT::datatable(go_table,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))} # Export as csv
```

```{r}
# Color scheme
color_scheme <- list()
color_scheme$cs <- "#839FD0"
color_scheme$dsx <- "#A08BCE"
color_scheme$fru <- "#DD99E6"
color_scheme$Or47b <- "#C1DD90"
color_scheme$Or67d <- "#4888AA"
```

```{r}
# Read data
# deseq obj
deseq_obj_fitted <- readRDS("../data_output/2024-1_diffexpr_output/deseq_obj_fitted_annotated.Rds")

```

```{r}
# Results joined files
res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```

```{r}
# VST for PCA
vsd_combat <- readRDS("../data_output/2024-1_diffexpr_output/vsd_combat.Rds")
```

```{r}
# Re-shaped data
# res_long_df
res_long_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/res_long_df.Rds")

# Lists of differentially expressed genes by comparison 
comp_list <- readRDS(file = "../data_output/2024-1_diffexpr_output/comp_list.Rds")

# Counts matrix for heatmaps
norm_cts <- readRDS(file = "../data_output/2024-1_diffexpr_output/norm_cts.Rds")
norm_cts_median <- readRDS(file = "../data_output/2024-1_diffexpr_output/norm_cts_median.Rds")
log2fc_mat_housing <- readRDS(file = "../data_output/2024-1_diffexpr_output/log2fc_mat_housing.Rds")
log2fc_mat_genotype_gh <- readRDS(file = "../data_output/2024-1_diffexpr_output/log2fc_mat_genotype_gh.Rds")
log2fc_mat_genotype_sh <- readRDS(file = "../data_output/2024-1_diffexpr_output/log2fc_mat_genotype_sh.Rds")
```


```{r}
# Pairwise comparison data for LRT significant genes

pairwise_log2fc_interaction_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/pairwise_log2fc_interaction_df.Rds")
pairwise_log2fc_housing_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/pairwise_log2fc_housing_df.Rds")
pairwise_log2fc_genotype_df <- readRDS(file = "../data_output/2024-1_diffexpr_output/pairwise_log2fc_genotype_df.Rds")

```


```{r}
#Enriched go terms

go_housing <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_housing.Rds")
go_genotype <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_genotype.Rds")
go_lrt <- readRDS(file = "../data_output/2024-1_diffexpr_output/go_lrt.Rds")

```

```{r}
#Enriched go terms

reactome_housing <- readRDS(file = "../data_output/2024-1_diffexpr_output/reactome_housing.Rds")
reactome_genotype <- readRDS(file = "../data_output/2024-1_diffexpr_output/reactome_genotype.Rds")
reactome_lrt <- readRDS(file = "../data_output/2024-1_diffexpr_output/reactome_lrt.Rds")

```

```{r}
# Lists of gene names for differentially expressed genes
de <- readRDS(file = "../data_output/2024-1_diffexpr_output/de.Rds")
```


```{r}
# Data processing

### Read target genes

#### Fru

fru_ma_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 1-fruma_targets.csv")[,-2]
fru_mc_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 2-frumc_targets.csv")[,-2]
fru_mb_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 3-frumb_targets.csv")[,-2]


fru_ma_genes <- fru_ma_genes$FruMA
fru_mc_genes <- fru_mc_genes$FruMC
fru_mb_genes <- fru_mb_genes$FruMB

fru_target_genes <- unique(c(fru_ma_genes, fru_mc_genes, fru_mb_genes)) # Combine three different isoforms
```


```{r}
# Filtering differential genes to keep overlap with fru targets 
de$cs_genes_id_fru <- de$cs_genes_id[de$cs_genes_id %in% fru_target_genes]
de$genotype_gh_genes_id_fru <- de$genotype_gh_genes_id[de$genotype_gh_genes_id %in% fru_target_genes]
de$genotype_sh_genes_id_fru <- de$genotype_sh_genes_id[de$genotype_sh_genes_id %in% fru_target_genes]
```

```{r}
#### dsx
dsx_target_genes <- readxl::read_excel("../data_input/gene_annotations/dsx_target_genes.xlsx",sheet = 3)
dsx_target_genes <- dsx_target_genes$`Male_Fatbody_DamIDseq_Gene_Level_Occupancy> 0.9`
```

```{r}
# Filtering differential genes to keep overlap with dsx targets 
de$cs_genes_id_dsx <- de$cs_genes_id[de$cs_genes_id %in% dsx_target_genes]
de$genotype_gh_genes_id_dsx <- de$genotype_gh_genes_id[de$genotype_gh_genes_id %in% dsx_target_genes]
de$genotype_sh_genes_id_dsx <- de$genotype_sh_genes_id[de$genotype_sh_genes_id %in% dsx_target_genes]

```

```{r}
#### go
# Map of flybase id to gene name 
symbol_ensembl_map_df <- clusterProfiler::bitr(geneID = res_df$gene_name, fromType = "SYMBOL",toType ="ENSEMBL",OrgDb = org.Dm.eg.db )
symbol_ensembl_map <- symbol_ensembl_map_df$SYMBOL 
names(symbol_ensembl_map) <-  symbol_ensembl_map_df$ENSEMBL

```


```{r}
#autophagy
autophagy_genes <- readLines("../data_input/gene_annotations/2024-02_autophagy_stress_response_go_terms/autophagy_go_terms.txt")

autophagy_genes <- symbol_ensembl_map[autophagy_genes]
autophagy_genes <- na.omit(autophagy_genes)
autophagy_genes <- autophagy_genes[autophagy_genes %in% res_df$gene_name]

```

```{r}
# stress response
oxidative_stress_esponse_genes <- readLines("../data_input/gene_annotations/2024-02_autophagy_stress_response_go_terms/response_to_oxidative_stress_go_terms.txt")
oxidative_stress_esponse_genes <- symbol_ensembl_map[oxidative_stress_esponse_genes]

oxidative_stress_esponse_genes <- na.omit(oxidative_stress_esponse_genes)

oxidative_stress_esponse_genes <- oxidative_stress_esponse_genes[oxidative_stress_esponse_genes %in% res_df$gene_name]

```


```{r}
# ribosomal proteins

ribosomal_genes <- readLines("../data_input/gene_annotations/2024-02_autophagy_stress_response_go_terms/ribosomal_subunit_go_terms.txt") # files of flybase id of genes within a GO term annotation  
ribosomal_genes <- symbol_ensembl_map[ribosomal_genes]

ribosomal_genes <- na.omit(ribosomal_genes)

ribosomal_genes <- ribosomal_genes[ribosomal_genes %in% res_df$gene_name]

```


# QC of the data: PCA plots between samples

```{r}
plotPCA(vsd_combat , intgroup = "condition") + ggtitle("PCA RNA-seq samples") +
  theme_classic() +
  theme(aspect.ratio = 1)
```

# Number of differentially expressed genes in pairwise comparisons 

## Differentially expressed genes between housing conditions in each genotype (SH / GH)

```{r}
res_long_df %>% 
  # First do data processing
  dplyr::select(comparison, padj, log2FoldChange) %>% # Keep relevant columns 
  dplyr::filter(!str_detect(comparison,"lrt") & str_detect(comparison,"housing")) %>% # Filtering comparisons of interest
  drop_na(padj) %>% # Filter out genes
  dplyr::filter(padj < 0.05 & abs(log2FoldChange) > 0.1)  %>% # get differential genes
  mutate(log2fc_sign = ifelse(sign(log2FoldChange) > 0,"UP", "DOWN")) %>% # Add log2fc sign variable 
  group_by(comparison, log2fc_sign) %>%
  summarise(n_diff = dplyr::n()) %>% # Count number of genes per group
  ungroup() %>%
  mutate(comparison = paste(comparison, log2fc_sign)) %>% # Split comparison by direction
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff)) %>% # Order by number of genes
  ggplot(aes(n_diff, comparison)) + 
  geom_col(aes(fill = log2fc_sign)) + # barplots 
  scale_fill_manual(values = c("UP"="#ff7777","DOWN" ="#7777ff")) +
  theme_classic() +
  geom_text(aes(label = n_diff),nudge_x = 1, size = 3) + # Add number of genes to bars
  theme(aspect.ratio = 1) +
  ggtitle("Number of differential genes between SH / GH") +
  xlab("Number of genes padj < 0.05 & abs(log2FoldChange) > 0.1")

```

Plot only Wild Tipe:

```{r }
res_long_df %>% 
  # First do data processing
  dplyr::select(comparison, padj, log2FoldChange) %>% # Keep relevant columns 
  dplyr::filter(str_detect(comparison,"CS_housing")) %>% # Filtering comparisons of interest
  drop_na(padj) %>% # Filter out genes
  dplyr::filter(padj < 0.05 & abs(log2FoldChange) > 0.1)  %>% # get differential genes
  mutate(log2fc_sign = ifelse(sign(log2FoldChange) > 0,"UP", "DOWN")) %>% # Add log2fc sign variable 
  group_by(comparison, log2fc_sign) %>%
  summarise(n_diff = dplyr::n()) %>% # Count number of genes per group
  ungroup() %>%
  mutate(comparison = paste(comparison, log2fc_sign)) %>% # Split comparison by direction
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff)) %>% # Order by number of genes
  ggplot(aes( n_diff,comparison)) + 
  geom_col(aes(fill = log2fc_sign)) + # barplots 
  scale_fill_manual(values = c("UP"="#ff7777","DOWN" ="#7777ff")) +
  theme_classic() +
  geom_text(aes(label = n_diff),nudge_x = 1, size = 5) + # Add number of genes to bars
  theme(aspect.ratio = 0.5) +
  ggtitle("Number of differential genes between SH / GH") +
  xlab("Number of genes padj < 0.05 & abs(log2FoldChange) > 0.1")

```



## Differentially expressed genes between genotype in each housing condition (Mutant / CS)

### Group Housed:

```{r}
res_long_df %>% 
  dplyr::select(comparison, padj, log2FoldChange) %>%
  dplyr::filter(!str_detect(comparison,"lrt") & str_detect(comparison,"GH_genotype")) %>%
  drop_na(padj) %>%
  dplyr::filter(padj < 0.05 & abs(log2FoldChange) > 0.1)  %>%
  mutate(log2fc_sign = ifelse(sign(log2FoldChange) > 0,"UP", "DOWN")) %>%
  group_by(comparison, log2fc_sign) %>%
  summarise(n_diff = dplyr::n()) %>%
  ungroup() %>%
  mutate(comparison = paste(comparison, log2fc_sign)) %>%
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff)) %>%
  ggplot(aes(n_diff, comparison)) +
  geom_col(aes(fill = log2fc_sign)) +
  scale_fill_manual(values = c("UP"="#ff7777","DOWN" ="#7777ff")) +
  theme_classic() +
  geom_text(aes(label = n_diff),nudge_x = 20, # Might need to change this depending on the number of genes
            size = 3) + 
  theme(aspect.ratio = 1) +
  ggtitle("Number of differential genes between Mutant GH / CantonS GH") +
  xlab("Number of genes padj < 0.05 & abs(log2FoldChange) > 0.1")

```

### Single Housed:

```{r}
res_long_df %>% 
  select(comparison, padj, log2FoldChange) %>%
  filter(!str_detect(comparison,"lrt") & str_detect(comparison,"SH_genotype")) %>%
  drop_na(padj) %>%
  filter(padj < 0.05 & abs(log2FoldChange) > 0.1)  %>%
  mutate(log2fc_sign = ifelse(sign(log2FoldChange) > 0,"UP", "DOWN")) %>%
  group_by(comparison, log2fc_sign) %>%
  summarise(n_diff = dplyr::n()) %>%
  ungroup() %>%
  mutate(comparison = paste(comparison, log2fc_sign)) %>%
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff)) %>%
  ggplot(aes(n_diff, comparison)) +
  geom_col(aes(fill = log2fc_sign)) +
  scale_fill_manual(values = c("UP"="#ff7777","DOWN" ="#7777ff")) +
  theme_classic() +
  geom_text(aes(label = n_diff),nudge_x = 50, size = 3) +
  theme(aspect.ratio = 1) +
  ggtitle("Number of differential genes between Mutant SH / CantonS SH") +
  xlab("Number of genes padj < 0.05 & abs(log2FoldChange) > 0.1")

```

# Venn diagram with (at least) three groups of DEGs:

## Housing within the same genotype

### All differential genes (without considerign sign of fold change) 

```{r}
# Input for venn diagrams is list of sets of genes 
ggVennDiagram::ggVennDiagram(comp_list$housing_all_symbol, 
                             label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() + # Change this if you want a different color scheme
  ggtitle("Housing within genotype All")
```

### Differential genes Up (fold change > 0.1, e.g. higher in SH, lower in GH)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$housing_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Housing within genotype UP") 
```

### Differential genes Down (fold change < -0.1, e.g. lower in SH, higher in GH)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$housing_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Housing within genotype DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```

## GH: each Mutant GH / CS GH

### All differential genes (without considerign sign of fold change) 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Up (fold change > 0.1, e.g. higher in Mutant, lower in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Down (fold change < -0.1, e.g. lower in Mutant, higher in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```

## SH: each Mutant SH / CS SH

### All differential genes (without considerign sign of fold change) 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Up (fold change > 0.1, e.g. higher in Mutant, lower in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

### Differential genes Down (fold change < -0.1, e.g. lower in Mutant, higher in CantonS)

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() + 
  ggtitle("Mutant vs CantonS SH DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```


# GO and Pathway terms for different comparisons

Note: All GO plots showing only Top 3 most enriched terms per group. See each table for full results. 

## Housing within the same genotype

### All differential genes (without considerign sign of fold change) 

Dotplot 


```{r}
# Input for go term plots are go_* objects
dotplot(go_housing$all_entrezid,
        showCategory = 5, # Number of top go terms to plot, based on p adjust value
by='GeneRatio') + 
  ggtitle("GO terms housing ALL")

```


```{r}
dotplot(reactome_housing$all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms housing ALL")
```
concept network

```{r}
cnetplot(go_housing$all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms housing ALL") 
```

```{r}
cnetplot(reactome_housing$all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms housing ALL")
```


Full table of GO Results:


```{r}
print_go_table(go_housing$all_entrezid@compareClusterResult)
```

Full table of Reactome Results:

```{r}
print_go_table(reactome_housing$all_entrezid@compareClusterResult)
```


### Differential genes Up (fold change > 0.1, e.g. higher in SH, lower in GH)

dotplot

```{r }

dotplot(go_housing$up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms housing UP")

```

```{r }

dotplot(reactome_housing$up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms housing UP")

```

Concept network plot

```{r}
cnetplot(go_housing$up_entrezid,showCategory = 5) +
  ggtitle("GO terms housing UP")
```

```{r}
cnetplot(reactome_housing$up_entrezid,showCategory = 5) +
  ggtitle("Reactome Pathway terms housing UP")
```

Full table of GO Results:

```{r}
print_go_table(go_housing$up_entrezid@compareClusterResult)
```

Full table of Reactome Results:

```{r}
print_go_table(reactome_housing$up_entrezid@compareClusterResult)
```

### Differential genes Down (fold change < -0.1, e.g. higher in GH, lower in SH)

dotplot

```{r}

dotplot(go_housing$down_entrezid,showCategory = 5) +
  ggtitle("GO terms housing Down")

```

```{r}

dotplot(reactome_housing$down_entrezid,showCategory = 5) +
  ggtitle("Reactome Pathway terms housing Down")

```

concept network plot

```{r}
cnetplot(go_housing$down_entrezid,) +
  ggtitle("GO terms housing DOWN")
```

```{r}
cnetplot(reactome_housing$down_entrezid,) +
  ggtitle("Reactome Pathway terms housing DOWN")
```

Full table of GO Results:

```{r}
print_go_table(go_housing$down_entrezid@compareClusterResult)
```

Full table of Reactome Results:

```{r}
print_go_table(reactome_housing$down_entrezid@compareClusterResult)
```



## GH: each Mutant GH / CS GH

### All differential genes (without considerign sign of fold change) 

dotplot

```{r}
dotplot(go_genotype$gh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH ALL")
```

```{r}
dotplot(reactome_genotype$gh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms Mutant vs CantonS GH ALL")
```

Concept network plot

```{r}
cnetplot(go_genotype$gh_all_entrezid,showCategory =3) +
  ggtitle("GO terms Mutant vs CantonS GH ALL")
```

```{r}
cnetplot(reactome_genotype$gh_all_entrezid,showCategory = 5) +
  ggtitle("Reactome Pathway terms Mutant vs CantonS GH ALL")
```

Full table of GO Results:

```{r}
print_go_table(go_genotype$gh_all_entrezid@compareClusterResult)
```

Full table of Reactome Results:

```{r}
print_go_table(reactome_genotype$gh_all_entrezid@compareClusterResult)
```

### Differential genes Up (fold change > 0.1, e.g. higher in Mutant, lower in CantonS)

dotplot

```{r}

dotplot(go_genotype$gh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH UP")

```

```{r}

dotplot(reactome_genotype$gh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms Mutant vs CantonS GH UP")

```

Concept Network Plot

```{r}

cnetplot(go_genotype$gh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH UP")

```

```{r}

cnetplot(reactome_genotype$gh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms Mutant vs CantonS GH UP")

```

Full table of GO Results:

```{r}
print_go_table(go_genotype$gh_up_entrezid@compareClusterResult)
```

Full table of Reactome Results:

```{r}
print_go_table(reactome_genotype$gh_up_entrezid@compareClusterResult)
```

### Differential genes Down (fold change < -0.1, e.g. lower in Mutant, higher in CantonS)

Note: No enriched terms for Reactome Pathway

dotplot

```{r}

dotplot(go_genotype$gh_down_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH Down")

```

Concept Network Plot

```{r}

cnetplot(go_genotype$gh_down_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH Down")

```

Full table of GO Results:

```{r}
print_go_table(go_genotype$gh_down_entrezid@compareClusterResult)
```

## SH: each Mutant SH / CS SH

### All differential genes (without considerign sign of fold change) 

dotplot

```{r}

dotplot(go_genotype$sh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH ALL")

```

```{r}

dotplot(reactome_genotype$sh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH ALL")

```

Concept Network Plot

```{r}

cnetplot(go_genotype$sh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH ALL")

```

```{r}

cnetplot(reactome_genotype$sh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH ALL")

```

Full table of GO Results:

```{r}
print_go_table(go_genotype$sh_all_entrezid@compareClusterResult)
```

Full table of Reactome Results:

```{r}
print_go_table(reactome_genotype$sh_all_entrezid@compareClusterResult)
```

### Differential genes UP (fold change > 0.1, e.g. higher in Mutant, lower in CantonS)

dotplot

```{r}

dotplot(go_genotype$sh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH UP")

```

```{r}

dotplot(reactome_genotype$sh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms Mutant vs CantonS SH UP")

```

Concept Network Plot

```{r}

cnetplot(go_genotype$sh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH UP")

```

```{r}

cnetplot(reactome_genotype$sh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("Reactome Pathway terms Mutant vs CantonS SH UP")

```

Full table of GO Results:

```{r}
print_go_table(go_genotype$sh_up_entrezid@compareClusterResult)
```

Full table of Reactome Results:

```{r}
print_go_table(reactome_genotype$sh_up_entrezid@compareClusterResult)
```

### Differential genes Down (fold change < -0.1, e.g. lower in Mutant, higher in CantonS)

Note: No reactome significant genes

dotplot

```{r}

dotplot(go_genotype$sh_down_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH Down")

```

Concept network plot

```{r}

cnetplot(go_genotype$sh_down_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH Down")

```

Full table of GO Results:

```{r}
print_go_table(go_genotype$sh_down_entrezid@compareClusterResult)
```

# Heatmaps:

### Housing within the same genotype

#### Per-row Z score matrix showing all replicates

Every row represents a different gene. Color is mappet to DESEQ2 normalized counts scaled by the per row (i.e. per gene) standard deviation, and mean-subtracted (i.e. z score).

##### All genes that are differentially expressed in SH CS / GH CS comparison 

Rows clustered 

```{r fig.height=13}
plot_heatmap(mat = norm_cts[de$cs_genes_id,], # Matrix of norm counts, subset by differential genes
             cluster_columns = FALSE,show_row_names = TRUE, cluster_rows = TRUE) # additional parameters for Heatmap function
```

Rows + columns clustered 

```{r fig.height=13}
plot_heatmap(norm_cts[de$cs_genes_id,],
             cluster_columns = TRUE,show_row_names = TRUE, cluster_rows = TRUE)
```

##### fru: differential genes subset by whether they are fru targets

rows clustered 

```{r fig.height=8}
plot_heatmap(norm_cts[de$cs_genes_id_fru,], cluster_columns = FALSE, show_row_names = TRUE, cluster_rows = TRUE)

```

rows and columns clustered 

```{r fig.height=8}
plot_heatmap(norm_cts[de$cs_genes_id_fru,], cluster_columns = TRUE, show_row_names = TRUE, cluster_rows = TRUE)

```

##### dsx: differential genes subset by whether they are dsx targets

rows clustered 

```{r}
plot_heatmap(norm_cts[de$cs_genes_id_dsx,],cluster_columns = FALSE, show_row_names = TRUE, cluster_rows = TRUE)

```

rows and columns clustered 

```{r}
plot_heatmap(norm_cts[de$cs_genes_id_dsx,],cluster_columns = TRUE, show_row_names = TRUE, cluster_rows = TRUE)

```

##### go

#### Z score median

Same data as above, but the replicates were combined in a single column by taking the median of all 3 replicate values.

##### All genes that are differentially expressed in SH CS / GH CS comparison 

rows clustered 

```{r fig.height=13}
plot_heatmap(norm_cts_median[de$cs_genes_id,], cluster_columns = FALSE, show_row_names = TRUE, cluster_rows = TRUE)
```

rows and columns clustered 

```{r fig.height=13}
plot_heatmap(norm_cts_median[de$cs_genes_id,], cluster_columns = TRUE, show_row_names = TRUE, cluster_rows = TRUE)
```

##### fru: differential genes subset by whether they are fru targets

rows clustered

```{r fig.height=8}
plot_heatmap(norm_cts_median[de$cs_genes_id_fru,], show_row_names = TRUE, cluster_columns = FALSE, cluster_rows = TRUE)
```

rows and columns clustered

```{r fig.height=8}
plot_heatmap(norm_cts_median[de$cs_genes_id_fru,], show_row_names = TRUE, cluster_columns = TRUE, cluster_rows = TRUE)
```

##### dsx: differential genes subset by whether they are dsx targets

clustered rows

```{r}
plot_heatmap(norm_cts_median[de$cs_genes_id_dsx,],cluster_columns = FALSE, show_row_names = TRUE, cluster_rows = TRUE)
```

clustered rows and columns

```{r}
plot_heatmap(norm_cts_median[de$cs_genes_id_dsx,],cluster_columns = TRUE, show_row_names = TRUE, cluster_rows = TRUE)
```

##### go

#### log2FoldChange

##### All genes that are differentially expressed in SH CS / GH CS comparison 

cluster rows 

```{r fig.height=13}
plot_heatmap_log2fc(log2fc_mat_housing,
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

cluster rows  and columns

```{r fig.height=13}
plot_heatmap_log2fc(log2fc_mat_housing,
                    cluster_rows = TRUE,
                    cluster_columns = TRUE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

##### fru: differential genes subset by whether they are fru targets

cluster rows

```{r fig.height=8}
plot_heatmap_log2fc(log2fc_mat_housing[rownames(log2fc_mat_housing) %in% de$cs_genes_id_fru,],
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)

```

cluster rows and columns

```{r fig.height=8}
plot_heatmap_log2fc(log2fc_mat_housing[rownames(log2fc_mat_housing) %in% de$cs_genes_id_fru,],
                    cluster_rows = TRUE,
                    cluster_columns = TRUE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)

```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows

```{r}
plot_heatmap_log2fc(log2fc_mat_housing[rownames(log2fc_mat_housing) %in% de$cs_genes_id_dsx,],
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

cluster rows and columns 

```{r}
plot_heatmap_log2fc(log2fc_mat_housing[rownames(log2fc_mat_housing) %in% de$cs_genes_id_dsx,],
                    cluster_rows = TRUE,
                    cluster_columns = TRUE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

##### go

### GH: each Mutant GH / CS GH

#### Z score all reps

##### All genes that are differentially expressed in SH CS / GH CS comparison 

cluster rows

```{r }
plot_heatmap(norm_cts[de$genotype_gh_genes_id,], cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts[de$genotype_gh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE,)
```

##### fru: differential genes subset by whether they are fru targets

cluster rows 

```{r}
plot_heatmap(norm_cts[de$genotype_gh_genes_id_fru,],cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts[de$genotype_gh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows 

```{r}
plot_heatmap(norm_cts[de$genotype_gh_genes_id_dsx,], cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts[de$genotype_gh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### go

#### Z score median

##### All genes that are differentially expressed in SH CS / GH CS comparison 

cluster rows 

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id,], cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### fru: differential genes subset by whether they are fru targets


cluster rows  

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id_fru,],cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns 

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id_dsx,], cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts_median[de$genotype_gh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```


##### go

#### log2FoldChange

##### All genes that are differentially expressed in SH CS / GH CS comparison 

cluster rows 

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh,
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

cluster rows and columns

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### fru: differential genes subset by whether they are fru targets

cluster rows

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[rownames(log2fc_mat_genotype_gh) %in% de$genotype_gh_genes_id_fru,],
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

cluster rows and columns

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[rownames(log2fc_mat_genotype_gh) %in% de$genotype_gh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows and columns

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[rownames(log2fc_mat_genotype_gh) %in% de$genotype_gh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

cluster rows 

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[rownames(log2fc_mat_genotype_gh) %in% de$genotype_gh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### go

### SH: each Mutant SH / CS SH

#### Z score all reps

##### All genes that are differentially expressed  

cluster rows

```{r}
plot_heatmap(norm_cts[de$genotype_sh_genes_id,], cluster_columns = FALSE,show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns 

```{r}
plot_heatmap(norm_cts[de$genotype_sh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### fru: differential genes subset by whether they are fru targets

cluster rows

```{r}
plot_heatmap(norm_cts[de$genotype_sh_genes_id_fru,],cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)

```

cluster rows and columns 

```{r}
plot_heatmap(norm_cts[de$genotype_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows

```{r}
plot_heatmap(norm_cts[de$genotype_sh_genes_id_dsx,], cluster_columns = FALSE,
             show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts[de$genotype_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### go

#### Z score median

##### All genes that are differentially expressed   

cluster rows

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id,],cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### fru: differential genes subset by whether they are fru targets

cluster rows

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id_fru,], cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id_dsx,],cluster_columns = FALSE, show_row_names = FALSE, cluster_rows = TRUE)
```

cluster rows and columns

```{r}
plot_heatmap(norm_cts_median[de$genotype_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### go

#### log2FoldChange

##### All genes that are differentially expressed in   

cluster rows

```{r}
plot_heatmap_log2fc(mat = log2fc_mat_genotype_sh, # Log2fc matrix
                    cluster_rows = TRUE, # Extra parameters for Heatmap
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1), # Cap the log2FC so that outliers don't drive the color scheme
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

cluster rows and columns

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### fru: differential genes subset by whether they are fru targets

cluster rows

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[rownames(log2fc_mat_genotype_sh) %in% de$genotype_sh_genes_id_fru,],
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")), 
                    show_row_names = FALSE)
```

cluster rows and columns

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[rownames(log2fc_mat_genotype_sh) %in% de$genotype_sh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")), 
                    show_row_names = FALSE)
```

##### dsx: differential genes subset by whether they are dsx targets

cluster rows

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[rownames(log2fc_mat_genotype_sh) %in% de$genotype_sh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    cluster_columns = FALSE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")), 
                    show_row_names = FALSE)
```

cluster rows and columns

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[rownames(log2fc_mat_genotype_sh) %in% de$genotype_sh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")), 
                    show_row_names = FALSE)
```


##### go

# Volcano plots for different comparisons

## Housing within the same genotype

```{r}

res_long_df %>%
  dplyr::filter(str_detect(comparison,"housing")) %>%
  dplyr::filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing")) %>% # removing "housing" from genotype names
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 & abs(log2FoldChange) > 0.1 )) + # cutoffs for padj and log2foldchange
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) + # modify for rows if needed 
  ylim(c(0,150)) + # cap padj values
  xlim(c(-5,5)) + # Cap log2foldchange
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("SH / GH within each genotype") + 
  scale_color_manual(values = c("FALSE" = "gray","TRUE" = "blue"))
  

```

Plot WT only

```{r fig.height=3, fig.width=3}

res_long_df %>%
  dplyr::filter(str_detect(comparison,"CS_housing")) %>%
  mutate(comparison = str_remove(comparison,"_housing")) %>% # removing "housing" from genotype names
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 & abs(log2FoldChange) > 0.1 )) + # cutoffs for padj and log2foldchange
  geom_point(size = 0.7, alpha = 1) +
  facet_grid(cols = vars(comparison)) + # modify for rows if needed 
  ylim(c(0,150)) + # cap padj values
  xlim(c(-5,5)) + # Cap log2foldchange
  theme_classic() +
  theme(aspect.ratio = 1, legend.position = "bottom") +
  scale_color_manual(values = c("FALSE" = "gray","TRUE" = "blue"))
  

```
## GH: each Mutant GH / CS GH

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(str_detect(comparison, "GH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_GH_genotype")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 & abs(log2FoldChange) > 0.1 )) +
  geom_point(size = 0.5, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,150)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("Mutant / CantonS within GH") + 
  scale_color_manual(values = c("FALSE" = "gray","TRUE" = "blue"))
  

```

## SH: each Mutant SH / CS SH

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(str_detect(comparison, "SH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_SH_genotype")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 & abs(log2FoldChange) > 0.1 )) +
  geom_point(size = 0.5, alpha = 1) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,150)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 0.75, legend.position = "bottom") +
  ggtitle("Mutant / CantonS within SH") + 
  scale_color_manual(values = c("FALSE" = "gray","TRUE" = "blue"))
  

```

# Normalized counts for specific genes 

## Fru

```{r }
plot_norm_counts(gene = "fru", dds = deseq_obj_fitted)
```

## Dsx

```{r }
plot_norm_counts("dsx", deseq_obj_fitted)
```

## Dsk

```{r }
plot_norm_counts("Dsk", deseq_obj_fitted)
```

## Housekeeping genes Or negative control genes 

## Housing

```{r}
# Use map function to loop over a vector of gene names (~ map works like lapply)
# Just plotting the top 3 here, but change if needed
map(.x = de$cs_genes_id[1:3], .f = plot_norm_counts , dds = deseq_obj_fitted)
```

## GH

```{r}
map(de$genotype_gh_genes_id[1:3], plot_norm_counts , dds = deseq_obj_fitted)
```

## SH

```{r}
map(de$genotype_sh_genes_id[1:3], plot_norm_counts , dds = deseq_obj_fitted)
```


# Results of ANOVA-like test: Likelihood Ratio Test (LRT)

The likelihood ratio test tells you for each gene, whether there is a significant effect of each term. You can think about it as a two-way anova with two factors:

- Genotype
- Housing

We can ask three questions:

- Genotype: For each gene, is there an effect of genotype? -> this will give us genes that are differentially expressed between genotypes. 
- Housing: For each gene, is there an effect of housing? -> this will give us genes that are differentially expressed between housing. 
- Genotype:Housing interaction: For each gene, is there a genotype-specific change in housing (for example, differentially expressed SH/GH only in CantonS but not in the rest.

## Number of differentially expressed genes in each ANOVA-like LRT comparison

```{r}
# Create a dataframe with number of diff genes in each category
c("genotype" = length(unique(pairwise_log2fc_genotype_df$gene_name)),
  "housing" = length(unique(pairwise_log2fc_housing_df$gene_name)),
  "interaction" = length(unique(pairwise_log2fc_interaction_df$gene_name))) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value,decreasing = TRUE))) %>% # Sort by value
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
    geom_text(aes(label = value),nudge_x = 200, size = 3) +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes LRT")

```

## Genotype

### Number of genes with significant effect of genotype by sign combination pattern

```{r}
pairwise_log2fc_genotype_df_genes <- pairwise_log2fc_genotype_df %>%
  dplyr::select(gene_name, sign_paste_genotype_gh) %>%
  unique()

sort(table(pairwise_log2fc_genotype_df_genes$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  geom_text(aes(label = value),nudge_x = 50, size = 3) +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes genotype")

```

### Heatmap of LRT genotype significant genes log2FoldChange of Mutant GH / CantonS GH


```{r }
pairwise_log2fc_genotype_df_ngenes <- pairwise_log2fc_genotype_df %>%
  group_by(sign_paste_genotype_gh) %>%
  summarise(n_genes = dplyr::n())

pairwise_log2fc_genotype_top_sign_combinations <- pairwise_log2fc_genotype_df_ngenes %>%
  slice_max(order_by = n_genes, n = 10) %>%
  pull(sign_paste_genotype_gh) %>%
  unique()

pairwise_log2fc_genotype_df_join <- left_join(pairwise_log2fc_genotype_df, pairwise_log2fc_genotype_df_ngenes, by = "sign_paste_genotype_gh")

pairwise_log2fc_genotype_df_join %>%
  dplyr::filter(sign_paste_genotype_gh %in% pairwise_log2fc_genotype_top_sign_combinations) %>%
  mutate(sign_paste_genotype_gh = fct_reorder(sign_paste_genotype_gh, desc(n_genes))) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  facet_wrap(ncol = 2,vars(sign_paste_genotype_gh) , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT genotype")  +
  theme(axis.text.y = element_blank())

```

## Housing

```{r }

pairwise_log2fc_housing_df_genes <- pairwise_log2fc_housing_df %>%
  dplyr::select(gene_name, sign_paste) %>%
  unique()


sort(table(pairwise_log2fc_housing_df_genes$sign_paste)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential genes LRT housing") +
  geom_text(aes(label = value),nudge_x = 2, size = 3) 

```

### Heatmap of LRT housing significant genes log2FoldChange of SH / GH within each genotye

```{r fig.width=6, fig.height=13}


pairwise_log2fc_housing_df %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  mutate(gene_name = fct_reorder(gene_name,log2FoldChange)) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 3) +
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("Differential genes LRT housing") 


```

## housing by genotype interaction

```{r }

pairwise_log2fc_interaction_df_genes <- pairwise_log2fc_interaction_df %>%
  dplyr::select(gene_name, sign_paste) %>%
  unique()

sort(table(pairwise_log2fc_interaction_df_genes$sign_paste)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes housing:genotype interaction") +
  geom_text(aes(label = value), nudge_x = 0.5, size = 3) 

```

### Heatmap of LRT interaction significant genes log2FoldChange of SH / GH within each genotye

```{r }

pairwise_log2fc_interaction_df_ngenes <- pairwise_log2fc_interaction_df %>%
  group_by(sign_paste) %>%
  summarise(n_genes = n())

pairwise_log2fc_interaction_top_sign_combinations <- pairwise_log2fc_interaction_df_ngenes %>%
  slice_max(order_by = n_genes, n = 5) %>%
  pull(sign_paste) %>%
  unique()

pairwise_log2fc_interaction_df_join <- left_join(pairwise_log2fc_interaction_df, pairwise_log2fc_interaction_df_ngenes, by = "sign_paste")

pairwise_log2fc_interaction_df_join %>%
  filter(sign_paste %in% pairwise_log2fc_interaction_top_sign_combinations) %>%
  mutate(sign_paste = fct_reorder(sign_paste, desc(n_genes))) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  facet_wrap(ncol = 1,vars(sign_paste) , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT housing:genotype interaction") 

```

Genes that are differential between CantonS and Or47b 

```{r}
pairwise_log2fc_interaction_df_47bdiff <- pairwise_log2fc_interaction_df %>%
  dplyr::filter(sign_paste %in% c("cs:1_dsx:-1_fru:-1_Or47b:-1_Or67d:-1" ,
 "cs:-1_dsx:-1_fru:-1_Or47b:1_Or67d:1"  ,
"cs:1_dsx:-1_fru:1_Or47b:-1_Or67d:-1"  ,
"cs:-1_dsx:1_fru:-1_Or47b:1_Or67d:1"   ,
"cs:-1_dsx:-1_fru:1_Or47b:1_Or67d:-1"  ))

pairwise_log2fc_interaction_df_47bdiff %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  facet_wrap(ncol =1,vars(sign_paste) , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT housing:genotype interaction: 47b different from CS") 

```

### GO

#### GO terms LRT Housing

Genes that are differentially expressed SH/GH consistently across all genotype 

```{r fig.height= 12}
dotplot(go_lrt$housing,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms LRT housing") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

#### GO terms LRT housing by genotype interaction

Genes that show a genotype-specific response to the social environment (e.g.  differentially expressed SH/GH in one genotype but not others, or in multiple genotypes but not one, etc) 

```{r fig.height=12}
dotplot(go_lrt$interaction,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms LRT housing:genotype interaction") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

#### GO terms LRT genotype

Genes that show mutant/WT differential expression consistently across housing conditions.

```{r}
dotplot(go_lrt$housing,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms LRT genotype") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# Correlation with behavior data

```{r}
# Remove data for dsx and fru
deseq_obj_fitted <- deseq_obj_fitted[,! colData(deseq_obj_fitted)$genotype %in% c("DSX","FRU")]
```

## Genes that are differential in genotype by housing interaction LRT and have different fold change sign between CS and Or47b pairwise comparisons

```{r}
interaction_genes <- unique(pairwise_log2fc_interaction_df_47bdiff$gene_name)

interaction_genes_cor <- map_dbl(interaction_genes,~get_ci_counts_cor(.x,dds = deseq_obj_fitted))

names(interaction_genes_cor) <- interaction_genes

interaction_genes_cor <- interaction_genes_cor[order(interaction_genes_cor^2,decreasing = TRUE)]
```

Table of genes sorted by r squared

```{r}
interaction_genes_cor_df <- enframe(interaction_genes_cor)
colnames(interaction_genes_cor_df) <- c("gene_name","pearson")
interaction_genes_cor_df$r_squared <- interaction_genes_cor_df$pearson^2

print_go_table(interaction_genes_cor_df)
```

Plot of top 5 genes ranked by r squared

```{r}
map(names(interaction_genes_cor)[1:1],~plot_regression_gene(.x,dds = deseq_obj_fitted))
```

## Genes that are differential in genotype by housing interaction LRT (with any combination of fold change signs)

```{r}
interaction_genes <- unique(pairwise_log2fc_interaction_df$gene_name)

interaction_genes_cor <- map_dbl(interaction_genes,~get_ci_counts_cor(.x,dds = deseq_obj_fitted))

names(interaction_genes_cor) <- interaction_genes

interaction_genes_cor <- interaction_genes_cor[order(interaction_genes_cor^2,decreasing = TRUE)]
```

Table of genes sorted by r squared

```{r}
interaction_genes_cor_df <- enframe(interaction_genes_cor)
colnames(interaction_genes_cor_df) <- c("gene_name","pearson")
interaction_genes_cor_df$r_squared <- interaction_genes_cor_df$pearson^2

print_go_table(interaction_genes_cor_df)
```

Plot of top 5 genes ranked by r squared

```{r}
map(names(interaction_genes_cor)[1:5],~plot_regression_gene(.x,dds = deseq_obj_fitted))
```

## Genes that are differential in any pairwise housing comparison

```{r}
interaction_genes <- res_long_df %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(padj < 0.05 & abs(log2FoldChange)>0.1) %>%
  pull(gene_name) %>%
  unique()

interaction_genes_cor <- map_dbl(interaction_genes,~get_ci_counts_cor(.x,dds = deseq_obj_fitted))

names(interaction_genes_cor) <- interaction_genes

interaction_genes_cor <- interaction_genes_cor[order(interaction_genes_cor^2,decreasing = TRUE)]
```

Table of genes sorted by r squared

```{r}
interaction_genes_cor_df <- enframe(interaction_genes_cor)
colnames(interaction_genes_cor_df) <- c("gene_name","pearson")
interaction_genes_cor_df$r_squared <- interaction_genes_cor_df$pearson^2

print_go_table(interaction_genes_cor_df)
```

Plot of top 5 genes ranked by r squared

```{r}
map(names(interaction_genes_cor)[1:5],~plot_regression_gene(.x,dds = deseq_obj_fitted))
```

