---
title: "Figure 2 Chromatin changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
date: '2024-02-13'
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r}
# Libraries
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
library(circlize)
library(clusterProfiler)
options(scipen = 999)
```

```{r}
# Functions
# plot z score matrix
plot_heatmap <- function(mat, ...) {
  Heatmap(mat = t(scale(t(mat),center = TRUE,scale = TRUE)), # z score
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), ... )
}
# log2fc matrix
plot_heatmap_log2fc <- function(mat, ...) {
  Heatmap(mat = mat,
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "log2FC",
                                      legend_height = unit(2, "in")) , ... )
}


# Data table that is exportable to CSV file
print_exportable_genes <- function(genes){
  DT::datatable(genes,extensions = 'Buttons',
                options = list(dom= 'Bfrtip',buttons = c('copy', 'csv')))
}

```

```{r}
# Read data

data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```

```{r}
# DESeq files
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```

```{r}
# Results joined files
res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```

```{r}
# VST data for PCA
vsd_h3k4me3 <- readRDS("../data_output/2024-01_diffbind_cutnrun/vsd_h3k4me3.Rds")
vsd_rnapolii <- readRDS("../data_output/2024-01_diffbind_cutnrun/vsd_rnapolii.Rds")

```

```{r}
# Long data frames for volcano plots
res_long_h3k4me3_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_h3k4me3_df.Rds")
res_long_rnapolii_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_rnapolii_df.Rds")

```

```{r}
# Normalized counts for heatmaps
norm_cts_h3k4me3 <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3.Rds")
norm_cts_rnapolii <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii.Rds")

# Median counts for heatmaps

norm_cts_h3k4me3_median <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3_median.Rds")
norm_cts_rnapolii_median <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii_median.Rds")

# Differential peaks 
de_genotype <- readRDS( "../data_output/2024-01_diffbind_cutnrun/de_genotype.Rds")

# log2fc matrix
log2fc_mat_h3k4me3_genotype_gh_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_gh_gene.Rds")
log2fc_mat_h3k4me3_genotype_sh <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_sh.Rds")
log2fc_mat_rnapolii_genotype_gh <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_gh.Rds")
log2fc_mat_rnapolii_genotype_sh <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_sh.Rds")

```

```{r}
# Ranges connected to genes
res_gr_h3k4me3_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_genes.Rds")
res_gr_rnapolii_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes.Rds")

```

```{r}
# Comparisons list
comp_list <- readRDS( "../data_output/2024-01_diffbind_cutnrun/comp_list.Rds")

```


```{r}
# Read pairwise log2fc matrices for LRT results plots
pairwise_log2fc_h3k4me3_df <- readRDS( "../data_output/2024-01_diffbind_cutnrun/pairwise_log2fc_h3k4me3_df.Rds")
pairwise_log2fc_rnapolii_df <- readRDS( "../data_output/2024-01_diffbind_cutnrun/pairwise_log2fc_rnapolii_df.Rds")
```

```{r}
# Normalized counts matrices but rows correspond to one gene only
norm_cts_h3k4me3_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3_gene.Rds")
norm_cts_h3k4me3_median_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_h3k4me3_median_gene.Rds")
norm_cts_rnapolii_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii_gene.Rds")
norm_cts_rnapolii_median_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/norm_cts_rnapolii_median_gene.Rds")
log2fc_mat_h3k4me3_genotype_gh_gene <- readRDS("../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_gh_gene.Rds")
log2fc_mat_rnapolii_genotype_gh_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_gh_gene.Rds")
log2fc_mat_h3k4me3_genotype_sh_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_h3k4me3_genotype_sh_gene.Rds")
log2fc_mat_rnapolii_genotype_sh_gene <- readRDS( "../data_output/2024-01_diffbind_cutnrun/log2fc_mat_rnapolii_genotype_sh_gene.Rds")
```

```{r}
# Peaks that are differential in at least one comparison
diff_ranges <- readRDS( "../data_output/2024-01_diffbind_cutnrun/diff_ranges.Rds")
```

```{r}
# Read fru and dsx target genes 
fru_ma_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 1-fruma_targets.csv")[,-2]
fru_mc_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 2-frumc_targets.csv")[,-2]
fru_mb_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 3-frumb_targets.csv")[,-2]


fru_ma_genes <- fru_ma_genes$FruMA
fru_mc_genes <- fru_mc_genes$FruMC
fru_mb_genes <- fru_mb_genes$FruMB

fru_target_genes <- unique(c(fru_ma_genes, fru_mc_genes, fru_mb_genes))

dsx_target_genes <- readxl::read_excel("../data_input/gene_annotations/dsx_target_genes.xlsx",sheet = 3)
dsx_target_genes <- dsx_target_genes$`Male_Fatbody_DamIDseq_Gene_Level_Occupancy> 0.9`

```

```{r}
# Go terms
res_gr_rnapolii_genes_go <- readRDS(file = "../data_output/2024-1_diffexpr_output/res_gr_rnapolii_genes_go.Rds")
res_gr_h3k4me3_genes_go <- readRDS(file = "../data_output/2024-1_diffexpr_output/res_gr_h3k4me3_genes_go.Rds")

```


# QC of the data: PCA plots between samples

```{r}
plotPCA(vsd_h3k4me3, intgroup = c("condition")) + 
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3")
```

```{r}
plotPCA(vsd_rnapolii, intgroup = c("condition")) + 
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("RNAPolII")

```

# Results of ANOVA-like test: Likelihood Ratio Test (LRT)

The likelihood ratio test tells you for each peak, whether there is a significant effect of each term. You can think about it as a two-way anova with two factors:

- Genotype
- Housing

We can ask three questions:

- Genotype: For each peak, is there an effect of genotype? -> this will give us genes that are differential between genotypes. 
- Housing: For each peak, is there an effect of housing? -> this will give us genes that are differential between housing. 
- Genotype:Housing interaction: For each peak, is there a genotype-specific change in housing (for example, differential SH/GH only in CantonS but not in the rest.

Only genotype term was significant, so showing results for that comparison only.


## H3K4me3


```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_h3k4me3_df$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential H3K4me3 peaks LRT genotype")

```


```{r fig.width=6, fig.height=10}

pairwise_log2fc_h3k4me3_df %>%
  filter(seqnames %in% c("2L","2R","3L","3R","X")) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste_genotype_gh , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("H3K4me3") 


```

## RNAPolII

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_rnapolii_df$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential RNAPolII regions") +
  theme_classic() +
  theme(aspect.ratio = 1)

```

Heatmap 

```{r fig.width=6,fig.height=10}

pairwise_log2fc_rnapolii_df %>%
  filter(seqnames %in% c("2L","2R","3L","3R","X")) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste_genotype_gh , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("RNAPolII")


```

# Pairwise tests

## Volcano plots for different comparisons

## Housing within the same genotype

```{r}
res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"housing")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(pvalue),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3 pairwise")
```

```{r}
res_long_rnapolii_df %>%
  filter(str_detect(comparison,"housing")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
  mutate(comparison = str_remove(comparison,"_housing_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(pvalue),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("RNAPolII pairwise")
```

## GH: all to CS

Pairwise mutant GH / CantonS GH 

```{r}

res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "GH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3 Mutant vs CS GH")


```

```{r}

res_long_rnapolii_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "GH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1)+
  ggtitle("RNAPolII Mutant vs CS GH")


```

## SH: all to a CS

```{r}

res_long_h3k4me3_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "SH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"H3K4me3_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3 Mutant vs CS SH")


```

```{r}

res_long_rnapolii_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "SH")) %>%
  filter(!str_detect(comparison,"lrt")) %>%
    mutate(comparison = str_remove(comparison,"_genotype_ashr")) %>%
  mutate(comparison = str_remove(comparison,"RNAPolII_")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_grid(cols = vars(comparison)) +
  ylim(c(0,100)) +
  xlim(c(-5,5)) +
  theme_classic() +
  theme(aspect.ratio = 1)+
  ggtitle("RNAPolII Mutant vs CS SH")


```


# Table of genes matched to differential CUT&RUN peaks

The table contains:
- DESEQ2 results for all differential peaks that were linked to the nearest gene (distance from peak to nearest gene is shown in distance column)

```{r}
res_gr_h3k4me3_genes %>%
  unique()%>%
  as.data.frame() %>%
  drop_na(gene_name) %>%
  dplyr::select(gene_name, distance, (starts_with("log2Fold")|starts_with("padj"))) %>% 
arrange(gene_name) %>%
  DT::datatable(extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))
```

# Stats of connection of peaks to genes  

## H3K4me3 Peak annotation 

```{r}
library(ChIPseeker) # Annotation functions for peaks
library(TxDb.Dmelanogaster.UCSC.dm6.ensGene) # Fly transcripts, promoters annotation

# Changing the names of chromosomes
res_gr_h3k4me3_genes_uscs <- res_gr_h3k4me3_genes
seqlevels(res_gr_h3k4me3_genes_uscs) <- paste0("chr",seqlevels(res_gr_h3k4me3_genes_uscs)) # Add "chr" to chromosome names

# Function to annotate peaks
res_gr_h3k4me3_anno <- ChIPseeker::annotatePeak(unique(granges(res_gr_h3k4me3_genes_uscs)), # peaks object
                                                TxDb =TxDb.Dmelanogaster.UCSC.dm6.ensGene) # annotation object

ChIPseeker::plotAnnoBar(res_gr_h3k4me3_anno)
ChIPseeker::plotDistToTSS(res_gr_h3k4me3_anno)
ChIPseeker::upsetplot(res_gr_h3k4me3_anno)
```

## H3K4me3 Peak annotation GO

```{r}

res_gr_h3k4me3_genes_mapped_to_genes <- as_data_frame(res_gr_h3k4me3_genes) %>%
  dplyr::select(gene_name, entrez_id, distance, range_id, starts_with("padj")) %>%
  pivot_longer(cols = starts_with("padj"), names_to = "comparison",values_to = "padj") %>%
  filter(padj < 0.05) %>%
  filter(distance < 3000) %>% # Distance to TSS filter
  dplyr::select(gene_name, entrez_id,comparison) %>%
  unique()

library(clusterProfiler)
library(org.Dm.eg.db)
# cluterProfiler for go terms
res_gr_h3k4me3_genes_mapped_to_genes_go <- clusterProfiler::compareCluster(split(x = res_gr_h3k4me3_genes_mapped_to_genes$entrez_id, res_gr_h3k4me3_genes_mapped_to_genes$comparison), OrgDb = org.Dm.eg.db,qvalueCutoff = 0.05, readable = TRUE)


dotplot(res_gr_h3k4me3_genes_mapped_to_genes_go,showCategory = Inf)

cnetplot(res_gr_h3k4me3_genes_mapped_to_genes_go,showCategory = Inf)
```

## RNAPolII Peak annotation 

```{r}

res_gr_rnapolii_genes_uscs <- res_gr_rnapolii_genes
seqlevels(res_gr_rnapolii_genes_uscs) <- paste0("chr",seqlevels(res_gr_rnapolii_genes_uscs))


res_gr_rnapolii_anno <- ChIPseeker::annotatePeak(unique(granges(res_gr_rnapolii_genes_uscs)),TxDb =TxDb.Dmelanogaster.UCSC.dm6.ensGene)

plotAnnoBar(res_gr_rnapolii_anno)
plotDistToTSS(res_gr_rnapolii_anno)

```
## RNAPolII Peak annotation GO

```{r}

res_gr_rnapolii_genes_mapped_to_genes <- as_data_frame(res_gr_rnapolii_genes) %>%
  dplyr::select(gene_name, entrez_id, distance, range_id, starts_with("padj")) %>%
  pivot_longer(cols = starts_with("padj"), names_to = "comparison",values_to = "padj") %>%
  filter(padj < 0.05) %>%
  filter(distance < 3000) %>%
  dplyr::select(gene_name, entrez_id,comparison) %>%
  unique()

res_gr_rnapolii_genes_mapped_to_genes_go <- clusterProfiler::compareCluster(split(x = res_gr_rnapolii_genes_mapped_to_genes$entrez_id, res_gr_rnapolii_genes_mapped_to_genes$comparison), OrgDb = org.Dm.eg.db,qvalueCutoff = 0.05, readable = TRUE)

dotplot(res_gr_rnapolii_genes_mapped_to_genes_go,showCategory = Inf)

cnetplot(res_gr_rnapolii_genes_mapped_to_genes_go,showCategory = Inf)

```

# Heatmaps:

### GH vs wt

#### Per-row Z score matrix showing all replicates

##### for all DEGs

```{r fig.height=10}
get_lgl_from_rownames <- function(row_names, genes_to_subset) {
  return((str_split(row_names,pattern = "-",n = 2) %>% map_chr(1)) %in% genes_to_subset)
}

plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene),diff_ranges$h3k4me3_gh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_gh_genes))
```

```{r fig.height=10}

diff_ranges$rnapolii_gh_genes <- diff_ranges$rnapolii_gh_genes[diff_ranges$rnapolii_gh_genes %in% rownames(norm_cts_rnapolii_gene)]

plot_heatmap(norm_cts_rnapolii_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_gene), diff_ranges$rnapolii_gh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 


```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_gh_genes))
```

##### fru: differential peaks subset by whether they are fru targets

```{r}
diff_ranges$h3k4me3_gh_genes_fru <- diff_ranges$h3k4me3_gh_genes[diff_ranges$h3k4me3_gh_genes %in% fru_target_genes]

plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene),diff_ranges$h3k4me3_gh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_gh_genes_fru))
```

```{r}
diff_ranges$rnapolii_gh_genes_fru <- diff_ranges$rnapolii_gh_genes[diff_ranges$rnapolii_gh_genes %in% fru_target_genes]


plot_heatmap(norm_cts_rnapolii_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_gene),diff_ranges$rnapolii_gh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_gh_genes_fru))
```

##### dsx: differential peaks subset by whether they are dsx targets

```{r}
diff_ranges$h3k4me3_gh_genes_dsx <- diff_ranges$h3k4me3_gh_genes[diff_ranges$h3k4me3_gh_genes %in% dsx_target_genes]

plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene),diff_ranges$h3k4me3_gh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_gh_genes_dsx))
```


```{r}
diff_ranges$rnapolii_gh_genes_dsx <- diff_ranges$rnapolii_gh_genes[diff_ranges$rnapolii_gh_genes %in% dsx_target_genes]

plot_heatmap(norm_cts_rnapolii_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_gene),diff_ranges$rnapolii_gh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_gh_genes_dsx))
```

##### go

#### Z score median

##### for all DEGs

H3K4me3

```{r fig.height=10}
plot_heatmap(norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),diff_ranges$h3k4me3_gh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_gh_genes))
```

RNAPolII 

```{r fig.height=10}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_gh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_gh_genes))
```

##### FRU targets

H3K4me3 

```{r}
plot_heatmap(norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),diff_ranges$h3k4me3_gh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_gh_genes_fru))
```

RNAPolII

```{r}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_gh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_gh_genes_fru))
```

##### dsx

H3K4me3

```{r}
plot_heatmap(norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),diff_ranges$h3k4me3_gh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_gh_genes_dsx))
```

RNAPolII

```{r}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_gh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_gh_genes_dsx))
```

##### go

#### log2FC

##### for all DEGs

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_gh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```
Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_gh_gene)))
```

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_gh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_gh_gene)))
```

##### fru targets

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_gh_gene),fru_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_gh_gene), fru_target_genes),])))
```

RNAPolII

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_gh_gene),fru_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_gh_gene) ,fru_target_genes),])))
```

##### dsx targets

H3K4me3

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_gh_gene) ,dsx_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```


Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_gh_gene) , dsx_target_genes),])))
```


RNAPolII

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_gh_gene), dsx_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_gh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_gh_gene), dsx_target_genes),])))
```


##### go

### SH vs wt

#### Z score all reps

##### for all DEGs

H3K4me3

```{r fig.height=10}


plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene),diff_ranges$h3k4me3_sh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_sh_genes))
```

RNAPolII

```{r fig.height=10}

diff_ranges$rnapolii_sh_genes <- diff_ranges$rnapolii_sh_genes[diff_ranges$rnapolii_sh_genes %in% rownames(norm_cts_rnapolii)]

plot_heatmap(norm_cts_rnapolii_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_gene),diff_ranges$rnapolii_sh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 


```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_sh_genes))
```

##### fru targets

```{r}
diff_ranges$h3k4me3_sh_genes_fru <- diff_ranges$h3k4me3_sh_genes[diff_ranges$h3k4me3_sh_genes %in% fru_target_genes]

plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene),diff_ranges$h3k4me3_sh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_sh_genes_fru))
```

```{r}
diff_ranges$rnapolii_sh_genes_fru <- diff_ranges$rnapolii_sh_genes[diff_ranges$rnapolii_sh_genes %in% fru_target_genes]


plot_heatmap(norm_cts_rnapolii_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_gene),diff_ranges$rnapolii_sh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_sh_genes_fru))
```

##### dsx targets

```{r}
diff_ranges$h3k4me3_sh_genes_dsx <- diff_ranges$h3k4me3_sh_genes[diff_ranges$h3k4me3_sh_genes %in% dsx_target_genes]

plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene), diff_ranges$h3k4me3_sh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_sh_genes_dsx))
```


```{r}
diff_ranges$rnapolii_sh_genes_dsx <- diff_ranges$rnapolii_sh_genes[diff_ranges$rnapolii_sh_genes %in% dsx_target_genes]

plot_heatmap(norm_cts_rnapolii[get_lgl_from_rownames(rownames(norm_cts_rnapolii),diff_ranges$rnapolii_sh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_sh_genes_dsx))
```

##### go

#### Z score median

##### for all DEGs

H3K4me3

```{r fig.height=10}
plot_heatmap(norm_cts_h3k4me3_median_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_median_gene),diff_ranges$h3k4me3_sh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_sh_genes))
```

RNAPolII 

```{r fig.height=10}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_sh_genes),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_sh_genes))
```

##### FRU targets

H3K4me3 

```{r}
plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene),diff_ranges$h3k4me3_sh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_sh_genes_fru))
```

RNAPolII

```{r}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_sh_genes_fru),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_sh_genes_fru))
```

##### dsx

H3K4me3

```{r}
plot_heatmap(norm_cts_h3k4me3_gene[get_lgl_from_rownames(rownames(norm_cts_h3k4me3_gene),diff_ranges$h3k4me3_sh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$h3k4me3_sh_genes_dsx))
```

RNAPolII

```{r}
plot_heatmap(norm_cts_rnapolii_median_gene[get_lgl_from_rownames(rownames(norm_cts_rnapolii_median_gene),diff_ranges$rnapolii_sh_genes_dsx),], show_row_names = TRUE, cluster_rows = TRUE) 
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = diff_ranges$rnapolii_sh_genes_dsx))
```

##### go

#### log2FC

##### for all DEGs

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_sh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```
Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_sh_gene)))
```

```{r fig.height=10}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_sh_gene,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_sh_gene)))
```

##### fru targets

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_sh[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_sh_gene) , fru_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_sh_gene[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_sh_gene), fru_target_genes),])))
```

RNAPolII

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_sh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_sh_gene), fru_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_sh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_sh_gene), fru_target_genes),])))
```

##### dsx targets

H3K4me3

```{r}
plot_heatmap_log2fc(log2fc_mat_h3k4me3_genotype_sh_gene[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_sh_gene), dsx_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```


Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_h3k4me3_genotype_sh_gene[get_lgl_from_rownames(rownames(log2fc_mat_h3k4me3_genotype_sh_gene), dsx_target_genes),])))
```


RNAPolII

```{r}
plot_heatmap_log2fc(log2fc_mat_rnapolii_genotype_sh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_sh_gene), dsx_target_genes),],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-4,0,4),
                                     colors = c("blue","white","red")),
                    show_row_names = TRUE)
```

Get the genes underlying this heatmap:

```{r}
print_exportable_genes(data.frame("genes" = rownames(log2fc_mat_rnapolii_genotype_sh_gene[get_lgl_from_rownames(rownames(log2fc_mat_rnapolii_genotype_sh_gene), dsx_target_genes),])))
```


# Venn diagram with (at least) three groups of DEGs:

## Plot venn diagrams

## GH: all to CS

### All

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Up

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

## SH: all to a CS

### All

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Up

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_h3k4me3_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH DOWN H3K4me3") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_rnapolii_rangeid, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH DOWN RNAPolII") + scale_x_continuous(expand = expansion(mult = .2))
```

# GO terms for different comparisons, distance-based gene to peak connections

```{r}
dotplot(res_gr_h3k4me3_genes_go,showCategory = Inf, by='GeneRatio') +
  ggtitle("GO terms H3K4me3")
```

```{r}
cnetplot( res_gr_h3k4me3_genes_go,showCategory = Inf, by='GeneRatio') +
  ggtitle("GO terms H3K4me3")

```

Get GO Table with genes:

```{r}
DT::datatable(res_gr_h3k4me3_genes_go@compareClusterResult,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))
```


```{r}
dotplot(res_gr_rnapolii_genes_go,showCategory = Inf, by='GeneRatio') +
  ggtitle("GO terms RNAPolII")
```


```{r}
cnetplot(clusterProfiler::simplify( res_gr_rnapolii_genes_go),showCategory = Inf, by='GeneRatio') +
  ggtitle("GO terms RNAPolII")

```

Get GO Table with genes:

```{r}
DT::datatable(res_gr_rnapolii_genes_go@compareClusterResult,extensions = 'Buttons',
                options = list(scrollX = TRUE, dom= 'Bfrtip',buttons = c('copy', 'csv')))
```


