---
title: "R Notebook"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```



# Overview

## Figure 1 RNA-seq changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants

# Libraries
```{r}
library(ComplexHeatmap) # Heatmaps
library(DESeq2) 
library(ggVennDiagram) 
library(clusterProfiler) # Go terms
library(org.Dm.eg.db) # GO annotation
library(tidyverse)
library(circlize) # Colors
```

# Functions
```{r}
# plot z score matrix
plot_heatmap <- function(mat, ...) {
  Heatmap(mat = t(scale(t(mat),center = TRUE,scale = TRUE)), # z score
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "Z score",
                                      legend_height = unit(2, "in")), ... )
}
# log2fc matrix
plot_heatmap_log2fc <- function(mat, ...) {
  Heatmap(mat = mat,
          cluster_columns = FALSE,
          heatmap_legend_param = list(title = "log2FC",
                                      legend_height = unit(2, "in")) , ... )
}


```

# Read data

```{r}
data_dir <- "../data_output/2024-1_diffexpr_input/"
```

DESeq files raw
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```

DESeq files fitted 

```{r}
deseq_obj_fitted <- readRDS("../data_output/2024-1_diffexpr_output/social_mutants_housing_lrt_deseq_obj_fitted.Rds")
```

Results joined files

```{r}
res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```

# Data re-shaping

## Add entrezid column
```{r}
symbol_etrez_map_df <- clusterProfiler::bitr(geneID = res_df$gene_name, fromType = "SYMBOL",toType ="ENTREZID",OrgDb = org.Dm.eg.db )
symbol_etrez_map <- symbol_etrez_map_df$ENTREZ 
names(symbol_etrez_map) <-  symbol_etrez_map_df$SYMBOL

res_df$entrezid <- symbol_etrez_map[res_df$gene_name]

```


## Pivot Longer

### Data transform for volcano plots
```{r}
log2fc_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("log2FoldChange")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

rawlog2fc_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("rawlog2FoldChange")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "rawlog2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"rawlog2FoldChange_" ))

padj_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("padj")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("pvalue")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df %>%
  dplyr::select(gene_name,entrezid, starts_with("baseMean")) %>%
  pivot_longer(c(-gene_name,-entrezid), names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long,rawlog2fc_long, log2fc_long, padj_long, pval_long)
res_long_df <- purrr::reduce(res_long_list,left_join,by =c("gene_name","entrezid","comparison") )
```

## Make lists for different combinations of comparisons


Get all genes that are diff expressed in at least one comparison
```{r}
res_long_df_diff_any <- res_long_df %>%
  drop_na(padj) %>%
  filter(padj < 0.01)
```


## Housing within the same genotype

### All
```{r}
comp_list_housing_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
  mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")

```
### Up
```{r}
comp_list_housing_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

### Down
```{r}
comp_list_housing_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_housing_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"housing") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
    mutate(comparison = str_remove(comparison, "_housing")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

## GH: all to CS

### All
```{r}

comp_list_genotype_gh_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
    mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

### Up
```{r}
comp_list_genotype_gh_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

### Down
```{r}
comp_list_genotype_gh_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_gh_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_GH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

## SH: all to CS


### All
```{r}

comp_list_genotype_sh_all_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_all_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```

### Up
```{r}
comp_list_genotype_sh_up_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_up_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange > 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")
```

### Down
```{r}
comp_list_genotype_sh_down_symbol <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(gene_name, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("gene_name")

comp_list_genotype_sh_down_entrezid <- res_long_df_diff_any %>%
  filter(str_detect(comparison,"_SH") & str_detect(comparison,"genotype") & ! str_detect(comparison,"lrt")) %>%
  filter(log2FoldChange < 0) %>%
  dplyr::select(entrezid, comparison) %>%
      mutate(comparison = str_remove(comparison, "_genotype")) %>%
  split(.$comparison) %>%
  map("entrezid")

```


# Figure 1&2  Social experience in combination with components of courtship neuronal circuits affect transcriptome of male Drosophila brains 

# Set up of the bulk RNA-seq experiment 
# QC of the data: PCA plots

# PCA between samples

```{r}
vsd_combat <- vst(deseq_list$social_mutants.salmon.merged.gene_counts.rds)

plotPCA(vsd_combat , intgroup = "condition") + ggtitle("PCA RNA-seq samples") +
  theme_classic() +
  theme(aspect.ratio = 1)

```


# Data summary plots

## Number of DEGs

```{r}
res_long_df %>% 
  select(comparison, padj) %>%
  drop_na(padj) %>%
  filter(padj < 0.01)  %>%
  group_by(comparison) %>%
  summarise(n_diff = n()) %>%
  ungroup() %>%
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff)) %>%
  ggplot(aes(n_diff, comparison)) +
  geom_col() +
  theme_classic() +
  geom_text(aes(label = n_diff), nudge_x = 500, size = 3) +
  theme(aspect.ratio = 1) +
  ggtitle("Number of differentially expressed genes") +
  xlab("Number of genes padj < 0.01")

```

```{r}
res_long_df %>% 
  filter(str_detect(comparison, "lrt")) %>%
  select(comparison, padj) %>%
  drop_na(padj) %>%
  filter(padj < 0.01)  %>%
  group_by(comparison) %>%
  summarise(n_diff = n()) %>%
  mutate(comparison = str_remove(comparison, "social_mutants_")) %>%
  mutate(comparison = fct_reorder(comparison, n_diff)) %>%
  ggplot(aes(n_diff, comparison)) +
  geom_col() +
  theme_classic() +
  geom_text(aes(label = n_diff), nudge_x = 500, size = 3) +
  theme(aspect.ratio = 1) +
  ggtitle("Number of differentially expressed genes") +
  xlab("Number of genes padj < 0.01")

```


```{r}
res_long_df %>% 
  filter(!str_detect(comparison, "lrt")) %>%
  filter(str_detect(comparison,"housing")) %>%
  select(comparison, padj) %>%
  drop_na(padj) %>%
  filter(padj < 0.01)  %>%
  group_by(comparison) %>%
  summarise(n_diff = n()) %>%
  ungroup() %>%
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff)) %>%
  ggplot(aes(n_diff, comparison)) +
  geom_col() +
  theme_classic() +
  geom_text(aes(label = n_diff), nudge_x = 20, size = 3) +
  theme(aspect.ratio = 1) +
  ggtitle("Number of differentially expressed genes") +
  xlab("Number of genes padj < 0.01")

```

```{r}
res_long_df %>% 
  filter(!str_detect(comparison, "lrt")) %>%
  filter(str_detect(comparison,"genotype")) %>%
  select(comparison, padj) %>%
  drop_na(padj) %>%
  filter(padj < 0.01)  %>%
  group_by(comparison) %>%
  summarise(n_diff = n()) %>%
  ungroup() %>%
  mutate(comparison = fct_reorder(.f = as.factor(comparison), .x = n_diff)) %>%
  ggplot(aes(n_diff, comparison)) +
  geom_col() +
  theme_classic() +
  geom_text(aes(label = n_diff), nudge_x = 500, size = 3) +
  theme(aspect.ratio = 1) +
  ggtitle("Number of differentially expressed genes") +
  xlab("Number of genes padj < 0.01")

```

# Venn diagram with (at least) three groups of DEGs:

## Housing within the same genotype

### All
```{r}
ggVennDiagram::ggVennDiagram(comp_list_housing_all_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Housing within genotype All")
```
### Up
```{r}
ggVennDiagram::ggVennDiagram(comp_list_housing_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Housing within genotype UP") 
```

### Down
```{r}
ggVennDiagram::ggVennDiagram(comp_list_housing_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Housing within genotype DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```

## GH: all to CS

### All
```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_all_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))
```
### Up
```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down
```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_gh_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```


## SH: all to a CS

### All
```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_all_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH All") + scale_x_continuous(expand = expansion(mult = .2))
```
### Up
```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_up_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

### Down
```{r}
ggVennDiagram::ggVennDiagram(comp_list_genotype_sh_down_symbol, label_alpha = 0, label = "count", label_color = "white", label_size = 5) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS SH DOWN") + scale_x_continuous(expand = expansion(mult = .2))
```


# GO terms for different comparisons

Get universe
```{r}
go_universe<- res_long_df %>%
  drop_na(padj, pvalue) %>%
  pull(entrezid) %>%
  unique()
```


##Housing within the same genotype

### All

```{r}
go_housing_all_entrezid <- compareCluster(geneClusters = comp_list_housing_all_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_housing_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms housing ALL")

```

### Up
```{r}
go_housing_up_entrezid <- compareCluster(geneClusters = comp_list_housing_up_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_housing_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms housing UP")

```

### Down
```{r}
go_housing_down_entrezid <- compareCluster(geneClusters = comp_list_housing_down_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_housing_down_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms housing Down")

```


##GH: all to CS

### All

```{r}
go_genotype_gh_all_entrezid <- compareCluster(geneClusters = comp_list_genotype_gh_all_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_genotype_gh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH ALL")

```

### Up

```{r}
go_genotype_gh_up_entrezid <- compareCluster(geneClusters = comp_list_genotype_gh_up_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_genotype_gh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH UP")

```

### Down
```{r}
go_genotype_gh_down_entrezid <- compareCluster(geneClusters = comp_list_genotype_gh_down_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_genotype_gh_down_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS GH Down")

```

##SH: all to a CS

### All

```{r}
go_genotype_sh_all_entrezid <- compareCluster(geneClusters = comp_list_genotype_sh_all_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_genotype_sh_all_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH ALL")

```

### Up

```{r}
go_genotype_sh_up_entrezid <- compareCluster(geneClusters = comp_list_genotype_sh_up_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_genotype_sh_up_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH UP")

```

### Down
```{r}
go_genotype_sh_down_entrezid <- compareCluster(geneClusters = comp_list_genotype_gh_down_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_genotype_sh_down_entrezid,showCategory = 5, by='GeneRatio') +
  ggtitle("GO terms Mutant vs CantonS SH Down")

```

# Heatmaps:

## Data re-shaping

### Build norm counts z score matrix

```{r}
norm_cts <- counts(deseq_obj_fitted,norm =TRUE)
```

```{r}
de_cs_genes_id <- res_long_df %>%
  dplyr::select(gene_name, comparison, padj, log2FoldChange) %>%
  filter(comparison == "CS_housing") %>%
  filter(padj < 0.01) %>%
  arrange(log2FoldChange) %>%
  pull(gene_name) %>%
  unique()

de_genotype_gh_genes_id <- res_long_df %>%
  dplyr::select(gene_name, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "GH_genotype")) %>%
  filter(padj < 0.01) %>%
  pull(gene_name) %>%
  unique()

de_genotype_sh_genes_id <- res_long_df %>%
  dplyr::select(gene_name, comparison, padj, log2FoldChange) %>%
  filter(str_detect(comparison, "SH_genotype")) %>%
  filter(padj < 0.01) %>%
  pull(gene_name) %>%
  unique()

```

Norm counts median per group

```{r}
# Remove rows with zero counts
norm_cts_filt <- norm_cts[rowSums(norm_cts) > 0,]

# Get mean matrix
norm_cts_median <- as.data.frame(norm_cts_filt) %>% # convert matrix to data frame, makes it compatible with dplyr
  rownames_to_column(var = "gene_symbol") %>% # move rownames to a new column, makes it compatible with dplyr 
  pivot_longer(cols = -gene_symbol, # make data.frame in tidy format
               names_to = "sample_name",
               values_to = "normalizedCounts") %>% 
  mutate(condition = str_remove(sample_name, "_R\\d$")) %>% # Make condition variables 
  group_by(gene_symbol, condition) %>% # Group by experimental condition 
  summarise(normalizedCounts_median = median(normalizedCounts)) %>% # Calculate mean per groups 
  pivot_wider(names_from = condition, # Return from tidy to matrix format 
              values_from = normalizedCounts_median)
# process matrix further as a numeric matrix format with rownames, compatible with ComplexHeatmap
norm_cts_median <- as.data.frame(norm_cts_median) 
rownames(norm_cts_median) <- norm_cts_median$gene_symbol
norm_cts_median <- norm_cts_median %>%
  dplyr::select(- gene_symbol)
norm_cts_median <- as.matrix(norm_cts_median)

# Get factor with genotype info to use to separate heatmap into subsections
genotype_split <-  str_split(colnames(norm_cts_median),"_",n = 2) %>% map_chr(1)

```

### Build log2Fold change matrix
Select only log2FoldChane variables

```{r}
log2fc_mat_housing <- res_df %>%
  drop_na(padj_CS_housing) %>%
  filter(padj_CS_housing < 0.01 & abs(log2FoldChange_CS_housing) > 0) %>%
  dplyr::select(gene_name, starts_with("log2FoldChange") & contains("housing") & ! contains("lrt")) %>%
  arrange(log2FoldChange_CS_housing) %>%
  column_to_rownames(var = "gene_name") %>%
  as.matrix()

log2fc_mat_genotype_gh<- res_df %>%
    filter(padj_DSX_GH_genotype < 0.01 | 
           padj_FRU_GH_genotype < 0.01 |
           padj_Or67d_GH_genotype < 0.01 |
           padj_Or47b_GH_genotype) %>%
  dplyr::select(gene_name, starts_with("log2FoldChange") & contains("GH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "gene_name") %>%
  as.matrix()

log2fc_mat_genotype_sh<- res_df %>%
      filter(padj_DSX_SH_genotype < 0.01 | 
           padj_FRU_SH_genotype < 0.01 |
           padj_Or67d_SH_genotype < 0.01 |
           padj_Or47b_SH_genotype) %>%
  dplyr::select(gene_name, starts_with("log2FoldChange") & contains("SH_genotype") & ! contains("lrt")) %>%
  column_to_rownames(var = "gene_name") %>%
  as.matrix()

colnames(log2fc_mat_housing) <- str_remove(colnames(log2fc_mat_housing) ,"log2FoldChange_")
colnames(log2fc_mat_housing) <- str_remove(colnames(log2fc_mat_housing) ,"_housing")

colnames(log2fc_mat_genotype_gh) <- str_remove(colnames(log2fc_mat_genotype_gh) ,"log2FoldChange_")
colnames(log2fc_mat_genotype_gh) <- str_remove(colnames(log2fc_mat_genotype_gh) ,"_genotype")

colnames(log2fc_mat_genotype_sh) <- str_remove(colnames(log2fc_mat_genotype_sh) ,"log2FoldChange_")
colnames(log2fc_mat_genotype_sh) <- str_remove(colnames(log2fc_mat_genotype_sh) ,"_genotype")
```

### Read target genes

#### Fru

```{r}
fru_ma_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 1-fruma_targets.csv")[,-2]
fru_mc_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 2-frumc_targets.csv")[,-2]
fru_mb_genes <- read_csv("../data_input/gene_annotations/fru_targets/Sheet 3-frumb_targets.csv")[,-2]


fru_ma_genes <- fru_ma_genes$FruMA
fru_mc_genes <- fru_mc_genes$FruMC
fru_mb_genes <- fru_mb_genes$FruMB

fru_target_genes <- unique(c(fru_ma_genes, fru_mc_genes, fru_mb_genes))
```


```{r}
de_cs_genes_id_fru <- de_cs_genes_id[de_cs_genes_id %in% fru_target_genes]
de_genotype_gh_genes_id_fru <- de_genotype_gh_genes_id[de_genotype_gh_genes_id %in% fru_target_genes]
de_genotype_sh_genes_id_fru <- de_genotype_sh_genes_id[de_genotype_sh_genes_id %in% fru_target_genes]

```


#### dsx

```{r}
dsx_target_genes <- readxl::read_excel("../data_input/gene_annotations/dsx_target_genes.xlsx",sheet = 3)
dsx_target_genes <- dsx_target_genes$`Male_Fatbody_DamIDseq_Gene_Level_Occupancy> 0.9`
```


```{r}
de_cs_genes_id_dsx <- de_cs_genes_id[de_cs_genes_id %in% dsx_target_genes]
de_genotype_gh_genes_id_dsx <- de_genotype_gh_genes_id[de_genotype_gh_genes_id %in% dsx_target_genes]
de_genotype_sh_genes_id_dsx <- de_genotype_sh_genes_id[de_genotype_sh_genes_id %in% dsx_target_genes]

```

#### go
metabolism 
defense response
redox 
reproductive behavior 
feeding behavior 

### Housing within the same genotype

#### Z score all reps

##### for all DEGs

```{r}
plot_heatmap(norm_cts[de_cs_genes_id,], show_row_names = FALSE, cluster_rows = FALSE)
```

##### fru
```{r}
plot_heatmap(norm_cts[de_cs_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)

```


##### dsx
```{r}
plot_heatmap(norm_cts[de_cs_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)

```
##### go


#### Z score median

##### for all DEGs

```{r}
plot_heatmap(norm_cts_median[de_cs_genes_id,], show_row_names = FALSE, cluster_rows = FALSE)
```

##### fru

```{r}
plot_heatmap(norm_cts_median[de_cs_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### dsx

```{r}
plot_heatmap(norm_cts_median[de_cs_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```
##### go

#### log2FC

##### for all DEGs

```{r}
plot_heatmap_log2fc(log2fc_mat_housing,
                    cluster_rows = FALSE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### fru

```{r}
plot_heatmap_log2fc(log2fc_mat_housing[rownames(log2fc_mat_housing) %in% de_cs_genes_id_fru,],
                    cluster_rows = FALSE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### dsx

```{r}
plot_heatmap_log2fc(log2fc_mat_housing[rownames(log2fc_mat_housing) %in% de_cs_genes_id_dsx,],
                    cluster_rows = FALSE,
                    col = colorRamp2(breaks = c(-2,0,2),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### go

### GH vs wt

#### Z score all reps

##### for all DEGs

```{r}
plot_heatmap(norm_cts[de_genotype_gh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### fru
```{r}
plot_heatmap(norm_cts[de_genotype_gh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```
##### dsx
```{r}
plot_heatmap(norm_cts[de_genotype_gh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```
##### go

#### Z score median

##### for all DEGs

```{r}
plot_heatmap(norm_cts_median[de_genotype_gh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### fru
##### dsx
##### go


#### log2FC

##### for all DEGs

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### fru

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[rownames(log2fc_mat_genotype_gh) %in% de_genotype_gh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### dsx

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_gh[rownames(log2fc_mat_genotype_gh) %in% de_genotype_gh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### go

### SH vs wt

#### Z score all reps

##### for all DEGs

```{r}
plot_heatmap(norm_cts[de_genotype_sh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### fru

```{r}
plot_heatmap(norm_cts[de_genotype_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### dsx

```{r}
plot_heatmap(norm_cts[de_genotype_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### go

#### Z score median

##### for all DEGs

```{r}
plot_heatmap(norm_cts_median[de_genotype_sh_genes_id,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### fru

```{r}
plot_heatmap(norm_cts_median[de_genotype_sh_genes_id_fru,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### dsx

```{r}
plot_heatmap(norm_cts_median[de_genotype_sh_genes_id_dsx,], show_row_names = FALSE, cluster_rows = TRUE)
```

##### go


#### log2FC

##### for all DEGs

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh,
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")),
                    show_row_names = FALSE)
```

##### fru

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[rownames(log2fc_mat_genotype_sh) %in% de_genotype_sh_genes_id_fru,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")), 
                    show_row_names = FALSE)
```

##### dsx

```{r}
plot_heatmap_log2fc(log2fc_mat_genotype_sh[rownames(log2fc_mat_genotype_sh) %in% de_genotype_sh_genes_id_dsx,],
                    cluster_rows = TRUE,
                    col = colorRamp2(breaks = c(-1,0,1),
                                     colors = c("blue","white","red")), 
                    show_row_names = FALSE)
```

##### go

# Volcano plots for different comparisons

## Housing within the same genotype

```{r}

res_long_df %>%
  filter(str_detect(comparison,"housing")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison) +
  ylim(c(0,100)) +
  xlim(c(-10,10)) +
  theme_classic() +
  theme(aspect.ratio = 1)


```

## GH: all to CS

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(str_detect(comparison, "GH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison) +
  ylim(c(0,100)) +
  xlim(c(-10,10)) +
  theme_classic() +
  theme(aspect.ratio = 1)


```

## SH: all to a CS

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
  filter(str_detect(comparison, "SH")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.01 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison) +
  ylim(c(0,100)) +
  xlim(c(-10,10)) +
  theme_classic() +
  theme(aspect.ratio = 1)


```

# Normalized counts for specific genes 

```{r}
plot_norm_counts <- function(gene, dds) {
  DESeq2::plotCounts(gene, dds = dds, transform = FALSE,returnData = TRUE, intgroup = c("condition","genotype","housing","dissection")) %>%
      ggplot(aes(housing, count, color = condition)) +
  geom_jitter(width = 0.2, alpha = 0.7) +
  stat_summary() +
  facet_grid(cols = vars(genotype)) +
  theme_light() +
  theme(aspect.ratio = 1, legend.position = "none") +
  ylab("Normalized Counts") +
  xlab(NULL) +
  ggtitle(gene) 

}

```

## Fru

```{r }
plot_norm_counts("fru", deseq_obj_fitted)
```

## Dsx

```{r }
plot_norm_counts("dsx", deseq_obj_fitted)
```

## Dsk

```{r }
plot_norm_counts("Dsk", deseq_obj_fitted)
```

## to

```{r }
plot_norm_counts("to", deseq_obj_fitted)
```

## Housekeeping genes Or negative control genes 


## Housing
```{r}
map(de_cs_genes_id[1:3], plot_norm_counts , dds = deseq_obj_fitted)
```

## GH

```{r}
map(de_genotype_gh_genes_id[1:3], plot_norm_counts , dds = deseq_obj_fitted)
```

## SH
```{r}
map(de_genotype_sh_genes_id[1:3], plot_norm_counts , dds = deseq_obj_fitted)
```

# LRT results (ANOVA-like test)

## Data wrangling

Split  based on log2fc sign combinations

```{r}

my_sign <- function(x, cutoff = 0.1) {
  ifelse(between(x, -cutoff, cutoff),sign(0),sign(x))
}

res_df <- res_df %>%
  mutate(across(starts_with("log2FoldChange"),my_sign,.names = "sign_{.col}"))

res_df <- res_df %>%
  mutate(sign_paste_genotype_gh = paste0(
    "dsx-gh:",sign_log2FoldChange_DSX_GH_genotype,
    "_fru-gh:",sign_log2FoldChange_FRU_GH_genotype,
    "_Or47b-gh:",sign_log2FoldChange_Or47b_GH_genotype,
    "_Or67d-gh:",sign_log2FoldChange_Or67d_GH_genotype),
    sign_paste_genotype_sh = paste0(
    "dsx-sh:",sign_log2FoldChange_DSX_SH_genotype,
    "_fru-sh:",sign_log2FoldChange_FRU_SH_genotype,
    "_Or47b-sh:",sign_log2FoldChange_Or47b_SH_genotype,
    "_Or67d-sh:",sign_log2FoldChange_Or67d_SH_genotype),
    sign_paste_housing = paste0(
      "cs:",sign_log2FoldChange_CS_housing,
      "_dsx:",sign_log2FoldChange_DSX_housing,
      "_fru:",sign_log2FoldChange_FRU_housing,
      "_Or47b:",sign_log2FoldChange_Or47b_housing,
      "_Or67d:",sign_log2FoldChange_Or67d_housing))

```

## Genotype

```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_genotype_df <- res_df %>%
  filter(padj_social_mutants_genotype_lrt < 0.01) %>%
  select(gene_name, sign_paste_genotype_gh,starts_with("log2FoldChange")) %>%
  select(!contains("lrt")) %>%
  select(!contains("housing")) %>%
  select(!contains("_SH_"))

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_genotype_mat <- pairwise_log2fc_genotype_df %>%
  select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_genotype_filter <- rowSums(abs(pairwise_log2fc_genotype_mat) > 0) >= 1

# Filter out the dataframe
pairwise_log2fc_genotype_df <- pairwise_log2fc_genotype_df %>%
  filter(logfc_genotype_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_genotype_df) <- str_remove(colnames(pairwise_log2fc_genotype_df), "log2FoldChange_")
colnames(pairwise_log2fc_genotype_df) <- str_remove(colnames(pairwise_log2fc_genotype_df), "_GH_genotype")

```


```{r}
pairwise_log2fc_genotype_df <- pairwise_log2fc_genotype_df %>%
  pivot_longer(cols = - c(gene_name,sign_paste_genotype_gh), names_to = "genotype",values_to = "log2FoldChange")


```

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_genotype_df$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N genes") +
  ggtitle("Differential genes genotype")

```


```{r fig.width=6, fig.height=10}


pairwise_log2fc_genotype_df %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 5 ~ 5,
    log2FoldChange < -5 ~ -5,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste_genotype_gh , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT Genotype") 


```

## Housing

```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_housing_df <- res_df %>%
  filter(padj_social_mutants_housing_lrt < 0.01) %>%
  select(gene_name, sign_paste_housing,starts_with("log2FoldChange")) %>%
  select(!contains("lrt")) %>%
  select(!contains("genotype")) 

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_housing_mat <- pairwise_log2fc_housing_df %>%
  select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_housing_filter <- rowSums(abs(pairwise_log2fc_housing_mat) > 0) >= 1

# Filter out the dataframe
pairwise_log2fc_housing_df <- pairwise_log2fc_housing_df %>%
  filter(logfc_housing_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_housing_df) <- str_remove(colnames(pairwise_log2fc_housing_df), "log2FoldChange_")
colnames(pairwise_log2fc_housing_df) <- str_remove(colnames(pairwise_log2fc_housing_df), "_housing")

```


```{r}
pairwise_log2fc_housing_df <- pairwise_log2fc_housing_df %>%
  pivot_longer(cols = - c(gene_name,sign_paste), names_to = "genotype",values_to = "log2FoldChange")


```

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_housing_df$sign_paste)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential genes housing")

```


```{r fig.width=6, fig.height=10}


pairwise_log2fc_housing_df %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 5 ~ 5,
    log2FoldChange < -5 ~ -5,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT housing") 


```

## housing by genotype interaction

```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_interaction_df <- res_df %>%
  filter(padj_social_mutants_interaction_lrt < 0.01) %>%
  select(gene_name, entrezid, sign_paste_housing,starts_with("log2FoldChange")) %>%
  select(!contains("lrt")) %>%
  select(!contains("genotype")) 

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_interaction_mat <- pairwise_log2fc_interaction_df %>%
  select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_interaction_filter <- rowSums(abs(pairwise_log2fc_interaction_mat) > 0) >= 1

# Filter out the dataframe
pairwise_log2fc_interaction_df <- pairwise_log2fc_interaction_df %>%
  filter(logfc_interaction_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_interaction_df) <- str_remove(colnames(pairwise_log2fc_interaction_df), "log2FoldChange_")
colnames(pairwise_log2fc_interaction_df) <- str_remove(colnames(pairwise_log2fc_interaction_df), "_housing")

```


```{r}
pairwise_log2fc_interaction_df <- pairwise_log2fc_interaction_df %>%
  pivot_longer(cols = - c(gene_name,entrezid,sign_paste), names_to = "genotype",values_to = "log2FoldChange")


```

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_interaction_df$sign_paste)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential genes housing:genotype interaction")

```


```{r fig.width=6, fig.height=10}


pairwise_log2fc_interaction_df %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 5 ~ 5,
    log2FoldChange < -5 ~ -5,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("LRT housing:genotype interaction") 

```

### GO

```{r}
comp_list_interaction_entrezid <- pairwise_log2fc_interaction_df %>%
  select(entrezid, sign_paste) %>%
  split(.$sign_paste) %>%
  map("entrezid")


go_interaction_entrezid <- compareCluster(geneClusters = comp_list_interaction_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               
               universe = go_universe, qvalueCutoff = 0.01, readable = TRUE, ont = "ALL")

dotplot(go_interaction_entrezid,showCategory = 2, by='GeneRatio') +
  ggtitle("GO terms housing:genotype interaction")

```


Genotype by housing interaction genes

```{r}
map(unique(res_df %>%
  filter(padj_social_mutants_interaction_lrt < 0.01) %>%
    pull(gene_name)), plot_norm_counts , dds = deseq_obj_fitted)

```

