---
title: "fig2_helper_rnaseqdata_qc"
output: html_document
date: '2024-01-30'
---
# Overview

## Figure 1 RNA-seq changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants

## This is a helper notebook for general exploration of statistical parameters from the tests

# Libraries
```{r}
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
```

# Functions
```{r}


```

# Read data

```{r}
data_dir <- "../data_output/2024-1_diffexpr_input/"
```

DESeq files
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


Results joined files

```{r}
res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```


# Data re-shaping

## Pivot Longer

### Data transform for volcano plots
```{r}
log2fc_long <- res_df %>%
  select(gene_name, starts_with("log2FoldChange")) %>%
  pivot_longer(-gene_name, names_to = "comparison", values_to = "log2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"log2FoldChange_" ))

rawlog2fc_long <- res_df %>%
  select(gene_name, starts_with("rawlog2FoldChange")) %>%
  pivot_longer(-gene_name, names_to = "comparison", values_to = "rawlog2FoldChange") %>%
  mutate(comparison = str_remove(comparison,"rawlog2FoldChange_" ))

padj_long <- res_df %>%
  select(gene_name, starts_with("padj")) %>%
  pivot_longer(-gene_name, names_to = "comparison", values_to = "padj") %>%
  mutate(comparison = str_remove(comparison,"padj_" ))

pval_long <- res_df %>%
  select(gene_name, starts_with("pvalue")) %>%
  pivot_longer(-gene_name, names_to = "comparison", values_to = "pvalue") %>%
  mutate(comparison = str_remove(comparison,"pvalue_" ))

basemean_long <- res_df %>%
  select(gene_name, starts_with("baseMean")) %>%
  pivot_longer(-gene_name, names_to = "comparison", values_to = "baseMean") %>%
  mutate(comparison = str_remove(comparison,"baseMean_" ))


res_long_list <- list(basemean_long,rawlog2fc_long, log2fc_long, padj_long, pval_long)
res_long_df <- purrr::reduce(res_long_list,left_join,by =c("gene_name","comparison") )
```

# Read counts distributions

```{r}

as.data.frame(counts(deseq_list$social_mutants_raw_counts.salmon.merged.gene_counts.rds)) %>%
  pivot_longer(everything(), names_to = "sample", values_to = "counts") %>%
  ggplot(aes(log10(counts + 1), sample)) +
  geom_boxplot() +
  ggtitle("raw")


as.data.frame(counts(deseq_list$social_mutants.salmon.merged.gene_counts.rds)) %>%
  pivot_longer(everything(), names_to = "sample", values_to = "counts") %>%
  ggplot(aes(log10(counts + 1), sample)) +
  geom_boxplot() +
  ggtitle("combat")
```

# PCA between samples

```{r}
vsd_raw <- vst(deseq_list$social_mutants_raw_counts.salmon.merged.gene_counts.rds)
colData(vsd_raw)
plotPCA(vsd_raw , intgroup = "condition") + ggtitle("raw counts")

vsd_combat <- vst(deseq_list$social_mutants.salmon.merged.gene_counts.rds)
colData(vsd_combat)
plotPCA(vsd_combat , intgroup = "condition") + ggtitle("combat")


```


# P value distributions for each test


housing
```{r}
res_df %>%
  select(starts_with("pval")) %>%
  select(contains("housing")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram() +
  ggtitle("Housing comparisons P value distributions")

```


genotype
```{r}
res_df%>%
  select(starts_with("pval")) %>%
    select(contains("genotype")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram()  +
  ggtitle("Genotype comparisons P value distributions")
```

Interaction
```{r}

res_df %>%
  select(starts_with("pval")) %>%
    select(contains("interaction")) %>%
  pivot_longer(cols = everything(), names_to = "comparison", values_to = "pval") %>%
  ggplot(aes(pval)) +
  facet_wrap(vars(comparison)) +
  geom_histogram() +
  ggtitle("Interaction comparison P value distribution")

```

# 
```{r}
library(fdrtool)

res_df_dsx_fdrtool <- fdrtool::fdrtool(x = res_df$stat_DSX_housing [!is.na(res_df$padj_DSX_housing)],plot = TRUE)

res_df_dsx_fdrtool$pval %>%
  enframe() %>%
  ggplot(aes(value)) +
  geom_histogram()

summary(res_df_dsx_fdrtool$qval < 0.01)


```



# Volcano plot for pairwise comparisons

housing

```{r}

res_long_df %>%
  filter(str_detect(comparison,"housing")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison)+
  ylim(c(0,100)) +
  xlim(c(-5,5))

res_long_df %>%
  filter(str_detect(comparison,"housing")) %>%
      filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes(rawlog2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison)+
  ylim(c(0,100)) +
  xlim(c(-5,5))

```

```{r}

res_long_df %>%
  filter(str_detect(comparison,"housing")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes( log10(baseMean+1),log2FoldChange,color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison) +
  ylim(c(-5,5))


res_long_df %>%
  filter(str_detect(comparison,"housing")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes( log10(baseMean+1),rawlog2FoldChange,color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison)+
  ylim(c(-10,10))


```

genotype

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes(log2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison) +
  ylim(c(0,100)) +
  xlim(c(-10,10))

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
      filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes(rawlog2FoldChange, -10*log10(padj),color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison)+
  ylim(c(0,100)) +
  xlim(c(-10,10))

```

```{r}

res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes( log10(baseMean+1),log2FoldChange,color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison) +
  ylim(c(-5,5))


res_long_df %>%
  filter(str_detect(comparison,"genotype")) %>%
    filter(!str_detect(comparison,"lrt")) %>%
  ggplot(aes( log10(baseMean+1),rawlog2FoldChange,color = padj < 0.05 )) +
  geom_point(size = 0.5, alpha = 0.5) +
  facet_wrap(~comparison)+
  ylim(c(-10,10))


```

