---
title: "R Notebook"
output: html_notebook
---

# Overview

## Figure 2 Chromatin changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants

# Libraries
```{r}
library(tidyverse)
library(ComplexHeatmap)
```

# Functions
```{r}


```

# Read data

```{r}
data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```

DESeq files
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


Results joined files

```{r}
res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```


# Data re-shaping

Filter by chromatin mark 
```{r}
deseq_list_h3k4me3 <- str_detect(names(deseq_list),"H3K4me3")
deseq_list_h3k27ac <- str_detect(names(deseq_list),"H3K27ac")
deseq_list_rnapolii <- str_detect(names(deseq_list),"RNAPolII")

```

Clean list names
```{r}
names(deseq_list) <- str_remove(names(deseq_list),"cutnrun_")
```



# D Heatmap showing pairwise LFC for LRT test

```{r}
padj_mat_h3kme3 <- res_df_h3k4me3 %>%
  select(starts_with("padj"))
  
colnames(padj_mat_h3kme3) <- str_remove(colnames(padj_mat_h3kme3), "padj")

ComplexHeatmap::Heatmap(t(padj_mat_h3kme3),cluster_rows = FALSE)
```

```{r}
pairwise_log2f_mat_h3kme3 <- res_df_h3k4me3 %>%
  filter(padjH3K4me3_genotype_lrt < 0.000000000001) %>%
  select(starts_with("log2Fold")) %>%
  select(!contains("lrt")) %>%
  select(contains("genotype"))

colnames(pairwise_log2f_mat_h3kme3) <- str_remove(colnames(pairwise_log2f_mat_h3kme3), "log2FoldChange")
colnames(pairwise_log2f_mat_h3kme3) <- str_remove(colnames(pairwise_log2f_mat_h3kme3), "_genotype")
colnames(pairwise_log2f_mat_h3kme3) <- str_remove(colnames(pairwise_log2f_mat_h3kme3), "_ashr")


ComplexHeatmap::Heatmap(t(pairwise_log2f_mat_h3kme3),cluster_rows = FALSE)
```



# E Volcano plot for specific comparisons

```{r}

```


# G Venn diagrams for overlap of results for specific conditions




# Plots not made in R
## A Overview
## E Pileup of signal for specific clusters
## F IGV examples for specific clusters
## B Positive / Negative control genes IGV screenshot



