---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# Overview

## Figure 2 Chromatin changes in the central brain between social conditions, and olfactory receptor mutants and transcription factors mutants

# Libraries
```{r}
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
```

# Functions
```{r}


```

# Read data

```{r}
data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```

DESeq files
```{r}
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


Results joined files

```{r}
res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```


# Data re-shaping

Filter by chromatin mark 
```{r}
deseq_list_h3k4me3 <- str_detect(names(deseq_list),"H3K4me3")
deseq_list_h3k27ac <- str_detect(names(deseq_list),"H3K27ac")
deseq_list_rnapolii <- str_detect(names(deseq_list),"RNAPolII")

```

Clean list names
```{r}
names(deseq_list) <- str_remove(names(deseq_list),"cutnrun_")
```

# PCA

```{r}
vsd_h3k4me3 <- vst(deseq_list$H3K4me3_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds)
vsd_rnapolii <- vst(deseq_list$RNAPolII_seacrigg_peaks_union_deseq_counts_genotype_lrt_deseq_obj_fitted.Rds)

```

```{r}

vsd_h3k4me3$condition <- as.factor(paste0(vsd_h3k4me3$genotype,"_", vsd_h3k4me3$housing))
plotPCA(vsd_h3k4me3, intgroup = c("condition")) + 
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("H3K4me3")
```
```{r}
vsd_rnapolii$condition <- as.factor(paste0(vsd_rnapolii$genotype,"_", vsd_rnapolii$housing))
plotPCA(vsd_rnapolii, intgroup = c("condition")) + 
  theme_classic() +
  theme(aspect.ratio = 1) +
  ggtitle("RNAPolII")

```

# D Heatmap showing pairwise LFC for LRT test

Split  based on log2fc sign combinations

```{r}

res_df_h3k4me3 <- res_df_h3k4me3 %>%
  mutate(across(starts_with("log2FoldChange"),sign,.names = "sign_{.col}"))

res_df_h3k4me3 <- res_df_h3k4me3 %>%
  mutate(sign_paste_genotype_gh = paste0(
    "dsx-gh:",sign_log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr,
    "_fru-gh:",sign_log2FoldChange_H3K4me3_frumut_GH_genotype_ashr,
    "_Or47b-gh:",sign_log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr,
    "_Or67d-gh:",sign_log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr),
    sign_paste_genotype_sh = paste0(
      "dsx-sh:",sign_log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_H3K4me3_frumut_SH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr),
    sign_paste_genotype = paste0(
      "dsx-gh:",sign_log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr,
      "dsx-sh:",sign_log2FoldChange_H3K4me3_dsxmut_SH_genotype_ashr,
      "_fru-gh:",sign_log2FoldChange_H3K4me3_frumut_GH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_H3K4me3_frumut_SH_genotype_ashr,
      "_Or47b-gh:",sign_log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_H3K4me3_Or47bmut_SH_genotype_ashr,
      "_Or67d-gh:",sign_log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_H3K4me3_Or67dmut_SH_genotype_ashr))

```



```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_h3kme3_df <- res_df_h3k4me3 %>%
  filter(padj_H3K4me3_genotype_lrt < 0.01) %>%
  select(seqnames, start, end, sign_paste_genotype_gh,starts_with("log2FoldChange")) %>%
  select(!contains("lrt")) %>%
  select(!contains("housing")) %>%
  select(!contains("_SH_"))

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_h3kme3_mat <- pairwise_log2fc_h3kme3_df %>%
  select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_filter <- rowSums(abs(pairwise_log2fc_h3kme3_mat) > 1) >= 1

# Filter out the dataframe
pairwise_log2fc_h3kme3_df <- pairwise_log2fc_h3kme3_df %>%
  filter(logfc_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "log2FoldChange_")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "_genotype_ashr")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "_GH")
colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "H3K4me3_") 
  colnames(pairwise_log2fc_h3kme3_df) <- str_remove(colnames(pairwise_log2fc_h3kme3_df), "mut") 


colnames(pairwise_log2fc_h3kme3_df)
```


```{r}
pairwise_log2fc_h3kme3_df <- pairwise_log2fc_h3kme3_df %>%
  pivot_longer(cols = - c(seqnames, start, end,sign_paste_genotype_gh), names_to = "genotype",values_to = "log2FoldChange") %>%
  mutate(gene_name = paste0(seqnames,":",start,"-",end))


```

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_h3kme3_df$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
   theme_classic() +
  theme(aspect.ratio = 1) +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential H3K4me3 regions")

```


```{r fig.width=6, fig.height=10}


pairwise_log2fc_h3kme3_df %>%
  filter(seqnames %in% c("2L","2R","3L","3R","X")) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste_genotype_gh , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("H3K4me3") 


```


RNAPolII

Split  based on log2fc sign combinations

```{r}

res_df_rnapolii <- res_df_rnapolii %>%
  mutate(across(starts_with("log2FoldChange"),sign,.names = "sign_{.col}"))

res_df_rnapolii <- res_df_rnapolii %>%
  mutate(sign_paste_genotype_gh = paste0(
    "dsx-gh:",sign_log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr,
    "_fru-gh:",sign_log2FoldChange_RNAPolII_frumut_GH_genotype_ashr,
    "_Or47b-gh:",sign_log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr,
    "_Or67d-gh:",sign_log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr),
    sign_paste_genotype_sh = paste0(
      "dsx-sh:",sign_log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_RNAPolII_frumut_SH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr),
    sign_paste_genotype = paste0(
      "dsx-gh:",sign_log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr,
      "dsx-sh:",sign_log2FoldChange_RNAPolII_dsxmut_SH_genotype_ashr,
      "_fru-gh:",sign_log2FoldChange_RNAPolII_frumut_GH_genotype_ashr,
      "_fru-sh:",sign_log2FoldChange_RNAPolII_frumut_SH_genotype_ashr,
      "_Or47b-gh:",sign_log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr,
      "_Or47b-sh:",sign_log2FoldChange_RNAPolII_Or47bmut_SH_genotype_ashr,
      "_Or67d-gh:",sign_log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr,
      "_Or67d-sh:",sign_log2FoldChange_RNAPolII_Or67dmut_SH_genotype_ashr))

```



```{r}
# Filter results dataframe to get significant lrt genotype regions
# Select relevant columns for pairwise LogFC
pairwise_log2fc_rnapolii_df <- res_df_rnapolii %>%
  filter(padj_RNAPolII_genotype_lrt < 0.01) %>%
  select(seqnames, start, end, sign_paste_genotype_gh,starts_with("log2FoldChange")) %>%
  select(!contains("lrt")) %>%
  select(!contains("housing")) %>%
  select(!contains("_SH_"))

# Filter by absolute Fold change
# Create a matrix with only fold change 
pairwise_log2fc_rnapolii_mat <- pairwise_log2fc_rnapolii_df %>%
  select(starts_with("log2FoldChange"))
# Make a logical filterl
logfc_filter <- rowSums(abs(pairwise_log2fc_rnapolii_mat) > 1) >= 1

# Filter out the dataframe
pairwise_log2fc_rnapolii_df <- pairwise_log2fc_rnapolii_df %>%
  filter(logfc_filter)

# Change the column names for the data.frame to keeep only relevant info 
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "log2FoldChange_")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "_genotype_ashr")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "_GH")
colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "RNAPolII_") 
  colnames(pairwise_log2fc_rnapolii_df) <- str_remove(colnames(pairwise_log2fc_rnapolii_df), "mut") 


colnames(pairwise_log2fc_rnapolii_df)
```


```{r}
pairwise_log2fc_rnapolii_df <- pairwise_log2fc_rnapolii_df %>%
  pivot_longer(cols = - c(seqnames, start, end,sign_paste_genotype_gh), names_to = "genotype",values_to = "log2FoldChange") %>%
  mutate(gene_name = paste0(seqnames,":",start,"-",end))


```

```{r fig.width=5,fig.height=5}
sort(table(pairwise_log2fc_rnapolii_df$sign_paste_genotype_gh)) %>%
  enframe() %>%
  mutate(name = as.factor(name)) %>%
  mutate(name = fct_reorder(name, sort(value))) %>%
  ggplot(aes(value, name)) +
  geom_col() +
  ylab(NULL) +
  xlab("N regions") +
  ggtitle("Differential RNAPolII regions") +
  theme_classic() +
  theme(aspect.ratio = 1)

```


```{r fig.width=6,fig.height=10}


pairwise_log2fc_rnapolii_df %>%
  filter(seqnames %in% c("2L","2R","3L","3R","X")) %>%
  mutate(log2FoldChange = case_when(
    log2FoldChange > 1 ~ 1,
    log2FoldChange < -1 ~ -1,
    TRUE ~ log2FoldChange
  )) %>%
  ggplot(aes(genotype, gene_name, fill = log2FoldChange)) +
  geom_tile() +  
  scale_fill_gradient2(mid = "white",high = "red",low = "blue") +
  theme_minimal() +
  theme(aspect.ratio = 1,axis.text.y = element_blank()) +
  facet_wrap(~sign_paste_genotype_gh , scales = "free") + 
  ylab(NULL) +
  xlab(NULL) +
  ggtitle("RNAPolII")


```




# E Volcano plot for specific comparisons

H3K4me3
```{r}
volcplot_h3k4me3_dsx <- res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_dsxmut_GH_genotype_ashr, - 10 * log10(padj_H3K4me3_dsxmut_GH_genotype_ashr), color = padj_H3K4me3_dsxmut_GH_genotype_ashr < 0.01)) +
  geom_point() +
  ggtitle("dsx")+
  theme_classic() +
  theme(legend.position = "none", aspect.ratio = 1)+ 
  ylim(c(0,250))

volcplot_h3k4me3_fru <- res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_frumut_GH_genotype_ashr, - 10 * log10(padj_H3K4me3_frumut_GH_genotype_ashr), color = padj_H3K4me3_frumut_GH_genotype_ashr < 0.01)) +
  geom_point() +
    theme_classic() +
  theme(legend.position = "none", aspect.ratio = 1)+
  ggtitle("fru")+ 
  ylim(c(0,250))

volcplot_h3k4me3_or47b <- res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or47bmut_GH_genotype_ashr, - 10 * log10(padj_H3K4me3_Or47bmut_GH_genotype_ashr), color = padj_H3K4me3_Or47bmut_GH_genotype_ashr < 0.01)) +
  geom_point() +
    theme_classic() +

  theme(legend.position = "none", aspect.ratio = 1)+
  ggtitle("Or47b")+ 
  ylim(c(0,250))

volcplot_h3k4me3_or67d <- res_df_h3k4me3 %>%
  ggplot(aes(log2FoldChange_H3K4me3_Or67dmut_GH_genotype_ashr, - 10 * log10(padj_H3K4me3_Or67dmut_GH_genotype_ashr), color = padj_H3K4me3_Or67dmut_GH_genotype_ashr < 0.01)) +
  geom_point() +
    theme_classic() +

  theme(legend.position = "none", aspect.ratio = 1)+
  ggtitle("Or67d") + 
  ylim(c(0,250))

```

```{r fig.width=3,fig.height=3}
volcplot_h3k4me3_dsx
volcplot_h3k4me3_fru
volcplot_h3k4me3_or47b
volcplot_h3k4me3_or67d

```


RNAPolII
```{r}
volcplot_rnapolii_dsx <- res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr, - 10 * log10(padj_RNAPolII_dsxmut_GH_genotype_ashr), color = padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.05)) +
  geom_point() +
  ggtitle("dsx")+
  theme_classic() +
  theme(legend.position = "none", aspect.ratio = 1)+ 
  ylim(c(0,200))

volcplot_rnapolii_fru <- res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_frumut_GH_genotype_ashr, - 10 * log10(padj_RNAPolII_frumut_GH_genotype_ashr), color = padj_RNAPolII_frumut_GH_genotype_ashr < 0.05)) +
  geom_point() +
    theme_classic() +
  theme(legend.position = "none", aspect.ratio = 1)+
  ggtitle("fru")+ 
  ylim(c(0,200))

volcplot_rnapolii_or47b <- res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or47bmut_GH_genotype_ashr, - 10 * log10(padj_RNAPolII_Or47bmut_GH_genotype_ashr), color = padj_RNAPolII_Or47bmut_GH_genotype_ashr < 0.05)) +
  geom_point() +
    theme_classic() +

  theme(legend.position = "none", aspect.ratio = 1)+
  ggtitle("Or47b")+ 
  ylim(c(0,200))

volcplot_rnapolii_or67d <- res_df_rnapolii %>%
  ggplot(aes(log2FoldChange_RNAPolII_Or67dmut_GH_genotype_ashr, - 10 * log10(padj_RNAPolII_Or67dmut_GH_genotype_ashr), color = padj_RNAPolII_Or67dmut_GH_genotype_ashr < 0.05)) +
  geom_point() +
    theme_classic() +

  theme(legend.position = "none", aspect.ratio = 1)+
  ggtitle("Or67d") + 
  ylim(c(0,200))

```

```{r fig.width=3,fig.height=3}
volcplot_rnapolii_dsx
volcplot_rnapolii_fru
volcplot_rnapolii_or47b
volcplot_rnapolii_or67d

```



# G Venn diagrams for overlap of results for specific conditions

UpSet
```{r}
library(UpSetR)

all_comps_diff_list_h3k4me3 <- res_df_h3k4me3 %>%
  select(starts_with("padj")) %>%
  mutate(across(everything(),~ .x < 0.01)) %>%
  as.list() %>%
  map(which)

all_comps_diff_list_h3k4me3 <- all_comps_diff_list_h3k4me3[map_dbl(all_comps_diff_list_h3k4me3,length) > 0]

upset(fromList(all_comps_diff_list_h3k4me3),nsets = 16,nintersects = NA)


```

All
```{r}
upset(fromList(all_comps_diff_list_h3k4me3),nsets = 16,nintersects = NA)

```

Only Pairwise
```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt")],nsets = 16,nintersects = NA)

```

Pairwise GH
```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "GH")],nsets = 16,nintersects = NA)
```

Pairwise SH

```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "_SH_")],nsets = 16,nintersects = NA)
```

Pairwise within genotype

```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "fru")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "dsx")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "47b")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "67d")],nsets = 16,nintersects = NA)

```
```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "fru")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "dsx")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "47b")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "67d")],nsets = 16,nintersects = NA)

```


UpSet
```{r}
library("UpSetR")
library("ggVennDiagram")

all_comps_diff_list_rnapolii <- res_df_rnapolii %>%
  select(starts_with("padj")) %>%
  mutate(across(everything(),~ .x < 0.01)) %>%
  as.list() %>%
  map(which)

all_comps_diff_list_rnapolii <- all_comps_diff_list_rnapolii[map_dbl(all_comps_diff_list_rnapolii,length) > 0]

names(all_comps_diff_list_rnapolii) <- str_remove(names(all_comps_diff_list_rnapolii),"padj_RNAPolII_")
names(all_comps_diff_list_rnapolii) <- str_remove(names(all_comps_diff_list_rnapolii),"_genotype_ashr")
names(all_comps_diff_list_rnapolii) <- str_remove(names(all_comps_diff_list_rnapolii),"mut")

```

All
```{r}
upset(fromList(all_comps_diff_list_rnapolii),nsets = 16,nintersects = NA)

ggVennDiagram::ggVennDiagram(all_comps_diff_list_rnapolii)

```


Only Pairwise
```{r}
upset(fromList(all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt")],nsets = 16,nintersects = NA)

ggVennDiagram(all_comps_diff_list_rnapolii[!str_detect(names(all_comps_diff_list_rnapolii), "lrt")])
```




Pairwise GH
```{r}
upset(fromList(all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "GH")],nsets = 16,nintersects = NA)

ggVennDiagram((all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "GH")])+
  scale_fill_viridis_c()
```



Pairwise SH

```{r}
upset(fromList(all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "_SH")],nsets = 16,nintersects = NA)

ggVennDiagram((all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "_SH")]) +
  scale_fill_viridis_c()

```

Pairwise within genotype

```{r}
upset(fromList(all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "fru")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "dsx")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "47b")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "67d")],nsets = 16,nintersects = NA)

```
```{r}
ggVennDiagram((all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "fru")]) +
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "dsx")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "47b")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_rnapolii)[!str_detect(names(all_comps_diff_list_rnapolii), "lrt") & str_detect(names(all_comps_diff_list_rnapolii), "67d")])+
  scale_fill_viridis_c()

```




```{r}
upset(fromList(all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "fru")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "dsx")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "47b")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "67d")],nsets = 16,nintersects = NA)

```


```{r}
ggVennDiagram((all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "fru")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "dsx")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "47b")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_rnapolii)[str_detect(names(all_comps_diff_list_rnapolii), "lrt") | str_detect(names(all_comps_diff_list_rnapolii), "67d")])+
  scale_fill_viridis_c()

```



# H3K4me3 comparisons

UpSet
```{r}
all_comps_diff_list_h3k4me3 <- res_df_h3k4me3 %>%
  select(starts_with("padj")) %>%
  mutate(across(everything(),~ .x < 0.01)) %>%
  as.list() %>%
  map(which)

all_comps_diff_list_h3k4me3 <- all_comps_diff_list_h3k4me3[map_dbl(all_comps_diff_list_h3k4me3,length) > 0]

names(all_comps_diff_list_h3k4me3) <- str_remove(names(all_comps_diff_list_h3k4me3),"padj_H3K4me3_")
names(all_comps_diff_list_h3k4me3) <- str_remove(names(all_comps_diff_list_h3k4me3),"_genotype_ashr")
names(all_comps_diff_list_h3k4me3) <- str_remove(names(all_comps_diff_list_h3k4me3),"mut")

```

All
```{r}
upset(fromList(all_comps_diff_list_h3k4me3),nsets = 16,nintersects = NA)

ggVennDiagram::ggVennDiagram(all_comps_diff_list_h3k4me3)

```


Only Pairwise
```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt")],nsets = 16,nintersects = NA)

ggVennDiagram(all_comps_diff_list_h3k4me3[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt")])
```




Pairwise GH
```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "GH")],nsets = 16,nintersects = NA)

ggVennDiagram((all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "GH")])+
  scale_fill_viridis_c()
```



Pairwise SH

```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "_SH")],nsets = 16,nintersects = NA)

ggVennDiagram((all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "_SH")]) +
  scale_fill_viridis_c()

```

Pairwise within genotype

```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "fru")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "dsx")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "47b")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "67d")],nsets = 16,nintersects = NA)

```
```{r}
ggVennDiagram((all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "fru")]) +
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "dsx")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "47b")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_h3k4me3)[!str_detect(names(all_comps_diff_list_h3k4me3), "lrt") & str_detect(names(all_comps_diff_list_h3k4me3), "67d")])+
  scale_fill_viridis_c()

```




```{r}
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "fru")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "dsx")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "47b")],nsets = 16,nintersects = NA)
upset(fromList(all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "67d")],nsets = 16,nintersects = NA)

```


```{r}
ggVennDiagram((all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "fru")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "dsx")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "47b")])+
  scale_fill_viridis_c()
ggVennDiagram((all_comps_diff_list_h3k4me3)[str_detect(names(all_comps_diff_list_h3k4me3), "lrt") | str_detect(names(all_comps_diff_list_h3k4me3), "67d")])+
  scale_fill_viridis_c()

```

# Connect to genes

```{r}
library(GenomicRanges)
library(GenomicFeatures)
library(plyranges)
res_gr_h3k4me3 <- makeGRangesFromDataFrame( res_df_h3k4me3,keep.extra.columns = TRUE)
res_gr_rnapolii <- makeGRangesFromDataFrame( res_df_rnapolii,keep.extra.columns = TRUE)

```

```{r}
library(TxDb.Dmelanogaster.UCSC.dm6.ensGene)
library(org.Dm.eg.db)
library(GenomicFeatures)
library(clusterProfiler)

promoters_dm6 <- promoters(TxDb.Dmelanogaster.UCSC.dm6.ensGene, columns = "gene_id",upstream=0,downstream=1)

promoter_map_df <- clusterProfiler::bitr(geneID = unlist(promoters_dm6$gene_id), fromType = "ENSEMBL",toType ="SYMBOL",OrgDb = org.Dm.eg.db )
promoter_map <- promoter_map_df$SYMBOL 
names(promoter_map) <-  promoter_map_df$ENSEMBL

promoters_dm6$gene_name <- promoter_map[unlist(promoters_dm6$gene_id)]


promoter_map_df_entrez <- clusterProfiler::bitr(geneID = unlist(promoters_dm6$gene_id), fromType = "ENSEMBL",toType ="ENTREZID",OrgDb = org.Dm.eg.db )
promoter_map_entrez <- promoter_map_df_entrez$ENTREZ 
names(promoter_map_entrez) <-  promoter_map_df_entrez$ENSEMBL

promoters_dm6$entrez_id <- promoter_map_entrez[unlist(promoters_dm6$gene_id)]

```


```{r}
seqlevels(res_gr_h3k4me3) <- paste0("chr",seqlevels(res_gr_h3k4me3))
seqlevels(res_gr_rnapolii) <- paste0("chr",seqlevels(res_gr_rnapolii))

```

```{r}

res_gr_h3k4me3_genes <- plyranges::join_nearest_left(x = res_gr_h3k4me3,y = promoters_dm6, distance = TRUE) 

res_gr_rnapolii_genes <- plyranges::join_nearest_left(x = res_gr_rnapolii,y = promoters_dm6, distance = TRUE) 

```


# G GO terms
```{r}
as.data.frame(res_gr_h3k4me3_genes) %>%
  select(gene_name, contains("genotype") & contains("GH") & starts_with("padj") & ! contains("lrt")) %>%
  pivot_longer(-gene_name, names_to ="comparison",values_to = "padj") %>%
  filter(padj < 0.01) %>%
  mutate(comparison = str_remove(comparison, "padj_H3K4me3_")) %>%
  mutate(comparison = str_remove(comparison, "_genotype_ashr") ) %>%
  select(gene_name, comparison) %>%
  unique() %>%
  arrange(comparison) %>%
  write.csv("~/Downloads/h3k4me3_diff_genes.csv")

as.data.frame(res_gr_rnapolii_genes) %>%
  select(gene_name, contains("genotype") & contains("GH") & starts_with("padj") & ! contains("lrt")) %>%
  pivot_longer(-gene_name, names_to ="comparison",values_to = "padj") %>%
  filter(padj < 0.01) %>%
  mutate(comparison = str_remove(comparison, "padj_RNAPolII_")) %>%
  mutate(comparison = str_remove(comparison, "_genotype_ashr") ) %>%
  select(gene_name, comparison) %>%
  unique() %>%
  arrange(comparison) %>%
  write.csv("~/Downloads/rnapolii_diff_genes.csv")

```

```{r}

res_gr_h3k4me3_genes_list <- as.data.frame(res_gr_h3k4me3_genes) %>%
  select(entrez_id, contains("genotype") & contains("GH") & starts_with("padj") & ! contains("lrt")) %>%
  pivot_longer(-entrez_id, names_to ="comparison",values_to = "padj") %>%
  filter(padj < 0.01) %>%
  mutate(comparison = str_remove(comparison, "padj_H3K4me3_")) %>%
  mutate(comparison = str_remove(comparison, "_genotype_ashr") ) %>%
  drop_na() %>%
  split(f = .$comparison) %>%
  map(~unique(.x$entrez_id))

```



```{r}
clusterProfiler::compareCluster(res_gr_h3k4me3_genes_list,fun = enrichGO, OrgDb = org.Dm.eg.db)

enrichGO(unlist(res_gr_h3k4me3_genes_list),keyType = "ENTREZID", OrgDb = org.Dm.eg.db)
```



```{r}

res_gr_rnapolii_genes_list <- as.data.frame(res_gr_rnapolii_genes) %>%
  select(entrez_id, contains("genotype") & contains("GH") & starts_with("padj") & ! contains("lrt")) %>%
  pivot_longer(-entrez_id, names_to ="comparison",values_to = "padj") %>%
  filter(padj < 0.01) %>%
  mutate(comparison = str_remove(comparison, "padj_RNAPolII_")) %>%
  mutate(comparison = str_remove(comparison, "_genotype_ashr") ) %>%
  drop_na() %>%
  split(f = .$comparison) %>%
  map(~unique(.x$entrez_id))

```



```{r}
clust_comp <- clusterProfiler::compareCluster(res_gr_rnapolii_genes_list,fun = enrichGO, OrgDb = org.Dm.eg.db,readable = TRUE)

dotplot(clust_comp,showCategory = Inf)
```
```{r}
clust_comp@compareClusterResult %>%
  select(Cluster, Description, geneID) %>%
  write.csv("~/Downloads/results_go.csv")
```

# H Dsx and fru targets


# Plots not made in R
## A Overview
## E Pileup of signal for specific clusters
## F IGV examples for specific clusters
```{r}
res_df_rnapolii %>%
  filter(padj_RNAPolII_dsxmut_GH_genotype_ashr < 0.001) %>%
  filter(baseMean_RNAPolII_CS_housing_ashr > 25) %>%
  filter(seqnames %in% c("2L","2R","3L","3R","4","X")) %>%
  arrange(desc(abs(log2FoldChange_RNAPolII_dsxmut_GH_genotype_ashr)))

```

## B Positive / Negative control genes IGV screenshot



