---
title: "Figure 3 Correlation of the changes on transcriptome and chromatin"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
date: '2024-02-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```


```{r}
# Libraries
library(tidyverse)
library(ComplexHeatmap)
library(DESeq2)
library(circlize)
library(ComplexHeatmap) # Heatmaps
library(DESeq2) 
library(ggVennDiagram) 
library(clusterProfiler) # Go terms
library(org.Dm.eg.db) # GO annotation
library(tidyverse)
library(circlize) # Colors

```


```{r}
# Functions
get_genes_in_set <- function(gene_set, gene_universe) {
  return(map_lgl(gene_universe, ~ .x %in% gene_set))
}
get_overlap_genes <- function(named_list_gene_sets) {
  # Get all unique genes
  gene_universe <- na.omit(unique(unlist(named_list_gene_sets)))
  
  named_list_gene_sets <- map(named_list_gene_sets, # For each list:
                              # For each gene:
                              # Is gene in list? -> get logical for each list
                              get_genes_in_set,
                              gene_universe = gene_universe)
  
  # Return lgl matrix of presence / absence for each gene
  named_list_gene_sets <- as.data.frame(named_list_gene_sets)
  rownames(named_list_gene_sets) <- gene_universe
  return(named_list_gene_sets)
  
}
# Convert symbol to entrezid
tr_symbol2entrezid <- function(.x, symbol_etrez_map){
  symbol_etrez_map[.x]
}

```


```{r}
# Read chromatin data

# Read data

data_dir <- "../data_output/2024-01_diffbind_cutnrun/"
```


```{r}
# DESeq files
deseq_files <- list.files(data_dir,pattern = "[^$]+_deseq_obj_fitted.Rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```

```{r}
# Results joined files

res_df_h3k4me3 <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k4me3_all_join.tsv")
res_df_h3k27ac <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_h3k27ac_all_join.tsv")
res_df_rnapolii <- read_tsv(file = "../data_output/2024-01_diffbind_cutnrun/res_df_rnapolii_all_join.tsv")

```


```{r}
# Long data frames for volcano plots
res_long_h3k4me3_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_h3k4me3_df.Rds")
res_long_rnapolii_df <- readRDS("../data_output/2024-01_diffbind_cutnrun/res_long_rnapolii_df.Rds")

```



```{r}

# Read RNA data

# Read data

data_dir <- "../data_output/2024-1_diffexpr_input/"
```

```{r}
# DESeq files raw

deseq_files <- list.files(data_dir,pattern = "[^$]+rds")
deseq_list <- lapply(paste0(data_dir,deseq_files), readRDS)
names(deseq_list) <- deseq_files
```


```{r}
# DESeq files fitted 

deseq_obj_fitted <- readRDS("../data_output/2024-1_diffexpr_output/social_mutants_housing_lrt_deseq_obj_fitted.Rds")
```


```{r}
# Results joined files

res_df <- read_tsv(file = "../data_output/2024-1_diffexpr_output/res_df_all_join.tsv")
```

```{r}
# Comparisons list
comp_list <- readRDS( "../data_output/2024-01_diffbind_cutnrun/comp_list.Rds")
# Lists of differentially expressed genes by comparison 
comp_list <- c(comp_list,readRDS(file = "../data_output/2024-1_diffexpr_output/comp_list.Rds"))
comp_list_rna <- readRDS(file = "../data_output/2024-1_diffexpr_output/comp_list.Rds")
comp_list_rna$
```

```{r}
# Ranges connected to genes
res_gr_h3k4me3_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_h3k4me3_genes.Rds")
res_gr_rnapolii_genes <- readRDS( "../data_output/2024-01_diffbind_cutnrun/res_gr_rnapolii_genes.Rds")

```

# Venn diagram with comparisons:
 
## GH: all to CS, within the same genotype between RNAseq and CUT&RUN
```{r}

tr_range2gene <- function(res_id,gr_obj) {
  unique(gr_obj$gene_name[names(gr_obj) %in% res_id])
}
# Translate list gh all
comp_list$genotype_gh_all_h3k4me3_geneid <- map(comp_list$genotype_gh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_all_rnapolii_geneid <- map(comp_list$genotype_gh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_all_cutnrun_rna_list <- c(comp_list$genotype_gh_all_symbol,comp_list$genotype_gh_all_h3k4me3_geneid, comp_list$genotype_gh_all_rnapolii_geneid)

# Translate list gh up
comp_list$genotype_gh_up_h3k4me3_geneid <- map(comp_list$genotype_gh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_up_rnapolii_geneid <- map(comp_list$genotype_gh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_up_cutnrun_rna_list <- c(comp_list$genotype_gh_up_symbol,comp_list$genotype_gh_up_h3k4me3_geneid,comp_list$genotype_gh_up_rnapolii_geneid)

# Translate list gh down
comp_list$genotype_gh_down_h3k4me3_geneid <- map(comp_list$genotype_gh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_gh_down_rnapolii_geneid <- map(comp_list$genotype_gh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_gh_down_cutnrun_rna_list <- c(comp_list$genotype_gh_down_symbol,comp_list$genotype_gh_down_h3k4me3_geneid,comp_list$genotype_gh_down_rnapolii_geneid)

# Translate list sh all
comp_list$genotype_sh_all_h3k4me3_geneid <- map(comp_list$genotype_sh_all_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_all_rnapolii_geneid <- map(comp_list$genotype_sh_all_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_all_cutnrun_rna_list <- c(comp_list$genotype_sh_all_symbol,comp_list$genotype_sh_all_h3k4me3_geneid,comp_list$genotype_sh_all_rnapolii_geneid)

# Translate list sh up
comp_list$genotype_sh_up_h3k4me3_geneid <- map(comp_list$genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_up_rnapolii_geneid <- map(comp_list$genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_up_cutnrun_rna_list <- c(comp_list$genotype_sh_up_symbol,comp_list$genotype_sh_up_h3k4me3_geneid,comp_list$genotype_sh_up_rnapolii_geneid)

# Translate list sh down
comp_list$genotype_sh_down_h3k4me3_geneid <- map(comp_list$genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_down_rnapolii_geneid <- map(comp_list$genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_down_cutnrun_rna_list <- c(comp_list$genotype_sh_down_symbol,comp_list$genotype_sh_down_h3k4me3_geneid,comp_list$genotype_sh_down_rnapolii_geneid)


# Translate list gh down
comp_list$genotype_sh_down_h3k4me3_geneid <- map(comp_list$genotype_sh_up_h3k4me3_rangeid,tr_range2gene , gr_obj = res_gr_h3k4me3_genes)
comp_list$genotype_sh_down_rnapolii_geneid <- map(comp_list$genotype_sh_up_rnapolii_rangeid,tr_range2gene , gr_obj = res_gr_rnapolii_genes)

# Combine RNA and chromatin lists 
comp_list$genotype_sh_down_cutnrun_rna_list <- c(comp_list$genotype_sh_down_symbol,comp_list$genotype_sh_down_h3k4me3_geneid,comp_list$genotype_sh_down_rnapolii_geneid)



```

```{r}
# Combine RNA and chromatin lists 
comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list <- c(comp_list$lrt_interaction_gene_name,comp_list$genotype_gh_all_h3k4me3_geneid, comp_list$genotype_gh_all_rnapolii_geneid)

comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list <- c(comp_list$lrt_interaction_gene_name,comp_list$genotype_sh_all_h3k4me3_geneid, comp_list$genotype_sh_all_rnapolii_geneid)

comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list <- c(comp_list$lrt_housing_gene_name,comp_list$genotype_gh_all_h3k4me3_geneid, comp_list$genotype_gh_all_rnapolii_geneid)

comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list <- c(comp_list$lrt_housing_gene_name,comp_list$genotype_sh_all_h3k4me3_geneid, comp_list$genotype_sh_all_rnapolii_geneid)

comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list <- c(comp_list$lrt_genotype_gene_name,comp_list$genotype_gh_all_h3k4me3_geneid, comp_list$genotype_gh_all_rnapolii_geneid)

comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list <- c(comp_list$lrt_genotype_gene_name,comp_list$genotype_sh_all_h3k4me3_geneid, comp_list$genotype_sh_all_rnapolii_geneid)

```


### ALL 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list)
```



```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH All") + scale_x_continuous(expand = expansion(mult = .2))
```

Genes 
```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```

### UP 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH UP") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut))

```


```{r}
get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```


```{r}
get_overlap_genes(comp_list$genotype_gh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_up_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```


### DOWN 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS GH down") + scale_x_continuous(expand = expansion(mult = .2))
```
```{r}
get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_GH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_GH & (H3K4me3_frumut | RNAPolII_frumut))

```


```{r}
get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_GH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```


```{r}
get_overlap_genes(comp_list$genotype_gh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_gh_down_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_GH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```
## SH: all to a CS, within the same genotype between RNAseq and CUT&RUN

### ALL 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list)
```


```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh All") + scale_x_continuous(expand = expansion(mult = .2))
```

Genes 
```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```



### UP 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh up") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh UP") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_up_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_up_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```



### DOWN 

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list)
```

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"dsx|DSX")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"fru|FRU")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"47")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"67")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("Mutant vs CantonS sh down") + scale_x_continuous(expand = expansion(mult = .2))
```

```{r}
get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"dsx|DSX")]) %>%
  filter(DSX_SH & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"fru|FRU")]) %>%
  filter(FRU_SH & (H3K4me3_frumut | RNAPolII_frumut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"47")]) %>%
  filter(Or47b_SH & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

```

```{r}
get_overlap_genes(comp_list$genotype_sh_down_cutnrun_rna_list[str_detect(names(comp_list$genotype_sh_down_cutnrun_rna_list),"67")]) %>%
  filter(Or67d_SH & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

```



## Comparison of RNAseq LRT genotype:housing genes vs mutants CUT&RUN

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_interaction_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```


```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT interaction vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```


```{r}
get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_interaction_list),"dsx|DSX|lrt")]) %>%
  filter(social_mutants_interaction_lrt & (H3K4me3_dsxmut | RNAPolII_dsxmut))

```


## Comparison of RNAseq LRT housing genes vs mutants CUT&RUN

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_housing_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```


```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_housing_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT housing vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```

## Comparison of RNAseq LRT genotype genes vs mutants CUT&RUN

```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs GH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```



```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes <- get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_dsxmut | RNAPolII_dsxmut))

comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes %>%
  filter(H3K4me3_dsxmut)
```


```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go <- enrichGO(rownames(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_dsx_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


```




```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes <- get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_frumut | RNAPolII_frumut))

comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes
```


```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go <- enrichGO(rownames(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go)
```

```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go@result
```


```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes <- get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes
```


```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go <- enrichGO(rownames(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go)
```

```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go@result
```



```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes <- get_overlap_genes(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes
```

```{r}
comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go <- enrichGO(rownames(comp_list$genotype_gh_all_cutnrun_rna_lrt_genotype_list_67d_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


```




```{r}
ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))

ggVennDiagram::ggVennDiagram(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")], label_alpha = 0, label = "count", label_color = "white", label_size = 5 ) +
  scale_fill_viridis_c() +
  ggtitle("LRT genotype vs SH chromatin") + scale_x_continuous(expand = expansion(mult = .2))
```
```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes <- get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"dsx|DSX|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_dsxmut | RNAPolII_dsxmut))

comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes %>%
  filter(H3K4me3_dsxmut)
```


```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go <- enrichGO(rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go)
```

```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes_go@result
```


```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes <- get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"fru|FRU|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_frumut | RNAPolII_frumut))

comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes
```


```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go <- enrichGO(rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go)
```

```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes_go@result
```


```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes <- get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"47|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or47bmut | RNAPolII_Or47bmut))

comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes
```


```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go <- enrichGO(rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go)
```

```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes_go@result
```



```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes <- get_overlap_genes(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list[str_detect(names(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list),"67|lrt")]) %>%
  filter(social_mutants_genotype_lrt & (H3K4me3_Or67dmut | RNAPolII_Or67dmut))

comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes
```

```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go <- enrichGO(rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes),keyType = "SYMBOL", qvalueCutoff = 0.05,OrgDb = org.Dm.eg.db, ont = "ALL")


barplot(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go)
```
```{r}
comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes_go@result
```


# GO terms of any overlaps above:

```{r}

comp_list$genotype_gh_all_cutnrun_rna_list_entrezid <- map(comp_list$genotype_gh_all_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list$genotype_gh_up_cutnrun_rna_list_entrezid <- map(comp_list$genotype_gh_up_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list$genotype_gh_down_cutnrun_rna_list_entrezid <- map(comp_list$genotype_gh_down_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list$genotype_sh_all_cutnrun_rna_list_entrezid <- map(comp_list$genotype_sh_all_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list$genotype_sh_up_cutnrun_rna_list_entrezid <- map(comp_list$genotype_gh_up_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

comp_list$genotype_sh_down_cutnrun_rna_list_entrezid <- map(comp_list$genotype_gh_down_cutnrun_rna_list, tr_symbol2entrezid, symbol_etrez_map = symbol_etrez_map)

```

### GH

#### ALL 

```{r}
comp_list$genotype_gh_all_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list$genotype_gh_all_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list$genotype_gh_all_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS GH ALL")
```

#### UP 

```{r}
comp_list$genotype_gh_up_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list$genotype_gh_up_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list$genotype_gh_up_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS GH UP")
```

#### Down 

```{r}
comp_list$genotype_gh_down_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list$genotype_gh_down_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list$genotype_gh_down_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS GH DOWN")
```

### SH

#### ALL 

```{r}
comp_list$genotype_sh_all_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list$genotype_sh_all_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list$genotype_sh_all_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS SH ALL")
```

#### UP 

```{r}
comp_list$genotype_sh_up_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list$genotype_sh_up_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list$genotype_sh_up_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS SH UP")
```

#### Down 

```{r}
comp_list$genotype_sh_down_cutnrun_rna_list_entrezid_go <- compareCluster(geneClusters = comp_list$genotype_sh_down_cutnrun_rna_list_entrezid,
               OrgDb = org.Dm.eg.db,
               fun = enrichGO,
               qvalueCutoff = 0.05,
               readable = TRUE, ont = "ALL")



dotplot(comp_list$genotype_sh_down_cutnrun_rna_list_entrezid_go,showCategory = 5, by='GeneRatio') +
  ggtitle("Mutant vs CS SH DOWN")
```

```{r}
gene_mat <- get_overlap_genes(list("dsx" = rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_dsx_genes),
"fru" = rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_fru_genes),
"Or67d" = rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_67d_genes),
"Or47b" = rownames(comp_list$genotype_sh_all_cutnrun_rna_lrt_genotype_list_47b_genes))) %>%
  filter(rowSums(.)>=2)
gene_names_row_mat <- rownames(gene_mat)

gene_mat <- map_dfc(gene_mat, as.numeric) 
rownames(gene_mat) <-  gene_names_row_mat 


Heatmap(gene_mat %>%
  arrange(Or67d,Or47b),col = c("white","black"), cluster_rows = FALSE,cluster_columns = FALSE ) 

```


# Get tables for overlap genes




# Specific genes of any overlaps above:
## TPM or normed counts +p
## GVI view + stats